### 2012-04-16 trunk/tex/sigmasfr/ms.tex
checking in latex manuscript

\documentclass[apj]{emulateapj}
%\documentclass[12pt,preprint]{aastex}

\newcommand{\kms}{km~s$^{-1}$}
\newcommand{\mgii}{\textrm{Mg}~\textsc{ii}}
\newcommand{\nev}{[\textrm{Ne}~\textsc{v}]}
\newcommand{\oii}{[\textrm{O}~\textsc{ii}]}
\newcommand{\oiii}{[\textrm{O}~\textsc{iii}]}
\newcommand{\msun}{M$_{\odot}$}
\newcommand{\mstar}{M$_{*}$}
\newcommand{\units}{M$_{\odot}$~yr$^{-1}$~kpc$^{-2}$}
\newcommand{\lrest}{\lambda_{\textnormal{\scriptsize{rest}}}}
\newcommand{\lobs}{\lambda_{\textnormal{\scriptsize{obs}}}}
\newcommand{\sigmasfr}{\Sigma_{\textnormal{\scriptsize{SFR}}}}
\newcommand {\apgt} {\ {\raise-.5ex\hbox{$\buildrel>\over\sim$}}\ }
\newcommand {\aplt} {\ {\raise-.5ex\hbox{$\buildrel<\over\sim$}}\ }

\shorttitle{Compact Starbursts Revealed by HST and WISE}
\shortauthors{Diamond-Stanic et al.}

\begin{document}

%\title{HST and WISE Reveal Compact Starbursts Driving 1000
%  \kms\ Outflows}

\title{In the Crucible: Massive Compact Galaxies with High-Velocity
  Outflows and Eddington-Limited Star Formation}

\author{Aleksandar M. Diamond-Stanic\altaffilmark{1,2}, John
  Moustakas\altaffilmark{1}, Christy A. Tremonti\altaffilmark{3},
  Alison L. Coil\altaffilmark{1}, Ryan C. Hickox\altaffilmark{4}, Aday
  Robaina\altaffilmark{5}, Gregory H. Rudnick\altaffilmark{6}, \& Paul
  Sell\altaffilmark{3} }

\altaffiltext{1}{Center for Astrophysics and Space Sciences,
  University of California, San Diego, La Jolla, CA 92093, USA}
\altaffiltext{2}{Center for Galaxy Evolution Fellow}
\altaffiltext{3}{Department of Astronomy, University of
  Wisconsin-Madison, Madison, WI 53706, USA}
\altaffiltext{4}{Department of Physics and Astronomy, Dartmouth
  College, Hanover, NH 03755, USA}

\altaffiltext{5}{Institut de Ci{\'e}ncies del Cosmos, University of
  Barcelona, Barcelona, Spain}

\altaffiltext{6}{Department of Physics and Astronomy, University of
  Kansas, Lawrence, KS 66045, USA}

\begin{abstract}

Based on infrared photometry from the Wide-field Infrared Survey
Explorer (WISE) and optical morphologies from the Hubble Space
Telescope (HST), we present the discovery of compact, obscured star
formation in galaxies that exhibit $1000$~\kms\ outflows.  The implied
star formation rate (SFR) surface densities approach
$\sigmasfr=5000$~\msun~yr$^{-1}$~kpc$^{-2}$, and we argue that
feedback associated with this starburst event is a likely mechanism
for launching the high-velocity outflows.

\end{abstract}

\keywords{keywords}

\section{Introduction}

The central regions of elliptical galaxies are thought to form in
compact starbursts \citep[e.g.,][]{kor09,hop09}.  Feedback associated
with such starbursts can produce outflows driven by thermal energy
from supernova explosions \citep[e.g.,][]{che85}, stellar winds
\citep[e.g.,][]{lei92}, and momentum input from both supernova ram
pressure and radiation pressure on dust grains \citep[e.g.,][]{mur05}.
It has been argued that such feedback imposes a limit on the maximum
star-formation rate surface density ($\sigmasfr$) for starbursts
\citep[e.g.,][]{leh96,meu97,mur05,tho05} and the maximum stellar
surface density for elliptical galaxies and star clusters
\citep[e.g.,][]{hop10}.

% The relative importance of momentum injection versus thermal heating
% may vary as a function of galaxy mass \citep[e.g.,][]{hop12}, with
% thermal heating being less efficient in galaxies with larger gas
% densities and shorter cooling times.  Massive star clusters with large
% gas surface densities are a potential launching point for
% galactic-scale outflows driven by radiation pressure
% \citep[e.g.,][]{mur11}.

Galactic winds are ubiquitous in star-forming galaxies at all
redshifts and generally exhibit outflow velocities in the
100--500~\kms\ range
\citep[e.g.,][]{hec00,sha03,mar05,rup05,wei09,rub10,ste10}.  Thus, the
discovery of $|v|>1000$~\kms\ outflows in a sample of massive
($\textnormal{\mstar}\approx10^{11}$~\msun) post-starburst galaxies at
$z\sim0.6$ by \citet{tre07} suggested that a more energetic source,
such as feedback from an accreting supermassive black hole
\citep[e.g.,][]{sil98,dim05,deb12}, could have been responsible for
launching the winds.

However, it also plausible that feedback from a compact starburst
could expel gas with such large velocities.  Indeed, there is evidence
for a positive correlation between outflow velocity and starburst
luminosity \citep[e.g.,][]{mar05,rup05,tre07}, albeit with significant
scatter.  Furthermore, \citet{hec11} recently found outflows with
maximum velocities reaching $-1500$~\kms\ in a sample of local
starbursts with compact nuclei, and argued that such velocities could
be explained by feedback from massive stars.

% $|v|\gtrsim1000$~\kms\

In this Letter, we present results for a sample of massive galaxies at
$z\sim0.6$ that exhibit $|v|\apgt1000$~\kms\ outflows, expanding on
the sample from \citet{tre07}.  We seek to test whether the energetic
outflows in these galaxies could have been driven by feedback from
starbursts with very large star-formation rate (SFR) surface densities
($\sigmasfr$).  Our analysis combines galaxy sizes obtained with the
Hubble Space Telescope (HST) with star-formation rates and stellar
masses estimated from WISE, Spitzer, SDSS, and GALEX photometry.

% For example, there is evidence for a positive correlation between
% outflow velocity and starburst luminosity \citep[e.g.,][]{mar05},
% albeit with significant scatter.  Furthermore, \citet{hec11} recently
% found outflows reaching velocities of $-1500$~\kms\ in a sample of
% local starbursts with compact nuclei, and argued their higher
% velocities could be explained by feedback exerted by a large number of
% massive stars that are confined to a small radius.

% [which has been invoked theoretically as
%  a mechanism to quench star formation in galaxies,

% Winds are also common in active galactic nuclei (AGNs) with velocities
% in the 1000--20,000~\kms range \citep[e.g., ][]{cre03}, although it is
% unclear whether AGN feedback plays an important role in regulating
% star formation in galaxies.  There is clear observational evidence
% that active galactic nuclei (AGNs) produce outflows
% \citep[e.g.,][]{cre03} and that the outflowing gas can extend to
% $>$kpc scales \citep[e.g.,][]{rup11}, it is unclear whether such
% feedback plays an important role globally in quenching star formation.

% Feedback from massive stars and active black holes has important
% implications for galaxy evolution (e.g., luminosity function, star
% formation, galaxy color bi-modality, mass-metallicity relation,
% enrichment of IGM).

% Feedback from accreting supermassive black holes has also been invoked
% theoretically as a mechanism for quenching star formation in galaxies
% \citep[e.g.,][]{sil98,gra04,dim05}.  There is clear observational
% evidence that active galactic nuclei (AGNs) produce outflows
% \citep[e.g.,][]{cre03} and that the outflowing gas can extend to
% $>$kpc scales \citep[e.g.,][]{rup11}, but it is unclear whether such
% feedback plays an important role globally in quenching star formation
% and shaping the galaxy mass function.

% and optical spectra ($\lrest=2500$-5200~\AA)

%  The spectral region surrounding the
%  \mgii~$\lambda\lambda2796,2803$ absorption alines, which are used to
%  measure outflow velocities, is highlighted in both wavelength and
%  velocity space.

%  and are scaled to match the WISE channel 2 photometry ($\lobs=4.6$~$\mu$m)
% (\mgii~$\lambda2796$ is plotted in blue and \mgii~$\lambda2803$ is plotted in red)

\section{Analysis}

\subsection{HST/WFC3 Imaging}

Our sample derives from 29 galaxies targeted for HST/WFC3 imaging in
programs 12019 and 12272 (PI: C. Tremonti).  Using the F814W filter on
the UVIS channel, which has $0.04\arcsec$ pixels and
$\textnormal{FWHM}=0.074\arcsec$, we obtained $4\times10$~min
exposures in a single orbit for each galaxy.  The dithered images were
processed with
MultiDrizzle\footnote{http://stsdas.stsci.edu/multidrizzle/} to
produce science mosaics with $0.02\arcsec$ pixels.  For each galaxy,
we use GALFIT \citep{pen02,pen10} to model the two-dimensional surface
brightness profile with a single Sersic component, using stars in the
images to construct the model point-spread function (PSF).  The Sersic
index (n) and effective radius ($r_e$) are free parameters in the
model.  In cases where the best-fit model returns $n>4$, we also fit
an $n=4$ de Vaucouleurs model \citep{dev48}, yielding a larger $r_e$
value (due to the covariance between $n$ and $r_e$), and we use these
these larger effective radii in our analysis.

For this paper, we are most interested in the galaxies with the
largest $\sigmasfr$ values, which also have the smallest effective
radii.  We show the HST images for three high-$\sigmasfr$ galaxies in
Figure~\ref{fig:seds}.  In all three cases, the single-component model
GALFIT accounts for $>85\%$ of the total flux.  The residuals show
diffuse emission that is consistent with these systems being
late-stage galaxy mergers after final coalescence, although we defer a
detailed comparison of the observed morphologies with expectations
from merger simulations to future work.

For the most compact galaxy (J0905+5759, $r_e=0.013\arcsec$ or
100~pc), we also show the observed one-dimensional surface brightness
profile in the bottom-right panel of Figure~\ref{fig:profile}.  We
compare to the profiles of six stars in the same image, the best-fit
de Vaucouleurs model, and a de Vaucoulerus model with a larger
effective radius ($r_e=0.04\arcsec$, the native WFC3/UVIS pixel size,
which corresponds to a physical scale of 290~pc).  This comparison
illustrates that this galaxy, while only marginally resolved with an
effective radius that is $\sim20\%$ of the image FWHM, is clearly more
extended than a point source.

For such a compact source, there is significant uncertainty in our
$r_e$ measurement given uncertainties in the model PSF.  To quantify
this uncertainty, we used TinyTim to generate a model PSF that is
artificially narrower than the stars in the image (convolving the
output of tiny2 with a $\textnormal{FWHM}=0.04\arcsec$ Gaussian,
whereas the image FWHM is $0.074\arcsec$) and found that this
increased the effective radius in the GALFIT model by a factor of two.
We also fit a two-component PSF+Sersic model, but found that the
Sersic component dominates the fit, yielding a similar effective
radius.  Furthermore, the spectrum of the galaxy shows no evidence for
an AGN contribution to the $I$-band continuum (see
Figure~\ref{fig:spectra}), so there is no clear motivation for
including an unresolved, point-source component in the model.  We
conclude that this galaxy is quite compact and that our $r_e$ estimate
of 100~pc, while uncertain, is likely accurate within a factor of two.

\begin{figure}[!t]
%\includegraphics[angle=90,scale=0.68]{sigmasfr_datafigure.ps}
\includegraphics[angle=0,scale=0.41]{3seds.ps}
\caption{Left: Observed UV--IR SEDs ($\lrest=0.1$--15~$\mu$m) for
  three galaxies with large SFR surface densities
  ($\sigmasfr>3000$~\units).  We show stellar population fits to the
  $\lrest=0.1$--3~$\mu$m emission (black solid line) and three
  templates for dust emission \citep[M82 starburst, Arp 220 starburst,
    and obscured quasar;][]{pol07}.  The starburst templates provide
  reasonable fits to the $\lobs=12$ and 22~$\mu$m WISE photometry,
  while the quasar template does not.  Right: HST/WFC3 F814W images
  (probing $\lrest\approx5000$~\AA) showing that these galaxies are
  dominated by a compact nucleus.}
\label{fig:seds}
\end{figure}
% scaled to the WISE $\lobs=4.6~\mu$m flux.

\begin{figure}[!t]
\includegraphics[angle=0,scale=0.41]{profile.ps}
\label{fig:profile}
\caption{One-dimensional surface brightness profile for J0905+5759,
  which has the smallest effective radius in the sample.  The observed
  profile is shown as the solid black line, and the profiles of six
  stars in the same image are shown in blue.  The best-fit de
  Vaucouleurs profile with $r_e=100$~pc is shown as a dashed red line,
  and for comparison a broader profile with $r_e=0.04\arcsec=290$~pc
  is shown as the dotted green line.  This galaxy is quite compact,
  but is more extended than a point source.}
\end{figure}

\subsection{Photometry, Stellar Masses, and Star-formation rates}

We gathered photometry from the All-Sky Release of the Wide-field
Infrared Survey Explorer \citep[WISE,][]{wri10}, the Seventh Data
Release of the Sloan Digital Sky Survey \citep[SDSS,][]{aba09}, and
General Release 6 from the Galaxy Evolution Explorer (GALEX).  We also
obtained $5\times30$~sec dithered exposures in the 3.6~$\mu$m and
4.5~$\mu$m for all sources with the Infrared Array Camera
\citep{faz04} on the Spitzer Space Telescope \citep{wer04} as part of
General Observer program 60145 (PI: C. Tremonti).  We used the
post--basic calibrated data to perform aperture photometry on all
sources, and we also used the
APEX\footnote{http://irsa.ipac.caltech.edu/data/SPITZER/docs/dataanalysistools/tools/mopex/}
point-source extraction software for photometry of sources in crowded
fields.  All the photometry was corrected for Galactic extinction
based on the \citet{sch98} dust maps.  We show spectral energy
distributions (SEDs) for the three high-$\sigmasfr$ galaxies in
Figure~\ref{fig:seds}.

We use the method of \citet{mou11} to derive stellar masses and
UV-based SFRs from fits to the 0.1--5~$\mu$m SEDs.  We also estimate
IR-based SFRs from the 12~$\mu$m and 22~$\mu$m WISE photometry.

Comment on agreement between SFR indicators.

\begin{figure}[!t]
\includegraphics[angle=0,scale=0.41]{spectra.ps}
\caption{Spectra covering $\lrest=2500$--5200~\AA\ for the three
  galaxies shown in Figure~\ref{fig:seds}.  These spectra are
  dominated by light from the young stellar population and exhibit
  \oii~$\lambda3727$, H$\beta$~$\lambda4861$, and \oiii~$\lambda5007$
  emission lines.  The panels on the right zoom on the
  \mgii~$\lambda\lambda2796,2803$ spectral region in both wavelength
  and velocity space.  The spectrum in the bottom panel has sufficient
  spectral resolution ($\textnormal{FWHM}\approx8$~\kms) to resolve
  the intrinsic shape of the absorption-line profile, revealing that
  the gas near the centroid velocity has unity covering factor.}
\label{fig:spectra}
\end{figure}

\begin{figure*}[!t]
\begin{center}
\includegraphics[angle=0,scale=.8]{sigmasfr.ps} %\\
%\includegraphics[angle=0,scale=.7]{sizemass_sigmasfr.ps}
%\caption{$\sigmasfr$--mass and size--mass relationships.}
\caption{SFR surface densities and stellar masses for the HST--WISE
  sample described in this paper (black circles, with symbol size
  proportional to outflow velocity), along with samples of gas-rich
  mergers (orange squares) and star-forming galaxies (shown with 68\%
  contours).  We mark the empirical threshold for launching winds
  \citep[dotted line, $\sigmasfr=0.1$~\units;][]{hec02}, the
  90th-percentile starburst intensity limit from \citet{meu97} (dashed
  line, $\sigmasfr=45$~\units), and the Eddington limit from radiation
  pressure on dust grains \citep[solid line,
    $\sigmasfr\approx2000$~\units;][]{mur05,tho05,hop10}.  Our
  HST--WISE sample overlaps with the region characterized by gas-rich
  mergers, and extends to very large SFR surface densities near the
  Eddington limit.  The sample of gas-rich mergers includes ULIRGs
  \citep{vei06}, Lyman break analogs with dominant central objects
  \citep{ove09}, and the local compact starburst Arp 220 \citep{sco97,
    ken98, rod08}.  The samples of star-forming galaxies are drawn
  from \citet{wuy11} at $0.02<z<0.2$ (solid black contour),
  $0.5<z<1.5$ (dashed red countour), and $1.5<z<2.5$ (dotted purple
  contour), and from \citet{law12} at $2.5<z<3.6$ (dash-dotted blue
  contour). }
\label{fig:sigmasfr}
\end{center}
\end{figure*}

\subsection{Optical Spectroscopy}

We present low-resolution $R=1000-3000$ spectroscopy from MMT/Blue
Channel and SDSS (J1506+5402), Magellan/MagE (J1341-0321), and
Keck/LRIS (J0905+5759) in Figure~\ref{fig:spectra.}.  We also
highlight the \mgii~$\lambda\lambda2796,2803$ absorption lines, which
are used use to measure outflow velocities.

For J0905+5759 we show the \mgii\ absorption-line profiles from
$R\approx37,000$ spectra obtained with Keck/HIRES.  The oscillator
strength of \mgii~$\lambda$2796 is twice that of \mgii~$\lambda$2803,
but the equivalent widths of the two lines and the shapes of the line
profiles are quite similar, indicating that both lines are optically
thick.  The fact that the absorption line profile approaches zero near
the velocity centroid $v=-2470$~\kms\ indicates that the outflowing
gas covers the entire continuum source at these velocities.

%\section{Analysis}
%
%\subsection{Star-formation Rates and Stellar Masses}
%
%\subsection{Morphologies and Sizes}
%
%\subsection{Outflow Kinematics and Covering Factors}

% \begin{figure*}[!t]
% \begin{center}
% \includegraphics[angle=0,scale=.8]{sizemass_sigmasfr.ps}
% \caption{size--mass relationship.}
% \label{fig:sizemass}
% \end{center}
% \end{figure*}

% %\begin{center}
% \begin{deluxetable}{ccccccc}
% \tabletypesize{\scriptsize}
% 
% \tablecaption{Galaxy Properties\label{tab:properties}}
% \tablewidth{0pt}
% 
% \tablehead{ \colhead{Galaxy Name} & \colhead{z} & \colhead{$M_{*}$} & \colhead{$v$} & \colhead{SFR} & \colhead{$r_e$} & \colhead{$\sigmasfr$} }
% 
% \startdata
% J150636.29+540220.7   & 0.608 & 11.01 & -1211 &  621 & 0.13 & 5851 \\
% J090523.60+575912.4   & 0.712 & 10.62 & -2470 & 344 & 0.10 & 5478 \\ 
% %J094417.84+093019.3   & 0.514 & 10.73 & -1778 & $<43.22$ & 161 & 0.15 & 1139 \\
% J134136.79$-$032125.2   & 0.658 & 10.61 & -875  & 490 & 0.16 & 3058 \\ 
% % J1506 has Lx=42.66
% \enddata
% 
% %\tablecomments{}
% %\tablenotetext{a}{Star-formation rate based on \citet{ken98}.  No extinction correction has been applied.}
% 
% \end{deluxetable}
% %\end{center}

\section{Discussion}

The compact sizes ($r_e\approx100$~pc) and large star formation rates
($\textnormal{SFR}\approx500$~\msun) for the galaxies shown in
Figure~\ref{fig:seds} imply extremely large star-formation rate
surface densities ($\sigmasfr\approx5000$~\units).  To place these
galaxies in context, we plot their $\sigmasfr$ values as a function of
stellar mass in Figure~\ref{fig:sigmasfr}.  We also include
measurements of late-stage, gas-rich mergers at $z<0.3$ from
\citet{vei06}, star-forming galaxies at $z<0.3$ from \citet{ove09},
and star-forming galaxies at $z=1.5$--3.6 from \citet{law12}.

Points to make:
\begin{itemize}
\item \citet{ken98}, the standard reference for the relationship
  between SFR and gas surface density, includes Arp 200 with
  $\sigmasfr\approx10^3$~\units\ and
  $\Sigma_{H_2}\approx5\times10^{10}$~\msun~kpc$^{-2}$.  
\item The star clusters considered by \citet{meu97} extend into this
  $\sigmasfr>10^{3}$~\units\ range.

\end{itemize}

% We show relationship between effective radius and stellar mass for our
% WISE-HST sample in bottom panel of Figure~\ref{fig:sizemass}.  Here,
% we include the gas-rich mergers from \citet{vei06} as well as
% $z\sim2.3$ compact massive galaxies from \citet{van08}.  We also show
% the size--mass relationship for elliptical galaxies at $z\sim0.1$ from
% \citet{she03}, and the average size evolution of spheroidal ($n>2.5$)
% galaxies from $z=2$ to $z=0.1$ from \citet{tru07}.

%\subsection{A Maximum Star-Formation Rate Surface Density?}

\subsection{Momentum Flux from Supernovae and Stellar Winds}

\citet{meu97} argued for a limit near 45~\units (somewhat smaller for
a Chabrier IMF) based on the surface brightness of starbursts measured
using rest-frame UV, H$\alpha$, far-IR, and radio continuum emission,
such that only 10\% of starbursts exceeded this limit.  They argued
that the momentum flux from supernovae and stellar winds expected at
this threshold matches the mean central pressure measured by
\citet{hec90} for starburst-driven winds.

There are also relevant arguments about ram pressure driving of
high-velocity winds from \citet{hec11}.

\subsection{The Eddington Limit from Radiation Pressure on Dust Grains}

In models where gaseous outflows are driven by radiation pressure from
massive stars, estimates of the maximum $\sigmasfr$ where the outward
force from radiation exceeds the inward force of gravity are in the
$\sigmasfr\sim10^3$~\units\ range \citep[e.g.,][]{tho05,hop10}.

% Our galaxies exceed the \citet{meu97} limit but are roughly in line
% with the limit from radiation pressure.

The relative importance of momentum injection versus thermal heating
may vary as a function of galaxy mass \citep[e.g.,][]{hop12}, with
thermal heating being less efficient in galaxies with larger gas
densities and shorter cooling times.  Regarding momentum injection,
\citet{sha11} have argued that radiation pressure becomes more
important than ram pressure at large SFRs.  Massive star clusters with
large gas surface densities are the ideal launching point for
galactic-scale outflows driven by radiation pressure
\citep[e.g.,][]{mur11}, and the outflow velocities are expected to
scale with escape velocity of the most massive star clusters in a
galaxy.

\subsection{Outflows at the Escape Velocity}

The observed $\gtrsim1000$~\kms\ outflow velocities we observe correspond
approximately to the escape velocities for compact regions (i.e.,
massive star clusters) with the sizes and masses that we've measured.

\begin{equation}
v_{esc} = \sqrt{2GM_{cl}/r_{cl}} = 2074~\textnormal{km~s}^{-1} \\%\left({v_c\over200}\right)^{5/2} 
\left({M_{cl}\over10^{11} M_{\odot}}\right)^{1/2} 
\left({r_{cl}\over200~\textnormal{pc}}\right)^{-1/2}
\label{eq:vesc}
\end{equation}

% This is in agreement with the predicitons from radiation pressure
% launching winds from the most massive star clusters in a galaxy.

Question of whether other observables are plausible.  
\begin{itemize}
\item Expected velocity dispersion.  Some results have suggested that
  turbulence becomes large at high surface densities, and therefore
  the velocity dispersion should be large.  
\item The dynamical time for the starburst.  If gas is consumed with
  an efficiency of a few \% per dynamical time, how long do we expect
  the starburst to last?
\end{itemize}

Other points: 
\begin{itemize}
\item Is this mechanism viable for the whole sample?  We see large
  outflow velocities in rest of the sample, where the galaxies are
  more ``post'' starburst.  This fits in a scenario where the genuine
  post-starbursts are further along in the evolution after the outflow
  quenches star formation.
\item Will these evolve into ellipticals, or do they have enough gas
  to reform a disk?  If they do quench, how difficult would it be to
  grow in size to match the local size--mass relationship?  Could
  their descendants be the handful of local galaxies that don't lie on
  the size--mass relationship?
\item Is there disagreement between $L_{IR}+L_{UV}$ and H$\alpha$
  SFRs?  \citet{hec11} pointed out that this could be a sign of
  escaping ionizing photons.
\end{itemize}

\subsection{Limits on Ongoing AGN Activity}

No evidence in spectra for unobscured AGN component.  J1506+5402 has
X-ray and \nev.

\subsection{Placing These Galaxies in Context}

They are rare and thus represent an unusual or short-lived phase.

Connection to models.  How such large SFRs given the powerful wind?

Connection to ellipticals.  Conceivable that they could grown in size
sufficiently by $z=0$?

\acknowledgments

We acknowledge useful discussions with and assistance from several
people.  AMD acknowledges support from the Southern California Center
for Galaxy Evolution, a multi-campus research program funded by the
University of California Office of Research.

% James Bullock, Xavier Prochaska, Kate Rubin, Art Wolfe, Alex Mendez

\begin{thebibliography}{}
\bibitem[Abazajian et al.(2009)]{aba09} Abazajian, K.~N.,
  Adelman-McCarthy, J.~K., Ag{\"u}eros, M.~A., et al.\ 2009, \apjs,
  182, 543
% \bibitem[Baldwin et al.(1981)]{bal81} Baldwin, J.~A., Phillips, M.~M.,
%   \& Terlevich, R.\ 1981, \pasp, 93, 5
% \bibitem[Barton \& Cooke(2009)]{bar09} Barton, E.~J., \& Cooke,
%   J.\ 2009, \aj, 138, 1817
% \bibitem[Bordoloi et al.(2011)]{bor11} Bordoloi, R., et al.\ 2011,
%   arXiv:1106.0616
% \bibitem[Buitrago et al.(2008)]{bui08} Buitrago, F., Trujillo, I.,
%   Conselice, C.~J., Bouwens, R.~J., Dickinson, M., \& Yan, H.\ 2008,
%   \apjl, 687, L61
% \bibitem[Coil et al.(2011)]{coi11} Coil, A.~L., Weiner, B.~J., Holz,
%   D.~E., et al.\ 2011, \apj, 743, 46
% \bibitem[Chen et al.(2010)]{hchen10} Chen, H.-W., Wild, V., Tinker,
%   J.~L., Gauthier, J.-R., Helsby, J.~E., Shectman, S.~A., \& Thompson,
%   I.~B.\ 2010, \apjl, 724, L176
% \bibitem[Chen et al.(2010b)]{ychen10} Chen, Y.-M., Tremonti, C.~A.,
%   Heckman, T.~M., Kauffmann, G., Weiner, B.~J., Brinchmann, J., \&
%   Wang, J.\ 2010, \aj, 140, 445
\bibitem[Chevalier \& Clegg(1985)]{che85} Chevalier, R.~A., \& Clegg,
  A.~W.\ 1985, \nat, 317, 44
% \bibitem[Coil et al.(2011)]{coi11} Coil, A.~L., Weiner, B.~J., Holz,
%   D.~E., Cooper, M.~C., Yan, R., \& Aird, J.\ 2011, arXiv:1104.0681
\bibitem[Crenshaw et al.(2003)]{cre03} Crenshaw, D.~M., Kraemer,
  S.~B., \& George, I.~M.\ 2003, \araa, 41, 117
% \bibitem[Croton et al.(2006)]{cro06} Croton, D.~J., et al.\ 2006,
%   \mnras, 365, 11
% \bibitem[Dekel \& Birnboim(2006)]{dek06} Dekel, A., \& Birnboim,
%   Y.\ 2006, \mnras, 368, 2
\bibitem[de Vaucouleurs(1948)]{dev48} de Vaucouleurs, G.\ 1948,
  Annales d'Astrophysique, 11, 247
\bibitem[Debuhr et al.(2012)]{deb12} Debuhr, J., Quataert, E., \& Ma,
  C.-P.\ 2012, \mnras, 420, 2221
\bibitem[Di Matteo et al.(2005)]{dim05} Di Matteo, T., Springel, V.,
  \& Hernquist, L.\ 2005, \nat, 433, 604
\bibitem[Fazio et al.(2004)]{faz04} Fazio, G.~G., Hora, J.~L., Allen,
  L.~E., et al.\ 2004, \apjs, 154, 10
\bibitem[Granato et al.(2004)]{gra04} Granato, G.~L., De Zotti, G.,
  Silva, L., Bressan, A., \& Danese, L.\ 2004, \apj, 600, 580
\bibitem[Heckman et al.(1990)]{hec90} Heckman, T.~M., Armus, L., \&
  Miley, G.~K.\ 1990, \apjs, 74, 833
\bibitem[Heckman et al.(2000)]{hec00} Heckman, T.~M., Lehnert, M.~D.,
  Strickland, D.~K., \& Armus, L.\ 2000, \apjs, 129, 493
\bibitem[Heckman(2002)]{hec02} Heckman, T.~M.\ 2002, Extragalactic Gas
  at Low Redshift, 254, 292
\bibitem[Heckman et al.(2011)]{hec11} Heckman, T.~M., et al.\ 2011,
  \apj, 730, 5
% \bibitem[Hopkins et al.(2009)]{hop09} Hopkins, P.~F., Bundy, K.,
%   Murray, N., Quataert, E., Lauer, T.~R., \& Ma, C.-P.\ 2009, \mnras,
%   398, 898
%\bibitem[Hopkins et al.(2009)]{hop09} Hopkins, P.~F., Hernquist, L.,
%  Cox, T.~J., Keres, D., \& Wuyts, S.\ 2009, \apj, 691, 1424
\bibitem[Hopkins et al.(2009)]{hop09} Hopkins, P.~F., Cox, T.~J.,
  Dutta, S.~N., et al.\ 2009, \apjs, 181, 135
% \bibitem[Hopkins et al.(2010a)]{hop10a} Hopkins, P.~F.,
%   Bundy, K., Hernquist, L., Wuyts, S., \& Cox, T.~J.\ 2010, \mnras,
%   401, 1099
\bibitem[Hopkins et al.(2010)]{hop10} Hopkins, P.~F., Murray, N.,
  Quataert, E., \& Thompson, T.~A.\ 2010, \mnras, 401, L19
% %\bibitem[Hopkins et al.(2011)]{hop11} Hopkins, P.~F., Quataert, E., \&
% %  Murray, N.\ 2011, arXiv:1101.4940
% \bibitem[Hopkins et al.(2011)]{hop11} Hopkins, P.~F., Quataert, E., \&
%   Murray, N.\ 2011, arXiv:1110.4638
\bibitem[Hopkins et al.(2012)]{hop12} Hopkins, P.~F., Quataert, E., \&
  Murray, N.\ 2012, \mnras, arXiv:1110.4638
% \bibitem[Kacprzak et al.(2010)]{kac10} Kacprzak, G.~G., Churchill,
%   C.~W., Ceverino, D., Steidel, C.~C., Klypin, A., \& Murphy,
%   M.~T.\ 2010, \apj, 711, 533
% \bibitem[Kacprzak et al.(2011a)]{kac11a} Kacprzak, G.~G., Churchill,
%   C.~W., Barton, E.~J., \& Cooke, J.\ 2011, \apj, 733, 105
% \bibitem[Kacprzak et al.(2011b)]{kac11b} Kacprzak, G.~G., Churchill,
%   C.~W., Evans, J.~L., Murphy, M.~T., \& Steidel, C.~C.\ 2011,
%   arXiv:1106.3068
% \bibitem[Kauffmann et al.(2003)]{kau03} Kauffmann, G., Heckman, T.~M.,
%   Tremonti, C., et al.\ 2003, \mnras, 346, 1055
% \bibitem[Kennicutt(1998)]{ken98} Kennicutt, R.~C., Jr.\ 1998, \araa,
%   36, 189
\bibitem[Kennicutt(1998)]{ken98} Kennicutt, R.~C., Jr.\ 1998, \apj,
  498, 541
% \bibitem[Kere{\v s} et al.(2005)]{ker05} Kere{\v s}, D., Katz, N.,
%   Weinberg, D.~H., \& Dav{\'e}, R.\ 2005, \mnras, 363, 2
% \bibitem[Kere{\v s} et al.(2009)]{ker09} Kere{\v s}, D., Katz, N.,
%   Dav{\'e}, R., Fardal, M., \& Weinberg, D.~H.\ 2009, \mnras, 396,
%   2332
% \bibitem[Kobulnicky \& Kewley(2004)]{kob04} Kobulnicky, H.~A., \&
%   Kewley, L.~J.\ 2004, \apj, 617, 240
\bibitem[Kormendy et al.(2009)]{kor09} Kormendy, J., Fisher, D.~B.,
  Cornell, M.~E., \& Bender, R.\ 2009, \apjs, 182, 216
% \bibitem[Kriek et al.(2010)]{kri10} Kriek, M., et al.\ 2010, \apjl,
%   722, L64
\bibitem[Law et al.(2012)]{law12} Law, D.~R., Steidel, C.~C., Shapley,
  A.~E., et al.\ 2012, \apj, 745, 85
\bibitem[Lehnert \& Heckman(1996)]{leh96} Lehnert, M.~D., \& Heckman,
  T.~M.\ 1996, \apj, 472, 546
% \bibitem[Lehnert \& Heckman(1996)]{leh96} Lehnert, M.~D., \& Heckman,
%   T.~M.\ 1996, \apj, 462, 651
\bibitem[Leitherer et al.(1992)]{lei92} Leitherer, C., Robert, C., \&
  Drissen, L.\ 1992, \apj, 401, 596
\bibitem[Martin(2005)]{mar05} Martin, C.~L.\ 2005, \apj, 621, 227
% \bibitem[Martin(2006)]{mar06} Martin, C.~L.\ 2006, \apj, 647, 222
% \bibitem[Martin \& Bouch{\'e}(2009)]{mar09} Martin, C.~L., \&
%   Bouch{\'e}, N.\ 2009, \apj, 703, 1394
% \bibitem[McIntosh et al.(2005)]{mci05} McIntosh, D.~H., et al.\ 2005,
%   \apj, 632, 191
\bibitem[Meurer et al.(1997)]{meu97} Meurer, G.~R., Heckman, T.~M.,
  Lehnert, M.~D., Leitherer, C., \& Lowenthal, J.\ 1997, \aj, 114, 54
% \bibitem[Morrissey et al.(2007)]{mor07} Morrissey, P., Conrow, T.,
%   Barlow, T.~A., et al.\ 2007, \apjs, 173, 682
\bibitem[Moustakas et al.(2011)]{mou11} Moustakas, J., Zaritsky, D.,
  Brown, M., et al.\ 2011, arXiv:1112.3300
\bibitem[Murray et al.(2005)]{mur05} Murray, N., Quataert, E., \&
  Thompson, T.~A.\ 2005, \apj, 618, 569
\bibitem[Murray et al.(2011)]{mur11} Murray, N., M{\'e}nard, B., \&
  Thompson, T.~A.\ 2011, \apj, 735, 66
% \bibitem[Nath \& Silk(2009)]{nat09} Nath, B.~B., \& Silk, J.\ 2009,
%   \mnras, 396, L90
% \bibitem[Nestor et al.(2011)]{nes11} Nestor, D.~B., Johnson, B.~D.,
%   Wild, V., M{\'e}nard, B., Turnshek, D.~A., Rao, S., \& Pettini,
%   M.\ 2011, \mnras, 412, 1559
% \bibitem[Oke(1990)]{oke90} Oke, J.~B.\ 1990, \aj, 99, 1621
% \bibitem[Oke et al.(1995)]{oke95} Oke, J.~B., et al.\ 1995, \pasp,
%   107, 375
% \bibitem[Oppenheimer \& Dav{\'e}(2006)]{opp06} Oppenheimer, B.~D., \&
%   Dav{\'e}, R.\ 2006, \mnras, 373, 1265
% \bibitem[Osterbrock(1989)]{ost89} Osterbrock, D.~E.\ 1989,
%   Astrophysics of Gaseous Nebulae and Active Galactic Nuclei (Mill
%   Valley, CA: University Science Books) 
\bibitem[Overzier et al.(2009)]{ove09} Overzier, R.~A., Heckman,
  T.~M., Tremonti, C., et al.\ 2009, \apj, 706, 203
% \bibitem[Pagel et al.(1979)]{pag79} Pagel, B.~E.~J., Edmunds, M.~G.,
%   Blackwell, D.~E., Chun, M.~S., \& Smith, G.\ 1979, \mnras, 189, 95
\bibitem[Peng et al.(2002)]{pen02} Peng, C.~Y., Ho, L.~C., Impey,
  C.~D., \& Rix, H.-W.\ 2002, \aj, 124, 266
\bibitem[Peng et al.(2010)]{pen10} Peng, C.~Y., Ho, L.~C., Impey,
  C.~D., \& Rix, H.-W.\ 2010, \aj, 139, 2097
% \bibitem[Pettini et al.(2001)]{pet01} Pettini, M., Shapley, A.~E.,
%   Steidel, C.~C., Cuby, J.-G., Dickinson, M., Moorwood, A.~F.~M.,
%   Adelberger, K.~L., \& Giavalisco, M.\ 2001, \apj, 554, 981
\bibitem[Polletta et al.(2007)]{pol07} Polletta, M., Tajer, M.,
  Maraschi, L., et al.\ 2007, \apj, 663, 81
% \bibitem[Prochaska \& Hennawi(2009)]{pro09} Prochaska, J.~X., \&
%   Hennawi, J.~F.\ 2009, \apj, 690, 1558
% \bibitem[Prochaska et al.(2011a)]{pro11a} Prochaska, J.~X., Kasen, D.,
%   \& Rubin, K.\ 2011, arXiv:1102.3444
% \bibitem[Prochaska et al.(2011b)]{pro11b} Prochaska,
%   J.~X., Weiner, B., Chen, H.~-., Mulchaey, J.~S., \& Cooksey,
%   K.~L.\ 2011, arXiv:1103.1891
\bibitem[Rodr{\'{\i}}guez Zaur{\'{\i}}n et al.(2008)]{rod08}
  Rodr{\'{\i}}guez Zaur{\'{\i}}n, J., Tadhunter, C.~N., \&
  Gonz{\'a}lez Delgado, R.~M.\ 2008, \mnras, 384, 875
% \bibitem[Rubin et al.(2010a)]{rub10a} Rubin, K.~H.~R., Prochaska, J.~X.,
%   Koo, D.~C., Phillips, A.~C., \& Weiner, B.~J.\ 2010, \apj, 712, 574
\bibitem[Rubin et al.(2010)]{rub10} Rubin, K.~H.~R., Weiner, B.~J.,
  Koo, D.~C., Martin, C.~L., Prochaska, J.~X., Coil, A.~L., \& Newman,
  J.~A.\ 2010, \apj, 719, 1503
% \bibitem[Rubin et al.(2011)]{rub11} Rubin, K.~H.~R., Prochaska, J.~X.,
%   M{\'e}nard, B., Murray, N., Kasen, D., Koo, D.~C., \& Phillips,
%   A.~C.\ 2011, \apj, 728, 55
\bibitem[Rupke et al.(2005)]{rup05} Rupke, D.~S., Veilleux, S., \&
  Sanders, D.~B.\ 2005, \apjs, 160, 115 % analysis and discussion
% \bibitem[Rupke \& Veilleux(2011)]{rup11} Rupke, D.~S.~N., \& Veilleux,
%   S.\ 2011, \apjl, 729, L27
% \bibitem[Sato et al.(2009)]{sat09} Sato, T., Martin, C.~L., Noeske,
%   K.~G., Koo, D.~C., \& Lotz, J.~M.\ 2009, \apj, 696, 214
\bibitem[Schlegel et al.(1998)]{sch98} Schlegel, D.~J., Finkbeiner,
  D.~P., \& Davis, M.\ 1998, \apj, 500, 525
% \bibitem[Schwartz \& Martin(2004)]{sch04} Schwartz, C.~M., \& Martin,
%   C.~L.\ 2004, \apj, 610, 201
\bibitem[Scoville et al.(1997)]{sco97} Scoville, N.~Z., Yun, M.~S., \&
  Bryant, P.~M.\ 1997, \apj, 484, 702
\bibitem[Sharma \& Nath(2011)]{sha11} Sharma, M., \& Nath,
  B.~B.\ 2011, arXiv:1112.3447
\bibitem[Shapley et al.(2003)]{sha03} Shapley, A.~E., Steidel, C.~C.,
  Pettini, M., \& Adelberger, K.~L.\ 2003, \apj, 588, 65
\bibitem[Shen et al.(2003)]{she03} Shen, S., Mo, H.~J., White,
  S.~D.~M., et al.\ 2003, \mnras, 343, 978
\bibitem[Silk \& Rees(1998)]{sil98} Silk, J., \& Rees, M.~J.\ 1998,
  \aap, 331, L1
% \bibitem[Springel \& Hernquist(2003)]{spr03} Springel, V., \&
%   Hernquist, L.\ 2003, \mnras, 339, 312
% \bibitem[Steidel et al.(2002)]{ste02} Steidel, C.~C., Kollmeier,
%   J.~A., Shapley, A.~E., Churchill, C.~W., Dickinson, M., \& Pettini,
%   M.\ 2002, \apj, 570, 526
\bibitem[Steidel et al.(2010)]{ste10} Steidel, C.~C., Erb, D.~K.,
  Shapley, A.~E., Pettini, M., Reddy, N., Bogosavljevi{\'c}, M.,
  Rudie, G.~C., \& Rakic, O.\ 2010, \apj, 717, 289
% \bibitem[Stewart et al.(2011a)]{ste11a} Stewart, K.~R., Kaufmann, T.,
%   Bullock, J.~S., Barton, E.~J., Maller, A.~H., Diemand, J., \&
%   Wadsley, J.\ 2011, \apjl, 735, L1
% \bibitem[Stewart et al.(2011b)]{ste11b} Stewart, K.~R., Kaufmann, T.,
%   Bullock, J.~S., Barton, E.~J., Maller, A.~H., Diemand, J., \&
%   Wadsley, J.\ 2011, arXiv:1103.4388
% \bibitem[Strickland et al.(2004)]{str04} Strickland, D.~K., Heckman,
%   T.~M., Colbert, E.~J.~M., Hoopes, C.~G., \& Weaver, K.~A.\ 2004,
%   \apjs, 151, 193
% \bibitem[Taylor et al.(2010)]{tay10} Taylor, E.~N., Franx, M.,
%   Glazebrook, K., Brinchmann, J., van der Wel, A., \& van Dokkum,
%   P.~G.\ 2010, \apj, 720, 723
\bibitem[Thompson et al.(2005)]{tho05} Thompson, T.~A., Quataert, E.,
  \& Murray, N.\ 2005, \apj, 630, 167
\bibitem[Tremonti et al.(2007)]{tre07} Tremonti, C.~A., Moustakas, J.,
  \& Diamond-Stanic, A.~M.\ 2007, \apjl, 663, L77
% %\bibitem[Tremonti et al.(2012)]{tre12} Tremonti, C.~A., et al.\ 2012,
% %  in prep
\bibitem[Trujillo et al.(2007)]{tru07} Trujillo, I., Conselice, C.~J.,
  Bundy, K., et al.\ 2007, \mnras, 382, 109
\bibitem[van Dokkum et al.(2008)]{van08} van Dokkum, P.~G., et
  al.\ 2008, \apjl, 677, L5
% \bibitem[van Dokkum et al.(2010)]{van10} van Dokkum, P.~G., et
%   al.\ 2010, \apj, 709, 1018
% \bibitem[Vogt et al.(1994)]{vog94} Vogt, S.~S., et al.\ 1994,
%   \procspie, 2198, 362
\bibitem[Veilleux et al.(2006)]{vei06} Veilleux, S., Kim, D.-C., Peng,
  C.~Y., et al.\ 2006, \apj, 643, 707
\bibitem[Weiner et al.(2009)]{wei09} Weiner, B.~J., et al.\ 2009,
  \apj, 692, 187
\bibitem[Werner et al.(2004)]{wer04} Werner, M.~W., Roellig, T.~L.,
  Low, F.~J., et al.\ 2004, \apjs, 154, 1
\bibitem[Wright et al.(2010)]{wri10} Wright, E.~L., Eisenhardt,
  P.~R.~M., Mainzer, A.~K., et al.\ 2010, \aj, 140, 1868
% \bibitem[Wuyts et al.(2010)]{wuy10} Wuyts, S., Cox, T.~J., Hayward,
%   C.~C., Franx, M., Hernquist, L., Hopkins, P.~F., Jonsson, P., \& van
%   Dokkum, P.~G.\ 2010, \apj, 722, 1666
% \bibitem[Wuyts et al.(2011)]{wuy11} Wuyts, S., et al.\ 2011,
%   arXiv:1107.0317
\bibitem[Wuyts et al.(2011)]{wuy11} Wuyts, S., F{\"o}rster Schreiber,
  N.~M., van der Wel, A., et al.\ 2011, \apj, 742, 96
% \bibitem[Zhang \& Thompson(2010)]{zha10} Zhang, D., \& Thompson,
%   T.~A.\ 2010, arXiv:1005.4691
% \bibitem[Zirm et al.(2007)]{zir07} Zirm, A.~W., et al.\ 2007, \apj,
%   656, 66
\end{thebibliography}

\clearpage

%\clearpage

% \clearpage
% 
% \begin{figure*}[!t]
% \begin{center}
% \includegraphics[angle=0,scale=.60]{j0905_hires_mg.ps}
% \caption{Keck/HIRES spectra.}
% \label{fig:hires}
% \end{center}
% \end{figure*}

%\clearpage

\end{document}

### 2012-04-17 trunk/tex/sigmasfr/ms.tex
updates to section 2.2

@@
 
-We use the method of \citet{mou11} to derive stellar masses and
-UV-based SFRs from fits to the 0.1--5~$\mu$m SEDs.  We also estimate
-IR-based SFRs from the 12~$\mu$m and 22~$\mu$m WISE photometry.
+We estimate IR-based star-formation rates for the 25/29 galaxies with
+WISE 12~$\mu$m detections by fitting \citet{cha01} templates to their
+12 and 22~$\mu$m fluxes.  For the 14/29 galaxies with 22~$\mu$m
+detections, the method of \citet{ruj12} yields SFRs that agree with
+the above values within 0.05~dex.  We note that the shape of the IR
+SED for star-forming galaxies depends on the surface density of star
+formation \citep[e.g.,][]{ruj11,elb11}, with more compact starbursts
+having larger total-IR (8--1000~$\mu$m) to mid-IR (8--24~$\mu$m)
+ratios.  The extreme $\sigmasfr$ values of our sample imply large
+total-IR to mid-IR ratios, characteristic of the most luminous
+galaxies in the local universe \citep[e.g.,][]{cha01,dal02,rie09}.
+For the 8/29 sources where we estimate $SFR_{IR}>200$~\msun~yr$^{-1}$
+above, using the most luminous local templates would yield SFRs that
+are larger by 0.5~dex.
 
-Comment on agreement between SFR indicators.
+We also estimate star-formation rates and stellar masses based on
+stellar population fits to the $\lrest=0.1$--3~$\mu$m SEDs using the
+method of \citet{mou11}.  For galaxies with
+$SFR_{IR}>50$~\msun~yr$^{-1}$, there is agreement between these
+UV-optical-based estimates and $SFR_{IR}$ with a scatter of 0.32~dex.
 
@@
 %   D.~E., et al.\ 2011, \apj, 743, 46
+\bibitem[Chary \& Elbaz(2001)]{cha01} Chary, R., \& Elbaz, D.\ 2001,
+  \apj, 556, 562
 % \bibitem[Chen et al.(2010)]{hchen10} Chen, H.-W., Wild, V., Tinker,
@@
 %   \mnras, 365, 11
+\bibitem[Dale \& Helou(2002)]{dal02} Dale, D.~A., \& Helou, G.\ 2002,
+  \apj, 576, 159
 % \bibitem[Dekel \& Birnboim(2006)]{dek06} Dekel, A., \& Birnboim,
@@
   \& Hernquist, L.\ 2005, \nat, 433, 604
+\bibitem[Elbaz et al.(2011)]{elb11} Elbaz, D., Dickinson, M., Hwang,
+  H.~S., et al.\ 2011, \aap, 533, A119
 \bibitem[Fazio et al.(2004)]{faz04} Fazio, G.~G., Hora, J.~L., Allen,
@@
   Gonz{\'a}lez Delgado, R.~M.\ 2008, \mnras, 384, 875
+\bibitem[Rieke et al.(2009)]{rie09} Rieke, G.~H., Alonso-Herrero, A.,
+  Weiner, B.~J., et al.\ 2009, \apj, 692, 556
 % \bibitem[Rubin et al.(2010a)]{rub10a} Rubin, K.~H.~R., Prochaska, J.~X.,
@@
 %   A.~C.\ 2011, \apj, 728, 55
+\bibitem[Rujopakarn et al.(2011)]{ruj11} Rujopakarn, W.,
+  Rieke, G.~H., Eisenstein, D.~J., \& Juneau, S.\ 2011, \apj, 726, 93
+\bibitem[Rujopakarn et al.(2012)]{ruj12} Rujopakarn, W., Rieke, G.~H.,
+  Weiner, B.~J., et al.\ 2011, arXiv:1107.2921
 \bibitem[Rupke et al.(2005)]{rup05} Rupke, D.~S., Veilleux, S., \&

### 2012-04-17 tex/sigmasfr/ms.tex
more edits to section 2.2

--- 2012-04-16 trunk/tex/sigmasfr/ms.tex
@@
 \newcommand{\sigmasfr}{\Sigma_{\textnormal{\scriptsize{SFR}}}}
+\newcommand{\sfrir}{\textnormal{SFR}_{\textnormal{\scriptsize{IR}}}}
 \newcommand {\apgt} {\ {\raise-.5ex\hbox{$\buildrel>\over\sim$}}\ }
@@
 Release of the Sloan Digital Sky Survey \citep[SDSS,][]{aba09}, and
-General Release 6 from the Galaxy Evolution Explorer (GALEX).  We also
-obtained $5\times30$~sec dithered exposures in the 3.6~$\mu$m and
-4.5~$\mu$m for all sources with the Infrared Array Camera
-\citep{faz04} on the Spitzer Space Telescope \citep{wer04} as part of
-General Observer program 60145 (PI: C. Tremonti).  We used the
-post--basic calibrated data to perform aperture photometry on all
-sources, and we also used the
+General Release 6 from the Galaxy Evolution Explorer
+\citep[GALEX,][]{mar05galex}.  We also obtained $5\times30$~sec
+dithered exposures at 3.6~$\mu$m and 4.5~$\mu$m for all sources with
+the Infrared Array Camera \citep{faz04} on the Spitzer Space Telescope
+\citep{wer04} as part of General Observer program 60145 (PI:
+C. Tremonti).  We used the post--basic calibrated data to perform
+aperture photometry on all sources, and we also used the
 APEX\footnote{http://irsa.ipac.caltech.edu/data/SPITZER/docs/dataanalysistools/tools/mopex/}
@@
 
-We use the method of \citet{mou11} to derive stellar masses and
-UV-based SFRs from fits to the 0.1--5~$\mu$m SEDs.  We also estimate
-IR-based SFRs from the 12~$\mu$m and 22~$\mu$m WISE photometry.
+We estimate IR-based star-formation rates for the 25/29 galaxies with
+WISE 12 or 22~$\mu$m detections by fitting \citet{cha01} templates to
+their 12 and 22~$\mu$m fluxes.  For the 14/29 galaxies with 22~$\mu$m
+detections, this yields SFRs that agree with those obtained from the
+\citet{ruj12} method based on 24~$\mu$m luminosity (with a scatter of
+0.05~dex).  We note that several authors have shown that the shape of
+the IR SED for star-forming galaxies depends on the surface density of
+star formation \citep[e.g.,][]{ruj11,elb11}, with more compact
+starbursts having larger total-IR (8--1000~$\mu$m) to mid-IR
+(8--24~$\mu$m) ratios.  The extreme $\sigmasfr$ values of our sample
+imply large total-IR to mid-IR ratios, characteristic of the most
+luminous galaxies in the local universe
+\citep[e.g.,][]{cha01,dal02,rie09}.  For the 8/29 sources with SFRs in
+the ULIRG regime ($\sfrir>200$~\msun~yr$^{-1}$), we would obtain SFRs
+that are larger by 0.5~dex (compared to the values obtained above) if
+we used the most luminous local templates.
 
-Comment on agreement between SFR indicators.
+We also estimate star-formation rates and stellar masses based on
+stellar population fits to the $\lrest=0.1$--3~$\mu$m SEDs using the
+method of \citet{mou11}.  For galaxies with
+$\sfrir>50$~\msun~yr$^{-1}$, there is agreement between these UV-based
+SFR estimates and $\sfrir$ with a scatter of 0.32~dex.  We find a
+median extinction of $A_V=0.4$~mag for an SMC-based dust law.
 
@@
 %   Bouch{\'e}, N.\ 2009, \apj, 703, 1394
+\bibitem[Martin et al.(2005)]{mar05galex} Martin, D.~C., Fanson, J.,
+  Schiminovich, D., et al.\ 2005, \apjl, 619, L1
 % \bibitem[McIntosh et al.(2005)]{mci05} McIntosh, D.~H., et al.\ 2005,

### 2012-04-18 trunk/tex/sigmasfr/ms.tex
wrote section 3.1

--- 2012-04-16 trunk/tex/sigmasfr/ms.tex
@@
 \altaffiltext{5}{Institut de Ci{\'e}ncies del Cosmos, University of
-  Barcelona, Barcelona, Spain}
+  Barcelona, 08028 Barcelona, Spain}
 
@@
 Telescope (HST), we present the discovery of compact, obscured star
-formation in galaxies that exhibit $1000$~\kms\ outflows.  The implied
-star formation rate (SFR) surface densities approach
+formation in galaxies that exhibit $\gtrsim1000$~\kms\ outflows.  The
+implied star formation rate (SFR) surface densities approach
 $\sigmasfr=5000$~\msun~yr$^{-1}$~kpc$^{-2}$, and we argue that
@@
 
-\subsection{HST/WFC3 Imaging}
+%\subsection{HST/WFC3 Imaging}
+\subsection{Morphologies and Sizes}
 
@@
 
-\subsection{Photometry, Stellar Masses, and Star-formation rates}
+%\subsection{Photometry, Star Formation Rates, and Stellar Masses}
+\subsection{Star Formation Rates and Stellar Masses}
 
@@
 
-We use the method of \citet{mou11} to derive stellar masses and
-UV-based SFRs from fits to the 0.1--5~$\mu$m SEDs.  We also estimate
-IR-based SFRs from the 12~$\mu$m and 22~$\mu$m WISE photometry.
+We estimate IR-based star-formation rates for the 25/29 galaxies with
+WISE 12 or 22~$\mu$m detections by fitting \citet{cha01} templates to
+their 12 and 22~$\mu$m fluxes.  For the 14/29 galaxies with 22~$\mu$m
+detections, this yields SFRs that agree with those obtained from the
+\citet{ruj12} method based on 24~$\mu$m luminosity with a scatter of
+0.05~dex.  We note that several authors have shown that the shape of
+the IR SED for star-forming galaxies depends on the surface density of
+star formation \citep[e.g.,][]{ruj11,elb11}, with more compact
+starbursts having larger total-IR (8--1000~$\mu$m) to mid-IR
+(8--24~$\mu$m) ratios.  The extreme $\sigmasfr$ values of our sample
+imply large total-IR to mid-IR ratios, characteristic of the most
+luminous galaxies in the local universe
+\citep[e.g.,][]{cha01,dal02,rie09}.  If we used the most luminous
+local templates for the 8/29 sources with SFRs in the ULIRG regime
+($\sfrir>200$~\msun~yr$^{-1}$), we would obtain SFRs that are larger
+by 0.5~dex than the values we adopt for this paper.
 
-Comment on agreement between SFR indicators.
+We also estimate star-formation rates and stellar masses based on
+stellar population fits to the $\lrest=0.1$--3~$\mu$m SEDs using the
+method of \citet{mou11}.  For galaxies with
+$\sfrir>50$~\msun~yr$^{-1}$, there is agreement between these UV-based
+SFR estimates and $\sfrir$ with a scatter of 0.32~dex.  For an SMC
+dust law, we find a median attenuation of $A_V=0.4$~mag.
 
@@
   \oii~$\lambda3727$, H$\beta$~$\lambda4861$, and \oiii~$\lambda5007$
-  emission lines.  The panels on the right zoom on the
+  emission lines.  The panels on the right highlight the
   \mgii~$\lambda\lambda2796,2803$ spectral region in both wavelength
-  and velocity space.  The spectrum in the bottom panel has sufficient
-  spectral resolution ($\textnormal{FWHM}\approx8$~\kms) to resolve
-  the intrinsic shape of the absorption-line profile, revealing that
-  the gas near the centroid velocity has unity covering factor.}
+  and velocity space to illustrate the outflow kinematics.  The
+  spectrum in the bottom panel has sufficient spectral resolution
+  ($\textnormal{FWHM}\approx8$~\kms) to resolve the intrinsic shape of
+  the absorption-line profile, revealing that the gas near the
+  centroid velocity ($v=-2470$~\kms) covers the entire galaxy.}
 \label{fig:spectra}
@@
   proportional to outflow velocity), along with samples of gas-rich
-  mergers (orange squares) and star-forming galaxies (shown with 68\%
-  contours).  We mark the empirical threshold for launching winds
-  \citep[dotted line, $\sigmasfr=0.1$~\units;][]{hec02}, the
-  90th-percentile starburst intensity limit from \citet{meu97} (dashed
-  line, $\sigmasfr=45$~\units), and the Eddington limit from radiation
+  mergers (orange squares) and star-forming galaxies (shown with 68\%,
+  95\%, and 99.7\% contours).  We mark the empirical threshold for
+  launching winds \citep[dotted line,
+    $\sigmasfr\approx0.1$~\units;][]{hec02}, the 90th-percentile
+  starburst intensity limit from \citet{meu97} (dashed line,
+  $\sigmasfr\approx45$~\units), and the Eddington limit from radiation
   pressure on dust grains \citep[solid line,
@@
   mergers, and extends to very large SFR surface densities near the
-  Eddington limit.  The sample of gas-rich mergers includes ULIRGs
-  \citep{vei06}, Lyman break analogs with dominant central objects
-  \citep{ove09}, and the local compact starburst Arp 220 \citep{sco97,
-    ken98, rod08}.  The samples of star-forming galaxies are drawn
-  from \citet{wuy11} at $0.02<z<0.2$ (solid black contour),
-  $0.5<z<1.5$ (dashed red countour), and $1.5<z<2.5$ (dotted purple
-  contour), and from \citet{law12} at $2.5<z<3.6$ (dash-dotted blue
-  contour). }
+  Eddington limit, suggesting growth that is limited by momentum
+  injection from massive stars.}
 \label{fig:sigmasfr}
@@
 
-\subsection{Optical Spectroscopy}
+% The sample of gas-rich mergers includes ULIRGs
+%   \citep{vei06}, Lyman break analogs with dominant central objects
+%   \citep{ove09}, and the local compact starburst Arp 220 \citep{sco97,
+%     ken98, rod08}.  The samples of star-forming galaxies are drawn
+%   from \citet{wuy11} at $0.02<z<0.2$ (solid black contour),
+%   $0.5<z<1.5$ (dashed red countour), and $1.5<z<2.5$ (dotted purple
+%   contour), and from \citet{law12} at $2.5<z<3.6$ (dash-dotted blue
+%   contour).
 
-We present low-resolution $R=1000-3000$ spectroscopy from MMT/Blue
-Channel and SDSS (J1506+5402), Magellan/MagE (J1341-0321), and
-Keck/LRIS (J0905+5759) in Figure~\ref{fig:spectra.}.  We also
-highlight the \mgii~$\lambda\lambda2796,2803$ absorption lines, which
-are used use to measure outflow velocities.
+%\subsection{Optical Spectroscopy}
+\subsection{Outflow Kinematics and Covering Factors}
 
-For J0905+5759 we show the \mgii\ absorption-line profiles from
-$R\approx37,000$ spectra obtained with Keck/HIRES.  The oscillator
-strength of \mgii~$\lambda$2796 is twice that of \mgii~$\lambda$2803,
-but the equivalent widths of the two lines and the shapes of the line
-profiles are quite similar, indicating that both lines are optically
-thick.  The fact that the absorption line profile approaches zero near
-the velocity centroid $v=-2470$~\kms\ indicates that the outflowing
-gas covers the entire continuum source at these velocities.
+We present $\lrest=2500$--5200~\AA\ spectroscopy for three
+high-$\sigmasfr$ sources in Figure~\ref{fig:spectra} based on data
+from MMT/Blue Channel and SDSS (J1506+5402), Magellan/MAGE
+(J1341-0321), and Keck/LRIS and Keck/HIRES (J0905+5759).  The spectra
+are dominated by light from the young ($t<50$~Myr) stellar population.
+We highlight the \mgii~$\lambda\lambda2796,2803$ absorption lines,
+which are used used to measure outflow velocities.  At low spectral
+resolution (e.g., the top right panel of Figure~\ref{fig:spectra}) it
+is not possible to determine the intrinsic shape of the absorption
+line profile and therefore the covering factor of the outflowing gas.
+However, the Keck/HIRES spectrum of J0905+5759
+($\textnormal{FWHM}\approx8$~\kms) reveals that the gas covers the
+entire continuum source near the velocity centroid ($v=-2470$~\kms)
+indicating a galaxy-wide outflow.
+
+% MMT/Blue Channel (J1506+5402, $R\sim1000$), SDSS (J1506+5402,
+% $R\sim2000$), Magellan/MAGE (J1341-0321, $R\sim4000$), Keck/LRIS
+% (J0905+5759, $R\sim600$), and Keck/HIRES (J0905+5759, $R\sim37,000$)
 
@@
 The compact sizes ($r_e\approx100$~pc) and large star formation rates
-($\textnormal{SFR}\approx500$~\msun) for the galaxies shown in
-Figure~\ref{fig:seds} imply extremely large star-formation rate
-surface densities ($\sigmasfr\approx5000$~\units).  To place these
-galaxies in context, we plot their $\sigmasfr$ values as a function of
-stellar mass in Figure~\ref{fig:sigmasfr}.  We also include
-measurements of late-stage, gas-rich mergers at $z<0.3$ from
-\citet{vei06}, star-forming galaxies at $z<0.3$ from \citet{ove09},
-and star-forming galaxies at $z=1.5$--3.6 from \citet{law12}.
+($\textnormal{SFR}\approx500$~\msun) for the galaxies described above
+implies extremely large star-formation rate surface densities
+($\sigmasfr\approx5000$~\units).  To place these galaxies in context,
+we plot their $\sigmasfr$ values as a function of stellar mass in
+Figure~\ref{fig:sigmasfr}.  We include comparison samples of
+$\sim10^5$ star-forming galaxies at $0.5<z<1.5$ from \citet{wuy11} and
+a few dozen gas-rich mergers at $z<0.3$ including 32 ULIRGs from
+\citet{vei06}, five Lyman break analogs with dominant central objects
+from \citet{ove09}, and the local compact starburst Arp 220
+\citep{sco97, ken98, rod08}.  We also mark the empirical threshold for
+launching winds \citep[$\sigmasfr\approx0.1$~\units,][]{hec02}, the
+90th percentile limit for the surface brightness of starbursts
+measured using UV, H$\alpha$, far-IR, and radio continuum emission
+\citep[$\sigmasfr\approx45$~\units][]{meu97}, and the theoretical
+limit for a starburst limited by feedback from radiation pressure
+\citep[$\sigmasfr\approx2000$~\units,][]{mur05,tho05,hop10}.  The most
+luminous, compact starbursts in our sample exhibit SFR surface
+densities that reach the Eddington limit, suggesting that their growth
+is being regulated by momentum input from massive stars.
 
-Points to make:
-\begin{itemize}
-\item \citet{ken98}, the standard reference for the relationship
-  between SFR and gas surface density, includes Arp 200 with
-  $\sigmasfr\approx10^3$~\units\ and
-  $\Sigma_{H_2}\approx5\times10^{10}$~\msun~kpc$^{-2}$.  
-\item The star clusters considered by \citet{meu97} extend into this
-  $\sigmasfr>10^{3}$~\units\ range.
+%  We also include measurements of
+% late-stage, gas-rich mergers at $z<0.3$ from \citet{vei06},
+% star-forming galaxies at $z<0.3$ from \citet{ove09}, and star-forming
+% galaxies at $z=1.5$--3.6 from \citet{law12}.
 
-\end{itemize}
+% Points to make:
+% \begin{itemize}
+% \item \citet{ken98}, the standard reference for the relationship
+%   between SFR and gas surface density, includes Arp 200 with
+%   $\sigmasfr\approx10^3$~\units\ and
+%   $\Sigma_{H_2}\approx5\times10^{10}$~\msun~kpc$^{-2}$.  
+% \item The star clusters considered by \citet{meu97} extend into this
+%   $\sigmasfr>10^{3}$~\units\ range.
+% 
+% \end{itemize}
 
@@
 %\subsection{A Maximum Star-Formation Rate Surface Density?}
+
+%\section{Discussion}
+
+\subsection{Constraints on Ongoing AGN Activity}
+
+While the SEDs (see Figure~\ref{fig:seds}) and optical spectra (see
+Figure~\ref{fig:spectra}) for our sample indicate that their
+bolometric output is dominated by star formation, it is worthwhile to
+consider the amount of ongoing AGN activity in these systems.  The
+strongest case for detectable AGN emission among the high-$\sigmasfr$
+galaxies can be made for J1506+5402, which has a weak
+\nev~$\lambda3426$ emission line typically associated with AGN
+activity \citep[e.g., ][]{abe08}.  This galaxy was observed with the
+Chandra X-ray Observatory (proposal ID 11700896, PI: C. Tremonti) and
+had four detected counts, corresponding to a 0.5--8.0~keV X-ray
+luminosity of $10^{42.7}$~erg~s$^{-1}$ (see P. Sell et al., in
+preparation for more details on the 12/29 galaxies with Chandra
+observations).  Using the relationship between 2--10~keV X-ray and
+12.3~$\mu$m mid-IR luminosity for AGNs from \citet{gan09}, one would
+expect a source with
+$L_{\textnormal{\scriptsize{X}}}\approx5\times10^{42}$~erg~s$^{-1}$ to
+have
+$L_{\textnormal{\scriptsize{MIR}}}\approx7\times10^{42}$~erg~s$^{-1}$,
+which is 400$\times$ smaller than observed luminosity for J1506+5402,
+$L_{\textnormal{\scriptsize{MIR}}}\approx3\times10^{45}$~erg~s$^{-1}$.
+If this source were Compton-thick \citep[e.g., the typical 2--10~keV
+  attenuation for local Compton-thick AGNs is a factor of
+  100;][]{dia09}, then the expected mid-IR AGN contribution could be
+relevant at the $\lesssim$30\% level, but this would not affect our
+conclusions that this galaxy is starburst dominated with a $\sigmasfr$
+value near the Eddington limit.  As is the case for typical ULIRGs
+\citep[e.g.,][]{far07}, there is certainly evidence for AGN activity
+in a fraction of our sample, but the bolometric output is dominated by
+star formation.
+
+% No evidence in spectra for unobscured AGN component.  J1506+5402 has
+% X-ray and \nev.  Agreement between SFR indicators.  Mention Balmer
+% lines and dust geometry.  SEDs well fit by star-forming tempates.
+% Most ULIRGs are starburst dominated.  Mention Pauls's paper.  There is
+% likely some ongoing AGN activity in sources like J1506+5402, but in
+% general, the AGN does not seem to be relevant energetically.  Point
+% that high-velocity outflows don't mean that an outflow is AGN driven.
+
+\subsection{The Outflow Launching Mechanism}
 
@@
 
-Question of whether other observables are plausible.  
-\begin{itemize}
-\item Expected velocity dispersion.  Some results have suggested that
-  turbulence becomes large at high surface densities, and therefore
-  the velocity dispersion should be large.  
-\item The dynamical time for the starburst.  If gas is consumed with
-  an efficiency of a few \% per dynamical time, how long do we expect
-  the starburst to last?
-\end{itemize}
-
-Other points: 
-\begin{itemize}
-\item Is this mechanism viable for the whole sample?  We see large
-  outflow velocities in rest of the sample, where the galaxies are
-  more ``post'' starburst.  This fits in a scenario where the genuine
-  post-starbursts are further along in the evolution after the outflow
-  quenches star formation.
-\item Will these evolve into ellipticals, or do they have enough gas
-  to reform a disk?  If they do quench, how difficult would it be to
-  grow in size to match the local size--mass relationship?  Could
-  their descendants be the handful of local galaxies that don't lie on
-  the size--mass relationship?
-\item Is there disagreement between $L_{IR}+L_{UV}$ and H$\alpha$
-  SFRs?  \citet{hec11} pointed out that this could be a sign of
-  escaping ionizing photons.
-\end{itemize}
-
-\subsection{Limits on Ongoing AGN Activity}
-
-No evidence in spectra for unobscured AGN component.  J1506+5402 has
-X-ray and \nev.
+% Question of whether other observables are plausible.  
+% \begin{itemize}
+% \item Expected velocity dispersion.  Some results have suggested that
+%   turbulence becomes large at high surface densities, and therefore
+%   the velocity dispersion should be large.  
+% \item The dynamical time for the starburst.  If gas is consumed with
+%   an efficiency of a few \% per dynamical time, how long do we expect
+%   the starburst to last?
+% \end{itemize}
+% 
+% Other points: 
+% \begin{itemize}
+% \item Is this mechanism viable for the whole sample?  We see large
+%   outflow velocities in rest of the sample, where the galaxies are
+%   more ``post'' starburst.  This fits in a scenario where the genuine
+%   post-starbursts are further along in the evolution after the outflow
+%   quenches star formation.
+% \item Will these evolve into ellipticals, or do they have enough gas
+%   to reform a disk?  If they do quench, how difficult would it be to
+%   grow in size to match the local size--mass relationship?  Could
+%   their descendants be the handful of local galaxies that don't lie on
+%   the size--mass relationship?
+% \item Is there disagreement between $L_{IR}+L_{UV}$ and H$\alpha$
+%   SFRs?  \citet{hec11} pointed out that this could be a sign of
+%   escaping ionizing photons.
+% \end{itemize}
 
@@
 
-They are rare and thus represent an unusual or short-lived phase.
+They are rare and thus represent an unusual or short-lived phase.  Gas
+consumption time for starbursts.  Connection to ellipticals.
+Conceivable that they could grown in size sufficiently by $z=0$?
 
@@
 
-Connection to ellipticals.  Conceivable that they could grown in size
-sufficiently by $z=0$?
+\section{Conclusions}
 
@@
   182, 543
+\bibitem[Abel \& Satyapal(2008)]{abe08} Abel, N.~P., \& Satyapal,
+  S.\ 2008, \apj, 678, 686
 % \bibitem[Baldwin et al.(1981)]{bal81} Baldwin, J.~A., Phillips, M.~M.,
@@
   C.-P.\ 2012, \mnras, 420, 2221
+\bibitem[Diamond-Stanic et al.(2009)]{dia09} Diamond-Stanic, A.~M.,
+  Rieke, G.~H., \& Rigby, J.~R.\ 2009, \apj, 698, 623
 \bibitem[Di Matteo et al.(2005)]{dim05} Di Matteo, T., Springel, V.,
   \& Hernquist, L.\ 2005, \nat, 433, 604
+\bibitem[Elbaz et al.(2011)]{elb11} Elbaz, D., Dickinson, M., Hwang,
+  H.~S., et al.\ 2011, \aap, 533, A119
+\bibitem[Farrah et al.(2007)]{far07} Farrah, D., Bernard-Salas, J.,
+  Spoon, H.~W.~W., et al.\ 2007, \apj, 667, 149
 \bibitem[Fazio et al.(2004)]{faz04} Fazio, G.~G., Hora, J.~L., Allen,
   L.~E., et al.\ 2004, \apjs, 154, 10
+\bibitem[Gandhi et al.(2009)]{gan09} Gandhi, P., Horst, H., Smette,
+  A., et al.\ 2009, \aap, 502, 457
 \bibitem[Granato et al.(2004)]{gra04} Granato, G.~L., De Zotti, G.,

### 2012-04-18 trunk/tex/sigmasfr/ms.tex
revisions to section 3.1

@@
 
-While the SEDs (see Figure~\ref{fig:seds}) and optical spectra (see
-Figure~\ref{fig:spectra}) for our sample indicate that their
+While the SEDs (Figure~\ref{fig:seds}) and optical spectra
+(Figure~\ref{fig:spectra}) for our sample indicate that their
 bolometric output is dominated by star formation, it is worthwhile to
-consider the amount of ongoing AGN activity in these systems.  The
-strongest case for detectable AGN emission among the high-$\sigmasfr$
-galaxies can be made for J1506+5402, which has a weak
-\nev~$\lambda3426$ emission line typically associated with AGN
-activity \citep[e.g., ][]{abe08}.  This galaxy was observed with the
-Chandra X-ray Observatory (proposal ID 11700896, PI: C. Tremonti) and
-had four detected counts, corresponding to a 0.5--8.0~keV X-ray
-luminosity of $10^{42.7}$~erg~s$^{-1}$ (see P. Sell et al., in
-preparation for more details on the 12/29 galaxies with Chandra
-observations).  Using the relationship between 2--10~keV X-ray and
-12.3~$\mu$m mid-IR luminosity for AGNs from \citet{gan09}, one would
-expect a source with
+consider the level of ongoing AGN activity and its effect on our
+measurements.  Among the high-$\sigmasfr$ galaxies, the strongest case
+for detectable AGN emission can be made for J1506+5402, which has the
+most luminous \oiii~$\lambda5007$ line among the 29 galaxies observed
+by HST.  This source also has a weak \nev~$\lambda3426$ emission line,
+which is associated with AGN activity \citep[e.g.,][]{abe08,gil10}.
+It was observed with the Chandra X-ray Observatory (proposal ID
+11700896, PI: C. Tremonti) and had four detected counts, corresponding
+to a 0.5--8.0~keV X-ray luminosity of $10^{42.7}$~erg~s$^{-1}$ (see
+P. Sell et al., in preparation for more details on the 12/29 galaxies
+with Chandra observations).  Using the relationship between 2--10~keV
+X-ray and 12.3~$\mu$m mid-IR luminosity for AGNs from \citet{gan09},
+one would expect a source with
 $L_{\textnormal{\scriptsize{X}}}\approx5\times10^{42}$~erg~s$^{-1}$ to
@@
 $L_{\textnormal{\scriptsize{MIR}}}\approx7\times10^{42}$~erg~s$^{-1}$,
-which is 400$\times$ smaller than observed luminosity for J1506+5402,
-$L_{\textnormal{\scriptsize{MIR}}}\approx3\times10^{45}$~erg~s$^{-1}$.
-If this source were Compton-thick \citep[e.g., the typical 2--10~keV
-  attenuation for local Compton-thick AGNs is a factor of
-  100;][]{dia09}, then the expected mid-IR AGN contribution could be
-relevant at the $\lesssim$30\% level, but this would not affect our
-conclusions that this galaxy is starburst dominated with a $\sigmasfr$
-value near the Eddington limit.  As is the case for typical ULIRGs
-\citep[e.g.,][]{far07}, there is certainly evidence for AGN activity
-in a fraction of our sample, but the bolometric output is dominated by
-star formation.
+which is 400$\times$ smaller than observed luminosity for J1506+5402
+($L_{\textnormal{\scriptsize{MIR}}}\approx3\times10^{45}$~erg~s$^{-1}$).
+Based on its \oiii\ luminosity ($10^{42.1}$~erg~s$^{-1}$, a
+significant fraction of which could be attributed to star formation)
+and the calibration for type 1 AGNs from \citet{hec05}, one would
+expect an intrinsic 2--10~keV luminosity of
+$L_{\textnormal{\scriptsize{X}}}\approx5\times10^{43}$~erg~s$^{-1}$,
+suggesting absorption by a factor of $\sim10$ in the X-rays.  However,
+even if the X-ray attenuation were a factor of 100, which is the
+typical value for local Compton-thick AGNs \citep{dia09}, the expected
+mid-IR AGN contribution would only be relevant at the $\lesssim$30\%
+level.  Similar to local ULIRGs \citep[e.g.,][]{far07}, the bolometric
+output of the galaxies in our sample is dominated by star formation,
+and our conclusions regarding large $\sigmasfr$ values are not
+affected by AGN contamination.
+
+% ased on its \oiii\ luminosity $L(\oiii)=10^{42.1}$~erg~s$^{-1}$, the
+% expected X-ray luminosity \citep[adopting the relationship between
+%   \oiii\ and X-ray luminosity for type 1 AGNs from][]{hec05}
 
@@
   A., et al.\ 2009, \aap, 502, 457
+\bibitem[Gilli et al.(2010)]{gil10} Gilli, R., Vignali, C., Mignoli,
+  M., et al.\ 2010, \aap, 519, A92
 \bibitem[Granato et al.(2004)]{gra04} Granato, G.~L., De Zotti, G.,
@@
   at Low Redshift, 254, 292
+\bibitem[Heckman et al.(2005)]{hec05} Heckman, T.~M., Ptak, A.,
+  Hornschemeier, A., \& Kauffmann, G.\ 2005, \apj, 634, 161
 \bibitem[Heckman et al.(2011)]{hec11} Heckman, T.~M., et al.\ 2011,

### 2012-04-19 tex/sigmasfr/ms.tex
edits to section 3.2

@@
 compare to the profiles of six stars in the same image, the best-fit
-de Vaucouleurs model, and a de Vaucoulerus model with a larger
+de Vaucouleurs model, and a de Vaucouleurs model with a larger
 effective radius ($r_e=0.04\arcsec$, the native WFC3/UVIS pixel size,
@@
 detections, this yields SFRs that agree with those obtained from the
-\citet{ruj12} method based on 24~$\mu$m luminosity (with a scatter of
-0.05~dex).  We note that several authors have shown that the shape of
+\citet{ruj12} method based on 24~$\mu$m luminosity with a scatter of
+0.05~dex.  We note that several authors have shown that the shape of
 the IR SED for star-forming galaxies depends on the surface density of
@@
 luminous galaxies in the local universe
-\citep[e.g.,][]{cha01,dal02,rie09}.  For the 8/29 sources with SFRs in
-the ULIRG regime ($\sfrir>200$~\msun~yr$^{-1}$), we would obtain SFRs
-that are larger by 0.5~dex (compared to the values obtained above) if
-we used the most luminous local templates.
+\citep[e.g.,][]{cha01,dal02,rie09}.  If we used the most luminous
+local templates for the 8/29 sources with SFRs in the ULIRG regime
+($\sfrir>200$~\msun~yr$^{-1}$), we would obtain SFRs that are larger
+by 0.5~dex than the values we adopt for this paper.
 
@@
 $\sfrir>50$~\msun~yr$^{-1}$, there is agreement between these UV-based
-SFR estimates and $\sfrir$ with a scatter of 0.32~dex.  We find a
-median extinction of $A_V=0.4$~mag for an SMC-based dust law.
+SFR estimates and $\sfrir$ with a scatter of 0.32~dex.  For an SMC
+dust law, we find a median attenuation of $A_V=0.4$~mag.
 
@@
 
-\subsection{Momentum Flux from Supernovae and Stellar Winds}
+%\section{Discussion}
 
-\citet{meu97} argued for a limit near 45~\units (somewhat smaller for
-a Chabrier IMF) based on the surface brightness of starbursts measured
-using rest-frame UV, H$\alpha$, far-IR, and radio continuum emission,
-such that only 10\% of starbursts exceeded this limit.  They argued
-that the momentum flux from supernovae and stellar winds expected at
-this threshold matches the mean central pressure measured by
-\citet{hec90} for starburst-driven winds.
+\subsection{Constraints on Ongoing AGN Activity}
 
-There are also relevant arguments about ram pressure driving of
-high-velocity winds from \citet{hec11}.
+While the SEDs (Figure~\ref{fig:seds}) and optical spectra
+(Figure~\ref{fig:spectra}) for our sample indicate that their
+bolometric output is dominated by star formation, it is worthwhile to
+consider the level of ongoing AGN activity and its effect on our
+measurements.  Among the high-$\sigmasfr$ galaxies, the strongest case
+for detectable AGN emission can be made for J1506+5402, which has the
+most luminous \oiii~$\lambda5007$ line among the 29 galaxies observed
+by HST.  This source also has a weak \nev~$\lambda3426$ emission line,
+which is associated with AGN activity \citep[e.g.,][]{abe08,gil10}.
+It was observed with the Chandra X-ray Observatory (proposal ID
+11700896, PI: C. Tremonti) and had four detected counts, corresponding
+to a 0.5--8.0~keV X-ray luminosity of $10^{42.7}$~erg~s$^{-1}$ (see
+P. Sell et al., in preparation for more details on the 12/29 galaxies
+with Chandra observations).  Using the relationship between 2--10~keV
+X-ray and 12.3~$\mu$m mid-IR luminosity for AGNs from \citet{gan09},
+one would expect a source with
+$L_{\textnormal{\scriptsize{X}}}\approx5\times10^{42}$~erg~s$^{-1}$ to
+have
+$L_{\textnormal{\scriptsize{MIR}}}\approx7\times10^{42}$~erg~s$^{-1}$,
+which is 400$\times$ smaller than observed luminosity for J1506+5402
+($L_{\textnormal{\scriptsize{MIR}}}\approx3\times10^{45}$~erg~s$^{-1}$).
+Based on its \oiii\ luminosity ($10^{42.1}$~erg~s$^{-1}$, a
+significant fraction of which could be attributed to star formation)
+and the calibration for type 1 AGNs from \citet{hec05}, one would
+expect an intrinsic 2--10~keV luminosity of
+$L_{\textnormal{\scriptsize{X}}}\approx5\times10^{43}$~erg~s$^{-1}$,
+suggesting absorption by a factor of $\sim10$ in the X-rays.  However,
+even if the X-ray attenuation were a factor of 100, which is the
+typical value for local Compton-thick AGNs \citep{dia09}, the expected
+mid-IR AGN contribution would only be relevant at the $\lesssim$30\%
+level.  Thus, similar to local ULIRGs \citep[e.g.,][]{far07}, the
+bolometric output of the galaxies in our sample is dominated by star
+formation, and we conclude that our results regarding large
+$\sigmasfr$ values are not affected by AGN contamination.
 
-\subsection{The Eddington Limit from Radiation Pressure on Dust Grains}
+% ased on its \oiii\ luminosity $L(\oiii)=10^{42.1}$~erg~s$^{-1}$, the
+% expected X-ray luminosity \citep[adopting the relationship between
+%   \oiii\ and X-ray luminosity for type 1 AGNs from][]{hec05}
 
-In models where gaseous outflows are driven by radiation pressure from
-massive stars, estimates of the maximum $\sigmasfr$ where the outward
-force from radiation exceeds the inward force of gravity are in the
-$\sigmasfr\sim10^3$~\units\ range \citep[e.g.,][]{tho05,hop10}.
+% No evidence in spectra for unobscured AGN component.  J1506+5402 has
+% X-ray and \nev.  Agreement between SFR indicators.  Mention Balmer
+% lines and dust geometry.  SEDs well fit by star-forming tempates.
+% Most ULIRGs are starburst dominated.  Mention Pauls's paper.  There is
+% likely some ongoing AGN activity in sources like J1506+5402, but in
+% general, the AGN does not seem to be relevant energetically.  Point
+% that high-velocity outflows don't mean that an outflow is AGN driven.
+
+\subsection{The Outflow Launching Mechanism}
+
+It is worth considering whether the high-velocity outflows we observe
+were produced by the compact starburst.  \citet{mur11} argued that
+massive star clusters with large gas surface densities are the ideal
+launching point for galactic-scale outflows driven by radiation
+pressure, and that the outflow velocity should scale with escape
+velocity of the most massive star clusters in a galaxy.  The
+$\gtrsim1000$~\kms\ outflow velocities we observe correspond
+approximately to the escape velocities for a compact stellar
+population with the sizes and masses that we've measured.
+\begin{eqnarray}\nonumber
+v_{esc}&=&\sqrt{2GM_{*}/r} \\
+&=& 2100
+\left({M_{*}\over10^{11} M_{\odot}}\right)^{1/2} 
+\left({r\over200~\textnormal{pc}}\right)^{-1/2}
+\textnormal{km~s}^{-1} 
+\label{eq:vesc}
+\end{eqnarray}
+This argument, combined with the fact that we observe galaxies with
+significant dust-obscured star formation and $\sigmasfr$ values near
+the Eddington limit, indicates that momentum input from massive stars
+in the form of radiation pressure is a viable mechanism for launching
+these outflows.
+
+In addition to radiation pressure, we also expect significant momentum
+flux from stellar winds and supernovae.  For example, a starburst with
+$\textnormal{SFR}\approx200$~\msun~yr$^{-1}$ would be associated with
+radiation pressure $L_{bol}/c\approx2\times10^{35}$~dyne and ram
+pressure $\dot{p}\approx5$--$10\times10^{35}$~dyne from stellar winds
+and supernovae \citep[e.g.,][]{lei92,hec93,lei99,vei05}.  Furthermore,
+\citet{hec11} noted that such a large momentum injection
+($\dot{p}\approx10^{35}$~dyne) from a small initial radius
+$r_{0}\approx100$~pc could accelerate a cloud with column density
+$N_{H}\approx10^{21}$~cm$^{-2}$ to a terminal velocity
+$v_{\infty}\approx1800$~\kms.  Thus, the energetics of compact
+starbursts are sufficient to produce the high-velocity outflows we
+observe, and it is plausible that both radiation pressure on dust
+grains and supernova ram pressure contribute to driving the winds.
+
+% Following \citet{hec93} and
+% \citet{hec11}, the expected terminal velocity for a cloud with column
+% density $\approx10^{21}$~cm$^{-2}$ launched from a radius
+% $\approx200$~pc and driven by momentum flux
+% $\approx2\times10^{35}$~dynes is:
+% \begin{eqnarray}\nonumber
+% v_{\infty}&=&1800~\textnormal{km~s}^{-1}
+% \left(\dot{p}\over2\times10^{35}~\textnormal{dyne}\right)^{1/2} \\
+% &&
+% \left({r\over200~\textnormal{pc}}\right)^{-1/2}
+% \left({N\over10^{21}~\textnormal{cm}^{-2}}\right)^{-1/2}
+% \label{eq:vterm}
+% \end{eqnarray}
+% The expected momentum flux from stellar winds and supernovae for a
+% starburst with $\textnormal{SFR}\approx200$~\msun~yr$^{-1}$ is
+% $\approx5$--$10\times10^{35}$~dynes \citep{lei92,hec93,lei99,vei05}
+% while the $L_{bol}/c$ radiation pressure is
+% $\approx2\times10^{35}$~dynes.  Thus, there is more than enough
+% momentum available from stellar winds and supernovae or from radiation
+% pressure to produce the outflow velocities we observe.
+
+%AGN have been invoked to launch high-velocity winds.
+
+% \subsection{Momentum Flux from Supernovae and Stellar Winds}
+% 
+% \citet{meu97} argued for a limit near 45~\units (somewhat smaller for
+% a Chabrier IMF) based on the surface brightness of starbursts measured
+% using rest-frame UV, H$\alpha$, far-IR, and radio continuum emission,
+% such that only 10\% of starbursts exceeded this limit.  They argued
+% that the momentum flux from supernovae and stellar winds expected at
+% this threshold matches the mean central pressure measured by
+% \citet{hec90} for starburst-driven winds.
+% 
+% There are also relevant arguments about ram pressure driving of
+% high-velocity winds from \citet{hec11}.
+% 
+% 
+% \subsection{The Eddington Limit from Radiation Pressure on Dust Grains}
+
+% In models where gaseous outflows are driven by radiation pressure from
+% massive stars, estimates of the maximum $\sigmasfr$ where the outward
+% force from radiation exceeds the inward force of gravity are in the
+% $\sigmasfr\sim10^3$~\units\ range \citep[e.g.,][]{tho05,hop10}.
 
@@
 
-The relative importance of momentum injection versus thermal heating
-may vary as a function of galaxy mass \citep[e.g.,][]{hop12}, with
-thermal heating being less efficient in galaxies with larger gas
-densities and shorter cooling times.  Regarding momentum injection,
-\citet{sha11} have argued that radiation pressure becomes more
-important than ram pressure at large SFRs.  Massive star clusters with
-large gas surface densities are the ideal launching point for
-galactic-scale outflows driven by radiation pressure
-\citep[e.g.,][]{mur11}, and the outflow velocities are expected to
-scale with escape velocity of the most massive star clusters in a
-galaxy.
+% The relative importance of momentum injection versus thermal heating
+% may vary as a function of galaxy mass \citep[e.g.,][]{hop12}, with
+% thermal heating being less efficient in galaxies with larger gas
+% densities and shorter cooling times.  Regarding momentum injection,
+% \citet{sha11} have argued that radiation pressure becomes more
+% important than ram pressure at large SFRs.
 
-\subsection{Outflows at the Escape Velocity}
-
-The observed $\gtrsim1000$~\kms\ outflow velocities we observe correspond
-approximately to the escape velocities for compact regions (i.e.,
-massive star clusters) with the sizes and masses that we've measured.
-
-\begin{equation}
-v_{esc} = \sqrt{2GM_{cl}/r_{cl}} = 2074~\textnormal{km~s}^{-1} \\%\left({v_c\over200}\right)^{5/2} 
-\left({M_{cl}\over10^{11} M_{\odot}}\right)^{1/2} 
-\left({r_{cl}\over200~\textnormal{pc}}\right)^{-1/2}
-\label{eq:vesc}
-\end{equation}
+%\subsection{Outflows at the Escape Velocity}
 
@@
 
-Connection to ellipticals.  Conceivable that they could grown in size
-sufficiently by $z=0$?
+High-velocity outflows do not imply AGN feedback.
+
+Theoretical arguments about ram v. radiation pressure.  Point that we
+are observing 10$^4$~K gas.
+
+Sample as a whole. Interesting that high-$\sigmasfr$ galaxies tend to
+have larger outflow velocities.
+
+\section{Conclusions}
 
@@
   C.-P.\ 2012, \mnras, 420, 2221
+\bibitem[Diamond-Stanic et al.(2009)]{dia09} Diamond-Stanic, A.~M.,
+  Rieke, G.~H., \& Rigby, J.~R.\ 2009, \apj, 698, 623
 \bibitem[Di Matteo et al.(2005)]{dim05} Di Matteo, T., Springel, V.,
@@
   H.~S., et al.\ 2011, \aap, 533, A119
+\bibitem[Farrah et al.(2007)]{far07} Farrah, D., Bernard-Salas, J.,
+  Spoon, H.~W.~W., et al.\ 2007, \apj, 667, 149
 \bibitem[Fazio et al.(2004)]{faz04} Fazio, G.~G., Hora, J.~L., Allen,
   L.~E., et al.\ 2004, \apjs, 154, 10
+\bibitem[Gandhi et al.(2009)]{gan09} Gandhi, P., Horst, H., Smette,
+  A., et al.\ 2009, \aap, 502, 457
+\bibitem[Gilli et al.(2010)]{gil10} Gilli, R., Vignali, C., Mignoli,
+  M., et al.\ 2010, \aap, 519, A92
 \bibitem[Granato et al.(2004)]{gra04} Granato, G.~L., De Zotti, G.,
@@
   Miley, G.~K.\ 1990, \apjs, 74, 833
+\bibitem[Heckman et al.(1993)]{hec93} Heckman, T.~M., Lehnert, M.~D.,
+  \& Armus, L.\ 1993, The Environment and Evolution of Galaxies, 188,
+  455
 \bibitem[Heckman et al.(2000)]{hec00} Heckman, T.~M., Lehnert, M.~D.,
@@
   Drissen, L.\ 1992, \apj, 401, 596
+\bibitem[Leitherer et al.(1999)]{lei99} Leitherer, C., Schaerer, D.,
+  Goldader, J.~D., et al.\ 1999, \apjs, 123, 3
 \bibitem[Martin(2005)]{mar05} Martin, C.~L.\ 2005, \apj, 621, 227
@@
 %   \procspie, 2198, 362
+\bibitem[Veilleux et al.(2005)]{vei05} Veilleux, S., Cecil, G., \&
+  Bland-Hawthorn, J.\ 2005, \araa, 43, 769
 \bibitem[Veilleux et al.(2006)]{vei06} Veilleux, S., Kim, D.-C., Peng,

### 2012-04-19 trunk/tex/sigmasfr/ms.tex
edits to section 3.2

@@
 implied star formation rate (SFR) surface densities approach
-$\sigmasfr=5000$~\msun~yr$^{-1}$~kpc$^{-2}$, and we argue that
-feedback associated with this starburst event is a likely mechanism
-for launching the high-velocity outflows.
+$\sigmasfr\approx5000$~\msun~yr$^{-1}$~kpc$^{-2}$, comparable to the
+Eddington limit for a starburst where radiation pressure on dust
+grains overcomes gravity.  We argue that feedback associated with this
+starburst event, in the form of radiation pressure and supernova ram
+pressure, is a likely mechanism for launching the high-velocity
+outflows.
 
@@
 mid-IR AGN contribution would only be relevant at the $\lesssim$30\%
-level.  Similar to local ULIRGs \citep[e.g.,][]{far07}, the bolometric
-output of the galaxies in our sample is dominated by star formation,
-and our conclusions regarding large $\sigmasfr$ values are not
-affected by AGN contamination.
+level.  Thus, similar to local ULIRGs \citep[e.g.,][]{far07}, the
+bolometric output of the galaxies in our sample is dominated by star
+formation, and we conclude that our results regarding large
+$\sigmasfr$ values are not affected by AGN contamination.
 
@@
 
-\subsection{Momentum Flux from Supernovae and Stellar Winds}
+It is worth considering whether the high-velocity outflows we observe
+were produced by the compact starburst.  \citet{mur11} argued that
+massive star clusters with large gas surface densities are the ideal
+launching point for galactic-scale outflows driven by radiation
+pressure, and that the outflow velocity should scale with escape
+velocity of the most massive star clusters in a galaxy.  The
+$\gtrsim1000$~\kms\ outflow velocities we observe correspond
+approximately to the escape velocities for a compact stellar
+population with the sizes and masses that we've measured.
+\begin{eqnarray}\nonumber
+v_{esc}&=&\sqrt{2GM_{*}/r} \\
+&=& 2100
+\left({M_{*}\over10^{11} M_{\odot}}\right)^{1/2} 
+\left({r\over200~\textnormal{pc}}\right)^{-1/2}
+\textnormal{km~s}^{-1} 
+\label{eq:vesc}
+\end{eqnarray}
+This argument, combined with the fact that we observe galaxies with
+significant dust-obscured star formation and $\sigmasfr$ values near
+the Eddington limit, indicates that momentum input from massive stars
+in the form of radiation pressure is a viable mechanism for launching
+these outflows.
 
-\citet{meu97} argued for a limit near 45~\units (somewhat smaller for
-a Chabrier IMF) based on the surface brightness of starbursts measured
-using rest-frame UV, H$\alpha$, far-IR, and radio continuum emission,
-such that only 10\% of starbursts exceeded this limit.  They argued
-that the momentum flux from supernovae and stellar winds expected at
-this threshold matches the mean central pressure measured by
-\citet{hec90} for starburst-driven winds.
+In addition to radiation pressure, we also expect significant momentum
+flux from stellar winds and supernovae.  For example, a starburst with
+$\textnormal{SFR}\approx200$~\msun~yr$^{-1}$ would be associated with
+radiation pressure $L_{bol}/c\approx2\times10^{35}$~dyne and ram
+pressure $\dot{p}\approx5$--$10\times10^{35}$~dyne from stellar winds
+and supernovae \citep[e.g.,][]{lei92,hec93,lei99,vei05}.  Furthermore,
+\citet{hec11} noted that such a large momentum injection
+($\dot{p}\approx10^{35}$~dyne) from a small initial radius
+$r_{0}\approx100$~pc could accelerate a cloud with column density
+$N_{H}\approx10^{21}$~cm$^{-2}$ to a terminal velocity
+$v_{\infty}\approx1800$~\kms.  Thus, the energetics of compact
+starbursts are sufficient to produce the high-velocity outflows we
+observe, and it is plausible that both radiation pressure on dust
+grains and supernova ram pressure contribute to driving the winds.
 
-There are also relevant arguments about ram pressure driving of
-high-velocity winds from \citet{hec11}.
+% Following \citet{hec93} and
+% \citet{hec11}, the expected terminal velocity for a cloud with column
+% density $\approx10^{21}$~cm$^{-2}$ launched from a radius
+% $\approx200$~pc and driven by momentum flux
+% $\approx2\times10^{35}$~dynes is:
+% \begin{eqnarray}\nonumber
+% v_{\infty}&=&1800~\textnormal{km~s}^{-1}
+% \left(\dot{p}\over2\times10^{35}~\textnormal{dyne}\right)^{1/2} \\
+% &&
+% \left({r\over200~\textnormal{pc}}\right)^{-1/2}
+% \left({N\over10^{21}~\textnormal{cm}^{-2}}\right)^{-1/2}
+% \label{eq:vterm}
+% \end{eqnarray}
+% The expected momentum flux from stellar winds and supernovae for a
+% starburst with $\textnormal{SFR}\approx200$~\msun~yr$^{-1}$ is
+% $\approx5$--$10\times10^{35}$~dynes \citep{lei92,hec93,lei99,vei05}
+% while the $L_{bol}/c$ radiation pressure is
+% $\approx2\times10^{35}$~dynes.  Thus, there is more than enough
+% momentum available from stellar winds and supernovae or from radiation
+% pressure to produce the outflow velocities we observe.
 
-\subsection{The Eddington Limit from Radiation Pressure on Dust Grains}
+%AGN have been invoked to launch high-velocity winds.
 
-In models where gaseous outflows are driven by radiation pressure from
-massive stars, estimates of the maximum $\sigmasfr$ where the outward
-force from radiation exceeds the inward force of gravity are in the
-$\sigmasfr\sim10^3$~\units\ range \citep[e.g.,][]{tho05,hop10}.
+% \subsection{Momentum Flux from Supernovae and Stellar Winds}
+% 
+% \citet{meu97} argued for a limit near 45~\units (somewhat smaller for
+% a Chabrier IMF) based on the surface brightness of starbursts measured
+% using rest-frame UV, H$\alpha$, far-IR, and radio continuum emission,
+% such that only 10\% of starbursts exceeded this limit.  They argued
+% that the momentum flux from supernovae and stellar winds expected at
+% this threshold matches the mean central pressure measured by
+% \citet{hec90} for starburst-driven winds.
+% 
+% There are also relevant arguments about ram pressure driving of
+% high-velocity winds from \citet{hec11}.
+% 
+% 
+% \subsection{The Eddington Limit from Radiation Pressure on Dust Grains}
+
+% In models where gaseous outflows are driven by radiation pressure from
+% massive stars, estimates of the maximum $\sigmasfr$ where the outward
+% force from radiation exceeds the inward force of gravity are in the
+% $\sigmasfr\sim10^3$~\units\ range \citep[e.g.,][]{tho05,hop10}.
 
@@
 
+Few galaxies exhibit such high-velocity outflows because few galaxies
+have such extreme SFR surface densities.
+
 Connection to models.  How such large SFRs given the powerful wind?
+
+High-velocity outflows do not imply AGN feedback.
+
+Theoretical arguments about ram v. radiation pressure.  Point that we
+are observing 10$^4$~K gas.
+
+Sample as a whole. Interesting that high-$\sigmasfr$ galaxies tend to
+have larger outflow velocities.
+
+Mention high-$\sigmasfr$ galaxies at high z.
 

### 2012-04-19 trunk/tex/sigmasfr/ms.tex
working on discussion text

@@
 
-Based on infrared photometry from the Wide-field Infrared Survey
-Explorer (WISE) and optical morphologies from the Hubble Space
-Telescope (HST), we present the discovery of compact, obscured star
-formation in galaxies that exhibit $\gtrsim1000$~\kms\ outflows.  The
-implied star formation rate (SFR) surface densities approach
-$\sigmasfr\approx5000$~\msun~yr$^{-1}$~kpc$^{-2}$, comparable to the
-Eddington limit for a starburst where radiation pressure on dust
-grains overcomes gravity.  We argue that feedback associated with this
-starburst event, in the form of radiation pressure and supernova ram
-pressure, is a likely mechanism for launching the high-velocity
-outflows.
+We present the discovery of compact, obscured star formation in
+galaxies that exhibit $\gtrsim1000$~\kms\ outflows.  Using optical
+morphologies from the Hubble Space Telescope and infrared photometry
+from the Wide-field Infrared Survey Explorer, we estimate star
+formation rate (SFR) surface densities that approach
+$\sigmasfr\approx5000$~\msun~yr$^{-1}$~kpc$^{-2}$.  This is comparable
+to the Eddington limit from radiation pressure on dust grains.  We
+argue that feedback associated with a compact starburst in the form of
+radiation pressure from massive stars and ram pressure from supernovae
+and stellar winds is sufficient to launch the high-velocity outflows
+we observe, without the need to invoke feedback from an active
+galactic nucleus.
 
@@
 
-\keywords{keywords}
+\keywords{galaxies: evolution --- galaxies: kinematics and dynamics
+  --- galaxies: ISM --- galaxies: starburst}
 
@@
 \citep[e.g.,][]{sil98,dim05,deb12}, could have been responsible for
-launching the winds.
+launching the winds \citep[see][for a recent review]{fab12}.
 
@@
 The compact sizes ($r_e\approx100$~pc) and large star formation rates
-($\textnormal{SFR}\approx500$~\msun) for the galaxies described above
+($\textnormal{SFR}\approx300$~\msun) for the galaxies described above
 implies extremely large star-formation rate surface densities
@@
 
-They are rare and thus represent an unusual or short-lived phase.  Gas
-consumption time for starbursts.  Connection to ellipticals.
-Conceivable that they could grown in size sufficiently by $z=0$?
+The high-$\sigmasfr$ galaxies in our sample constitute a rare
+population (see Figure~\ref{fig:sigmasfr}), suggesting that they
+represent an unusual or short-lived phase.  Mergers of gas-rich
+galaxies are a viable mechanism for producing compact starbursts
+(e.g., Mihos+94), and such gas-rich major mergers are rare at
+$z\sim0.6$ due to the decline in both the merger rate and the gas
+fraction of galaxies since $z\sim1$.  The high-$\sigmasfr$ galaxies in
+particular are in a phase where there is strong feedback but star
+formation has not been quenched.  The length of this phase may be set
+by the gas consumption timescale or the timescale for feedback to
+suppress subsequent star formation.  Based on the Kennicutt--Schmidt
+(K-S) relation \citep{ken98}, a galaxy with $r_e\approx100$~pc,
+$\textnormal{SFR}\approx300$~\msun, and
+$\sigmasfr=5000$~\units\ (assuming half of the star formation occurs
+within the effective radius) would have a gas surface density of
+$\Sigma_{gas}\sim2\times10^5$~\msun~pc$^{-2}$, corresponding to
+$M_{gas}\sim5\times10^{9}$~\msun\ inside 100~pc, which would be
+consumed on a timescale $\sim30$~Myr.  It would be worthwhile to
+directly measure the molecular gas masses and kinematics of these
+extreme sources with CO observations to test this scenario.
+
+The vertical sequence in Figure~\ref{fig:sigmasfr} may be related to
+an evolutionary sequence, with the smaller $\sigmasfr$ galaxies being
+further along in their evolution towards a post-starburst phase.
+However, it is interesting to note that all 12/29 galaxies above the
+$\sigmasfr\approx45$~\units\ \citet{meu97} limit exhibit outflows
+(with median centroid velocity $v=-1500$~\kms), while all 7/29
+galaxies without detected outflows have $\sigmasfr<30$~\units.  If a
+compact starburst is a requirement for the production of high-velocity
+outflows, it may be that these latter sources have not gone through
+such a phase (see A. Robaina, et al, in preparation for a discussion
+of the relationship between outflow velocity, galaxy morphology, and
+stellar population age).
+
+% although simulations rarely produce starbursts that
+% are this compact.
+
+% While such major mergers are rare at $z\sim0.6$ \citep[e.g., the
+%   fraction of $M_{*}>3\times10^{10}$~\msun galaxies in $r<30$~kpc
+%   pairs is $\sim3$\%][]{bel06}, \citet{rob10} argued that such mergers
+% are sufficient to explain the number density evolution of massive red
+% sequence galaxies since $z\sim1$ \citep[e.g.,][]{fab07,bro07}.
+
+It is also worhwhile to consider the implications of these galaxies
+for models of massive galaxy formation.  Models do not produce
+starbursts this small.  Models that produce ellipticals have to invoke
+AGN feedback.  Models for size evolution would allow these galaxies to
+reach the size--mass relation by $z=0$.
+
+% A merger of two massive, gas-rich galaxies is a viable mechanism for
+% producing such a compact starburst (e.g., Mihos+94), but the
+% subsequent evolution depends on the assumed feedback prescriptions in
+% the model and the gas content of the progenitor galaxies.  It is
+% difficult for mergers to produce starbursts that are this compact.
+% Models can quench star formation by invoking AGN feedback,
 
@@
 
-Connection to models.  How such large SFRs given the powerful wind?
+% Connection to models.  How such large SFRs given the powerful wind?
 
@@
   H.~S., et al.\ 2011, \aap, 533, A119
+\bibitem[Fabian(2012)]{fab12} Fabian, A.~C.\ 2012,
+  arXiv:1204.4114
 \bibitem[Farrah et al.(2007)]{far07} Farrah, D., Bernard-Salas, J.,
@@
 %   K.~L.\ 2011, arXiv:1103.1891
+\bibitem[Robaina et al.(2010)]{rob10} Robaina, A.~R., Bell, E.~F., van
+  der Wel, A., et al.\ 2010, \apj, 719, 844
 \bibitem[Rodr{\'{\i}}guez Zaur{\'{\i}}n et al.(2008)]{rod08}

### 2012-04-20 trunk/tex/sigmasfr/ms.tex
updates to section 3.3

@@
 formation rate (SFR) surface densities that approach
-$\sigmasfr\approx5000$~\msun~yr$^{-1}$~kpc$^{-2}$.  This is comparable
+$\sigmasfr\approx5000$~\msun~yr$^{-1}$~kpc$^{-2}$, which is comparable
 to the Eddington limit from radiation pressure on dust grains.  We
@@
 radiation pressure from massive stars and ram pressure from supernovae
-and stellar winds is sufficient to launch the high-velocity outflows
+and stellar winds is sufficient to produce the high-velocity outflows
 we observe, without the need to invoke feedback from an active
@@
 % (\mgii~$\lambda2796$ is plotted in blue and \mgii~$\lambda2803$ is plotted in red)
+
+\begin{figure}[!t]
+%\includegraphics[angle=90,scale=0.68]{sigmasfr_datafigure.ps}
+\includegraphics[angle=0,scale=0.41]{3seds.ps}
+\caption{Left: Observed UV--IR SEDs ($\lrest=0.1$--15~$\mu$m) for
+  three galaxies with large SFR surface densities
+  ($\sigmasfr>3000$~\units).  We show stellar population fits to the
+  $\lrest=0.1$--3~$\mu$m emission (black solid line) and three
+  templates for dust emission \citep[M82 starburst, Arp 220 starburst,
+    and obscured quasar;][]{pol07}.  The starburst templates provide
+  reasonable fits to the $\lobs=12$ and 22~$\mu$m WISE photometry,
+  while the quasar template does not.  Right: HST/WFC3 F814W images
+  (probing $\lrest\approx5000$~\AA) showing that these galaxies are
+  dominated by a compact nucleus.}
+\label{fig:seds}
+\end{figure}
+% scaled to the WISE $\lobs=4.6~\mu$m flux.
 
@@
 of 100~pc, while uncertain, is likely accurate within a factor of two.
-
-\begin{figure}[!t]
-%\includegraphics[angle=90,scale=0.68]{sigmasfr_datafigure.ps}
-\includegraphics[angle=0,scale=0.41]{3seds.ps}
-\caption{Left: Observed UV--IR SEDs ($\lrest=0.1$--15~$\mu$m) for
-  three galaxies with large SFR surface densities
-  ($\sigmasfr>3000$~\units).  We show stellar population fits to the
-  $\lrest=0.1$--3~$\mu$m emission (black solid line) and three
-  templates for dust emission \citep[M82 starburst, Arp 220 starburst,
-    and obscured quasar;][]{pol07}.  The starburst templates provide
-  reasonable fits to the $\lobs=12$ and 22~$\mu$m WISE photometry,
-  while the quasar template does not.  Right: HST/WFC3 F814W images
-  (probing $\lrest\approx5000$~\AA) showing that these galaxies are
-  dominated by a compact nucleus.}
-\label{fig:seds}
-\end{figure}
-% scaled to the WISE $\lobs=4.6~\mu$m flux.
 
@@
 
-\subsection{The Outflow Launching Mechanism}
+\subsection{The Outflow Launching Mechanism}\label{sec:launch}
 
@@
 galaxies are a viable mechanism for producing compact starbursts
-(e.g., Mihos+94), and such gas-rich major mergers are rare at
+(e.g., Mihos+94), but such gas-rich major mergers are rare at
 $z\sim0.6$ due to the decline in both the merger rate and the gas
-fraction of galaxies since $z\sim1$.  The high-$\sigmasfr$ galaxies in
-particular are in a phase where there is strong feedback but star
+fraction of galaxies since $z\sim1$.  The high-$\sigmasfr$ galaxies
+are also in a particular phase where there is strong feedback but star
 formation has not been quenched.  The length of this phase may be set
@@
 $M_{gas}\sim5\times10^{9}$~\msun\ inside 100~pc, which would be
-consumed on a timescale $\sim30$~Myr.  It would be worthwhile to
-directly measure the molecular gas masses and kinematics of these
-extreme sources with CO observations to test this scenario.
-
-The vertical sequence in Figure~\ref{fig:sigmasfr} may be related to
-an evolutionary sequence, with the smaller $\sigmasfr$ galaxies being
-further along in their evolution towards a post-starburst phase.
-However, it is interesting to note that all 12/29 galaxies above the
-$\sigmasfr\approx45$~\units\ \citet{meu97} limit exhibit outflows
-(with median centroid velocity $v=-1500$~\kms), while all 7/29
-galaxies without detected outflows have $\sigmasfr<30$~\units.  If a
-compact starburst is a requirement for the production of high-velocity
-outflows, it may be that these latter sources have not gone through
-such a phase (see A. Robaina, et al, in preparation for a discussion
-of the relationship between outflow velocity, galaxy morphology, and
-stellar population age).
+consumed on a timescale $\sim30$~Myr.  Such estimates could be tested
+with observations of molecular gas masses and kinematics for these
+extreme galaxies.
+
+% which rely on extrapolating the K-S relation beyond the range where it had been calibrated,
+
+The vertical sequence among the galaxies in our sample in
+Figure~\ref{fig:sigmasfr} could be related to an evolutionary
+sequence, with smaller $\sigmasfr$ galaxies being further along in
+their evolution towards a post-starburst phase.  However, it is
+interesting to note that all 12/29 galaxies above the \citet{meu97}
+limit ($\sigmasfr\approx45$~\units) exhibit outflows (with median
+centroid velocity $v=-1500$~\kms), while all 7/29 galaxies without
+detected outflows have $\sigmasfr<30$~\units.  If a compact starburst
+is a requirement for the production of high-velocity outflows, as
+suggested by previous the discussion in Section~\ref{sec:launch}, it
+may be that the non-outflow sources have not gone through such a phase
+(see A. Robaina, et al., in preparation for a discussion of the
+relationship between outflow velocity, galaxy morphology, and stellar
+population age).
 
@@
 
-It is also worhwhile to consider the implications of these galaxies
-for models of massive galaxy formation.  Models do not produce
-starbursts this small.  Models that produce ellipticals have to invoke
-AGN feedback.  Models for size evolution would allow these galaxies to
-reach the size--mass relation by $z=0$.
+Finally, it is worthwhile to consider the implications of these
+galaxies for models of massive galaxy formation.  While simulaitons of
+major galaxy mergers with large gas fractions ($f_{gas}\sim50$\%) can
+produce $\textnormal{\mstar}\sim10^{11}$~\msun\ remnants with
+effective radii $r_{e}\sim1$~kpc \citep[e.g.,][]{wuy10}, similar to
+the observed sizes of compact quiescent galaxies at $z\sim2$
+\citep[e.g.,][]{van08}, our sample includes galaxies of similar mass
+that are smaller by almost an order of magnitude.  If these systems do
+evolve into quiescent elliptical galaxies, it would be quite
+challenging for them to grow in size from $r_e\sim0.1$~kpc to
+$r_e\sim5$~kpc to reach the local size--mass relation in the
+$t\sim6$~Gyr since $z=0.6$.  In this context, it is relevant point to
+note that the half-light radius (ignoring dust attenuation) at
+rest-frame $V$ band (where our HST observations prbe) can be a factor
+of 5--10 smaller than the half-mass radius for a system near the peak
+of the starburst \citep{wuy10}.  It would be worthwhile to test for
+such size discrepancies and to pronbe the radial dependence of the
+mass-to-light ratio by measuring sizes at rest-frame near-IR
+wavelengths.
 
@@
 
+% Connection to models.  How such large SFRs given the powerful wind?
+
+%Sample as a whole. Interesting that high-$\sigmasfr$ galaxies tend to
+%have larger outflow velocities.
+
+\section{Conclusions}
+
+Their descendants could perhaps be the local galaxies that are
+ significant outliers from the size--mass relation.
+
+Models that produce ellipticals have to invoke AGN feedback to quench
+star formation.
+
 Few galaxies exhibit such high-velocity outflows because few galaxies
@@
 
-% Connection to models.  How such large SFRs given the powerful wind?
-
-High-velocity outflows do not imply AGN feedback.
-
 Theoretical arguments about ram v. radiation pressure.  Point that we
@@
 
-Sample as a whole. Interesting that high-$\sigmasfr$ galaxies tend to
-have larger outflow velocities.
-
 Mention high-$\sigmasfr$ galaxies at high z.
 
-\section{Conclusions}
+High-velocity outflows do not imply AGN feedback.
 
@@
 %   arXiv:1107.0317
+\bibitem[Wuyts et al.(2010)]{wuy10} Wuyts, S., Cox, T.~J., Hayward,
+  C.~C., et al.\ 2010, \apj, 722, 1666
 \bibitem[Wuyts et al.(2011)]{wuy11} Wuyts, S., F{\"o}rster Schreiber,

### 2012-04-20 trunk/tex/sigmasfr/ms.tex
first full draft

--- 2012-04-19 trunk/tex/sigmasfr/ms.tex
@@
 \documentclass[apj]{emulateapj}
-%\documentclass[12pt,preprint]{aastex}
 
@@
 \newcommand{\sfrir}{\textnormal{SFR}_{\textnormal{\scriptsize{IR}}}}
-\newcommand {\apgt} {\ {\raise-.5ex\hbox{$\buildrel>\over\sim$}}\ }
-\newcommand {\aplt} {\ {\raise-.5ex\hbox{$\buildrel<\over\sim$}}\ }
 
-\shorttitle{Compact Starbursts Revealed by HST and WISE}
+\shorttitle{Compact Starbursts Driving High-Velocity Outflows}
 \shortauthors{Diamond-Stanic et al.}
@@
 \begin{document}
-
-%\title{HST and WISE Reveal Compact Starbursts Driving 1000
-%  \kms\ Outflows}
 
@@
 
-Based on infrared photometry from the Wide-field Infrared Survey
-Explorer (WISE) and optical morphologies from the Hubble Space
-Telescope (HST), we present the discovery of compact, obscured star
-formation in galaxies that exhibit $\gtrsim1000$~\kms\ outflows.  The
-implied star formation rate (SFR) surface densities approach
-$\sigmasfr\approx5000$~\msun~yr$^{-1}$~kpc$^{-2}$, comparable to the
-Eddington limit for a starburst where radiation pressure on dust
-grains overcomes gravity.  We argue that feedback associated with this
-starburst event, in the form of radiation pressure and supernova ram
-pressure, is a likely mechanism for launching the high-velocity
-outflows.
+We present the discovery of compact, obscured star formation in
+galaxies that exhibit $\gtrsim1000$~\kms\ outflows.  Using optical
+morphologies from the Hubble Space Telescope and infrared photometry
+from the Wide-field Infrared Survey Explorer, we estimate star
+formation rate (SFR) surface densities that approach
+$\sigmasfr\approx5000$~\msun~yr$^{-1}$~kpc$^{-2}$, which is comparable
+to the Eddington limit from radiation pressure on dust grains.  We
+argue that feedback associated with a compact starburst in the form of
+radiation pressure from massive stars and ram pressure from supernovae
+and stellar winds is sufficient to produce the high-velocity outflows
+we observe, without the need to invoke feedback from an active
+galactic nucleus.
 
@@
 
-% The relative importance of momentum injection versus thermal heating
-% may vary as a function of galaxy mass \citep[e.g.,][]{hop12}, with
-% thermal heating being less efficient in galaxies with larger gas
-% densities and shorter cooling times.  Massive star clusters with large
-% gas surface densities are a potential launching point for
-% galactic-scale outflows driven by radiation pressure
-% \citep[e.g.,][]{mur11}.
-
 Galactic winds are ubiquitous in star-forming galaxies at all
@@
 
-% $|v|\gtrsim1000$~\kms\
-
 In this Letter, we present results for a sample of massive galaxies at
-$z\sim0.6$ that exhibit $|v|\apgt1000$~\kms\ outflows, expanding on
-the sample from \citet{tre07}.  We seek to test whether the energetic
+$z\sim0.6$ that exhibit $\gtrsim1000$~\kms\ outflows, expanding on the
+sample from \citet{tre07}.  We seek to test whether the energetic
 outflows in these galaxies could have been driven by feedback from
@@
 
-% For example, there is evidence for a positive correlation between
-% outflow velocity and starburst luminosity \citep[e.g.,][]{mar05},
-% albeit with significant scatter.  Furthermore, \citet{hec11} recently
-% found outflows reaching velocities of $-1500$~\kms\ in a sample of
-% local starbursts with compact nuclei, and argued their higher
-% velocities could be explained by feedback exerted by a large number of
-% massive stars that are confined to a small radius.
-
-% [which has been invoked theoretically as
-%  a mechanism to quench star formation in galaxies,
-
-% Winds are also common in active galactic nuclei (AGNs) with velocities
-% in the 1000--20,000~\kms range \citep[e.g., ][]{cre03}, although it is
-% unclear whether AGN feedback plays an important role in regulating
-% star formation in galaxies.  There is clear observational evidence
-% that active galactic nuclei (AGNs) produce outflows
-% \citep[e.g.,][]{cre03} and that the outflowing gas can extend to
-% $>$kpc scales \citep[e.g.,][]{rup11}, it is unclear whether such
-% feedback plays an important role globally in quenching star formation.
-
-% Feedback from massive stars and active black holes has important
-% implications for galaxy evolution (e.g., luminosity function, star
-% formation, galaxy color bi-modality, mass-metallicity relation,
-% enrichment of IGM).
-
-% Feedback from accreting supermassive black holes has also been invoked
-% theoretically as a mechanism for quenching star formation in galaxies
-% \citep[e.g.,][]{sil98,gra04,dim05}.  There is clear observational
-% evidence that active galactic nuclei (AGNs) produce outflows
-% \citep[e.g.,][]{cre03} and that the outflowing gas can extend to
-% $>$kpc scales \citep[e.g.,][]{rup11}, but it is unclear whether such
-% feedback plays an important role globally in quenching star formation
-% and shaping the galaxy mass function.
-
-% and optical spectra ($\lrest=2500$-5200~\AA)
-
-%  The spectral region surrounding the
-%  \mgii~$\lambda\lambda2796,2803$ absorption alines, which are used to
-%  measure outflow velocities, is highlighted in both wavelength and
-%  velocity space.
-
-%  and are scaled to match the WISE channel 2 photometry ($\lobs=4.6$~$\mu$m)
-% (\mgii~$\lambda2796$ is plotted in blue and \mgii~$\lambda2803$ is plotted in red)
+\begin{figure}[!t]
+\includegraphics[angle=0,scale=0.41]{3seds.ps}
+\caption{Left: Observed UV--IR SEDs ($\lrest=0.1$--15~$\mu$m) for
+  three galaxies with large SFR surface densities
+  ($\sigmasfr>3000$~\units).  We show stellar population fits to the
+  $\lrest=0.1$--3~$\mu$m emission (black solid line) and three
+  templates for dust emission \citep[M82 starburst, Arp 220 starburst,
+    and obscured quasar;][]{pol07}.  The starburst templates provide
+  reasonable fits to the $\lobs=12$ and 22~$\mu$m WISE photometry,
+  while the quasar template does not.  Right: HST/WFC3 F814W images
+  (probing $\lrest\approx5000$~\AA) showing that these galaxies are
+  dominated by a compact nucleus.}
+\label{fig:seds}
+\end{figure}
 
@@
 
-%\subsection{HST/WFC3 Imaging}
 \subsection{Morphologies and Sizes}
@@
 \begin{figure}[!t]
-%\includegraphics[angle=90,scale=0.68]{sigmasfr_datafigure.ps}
-\includegraphics[angle=0,scale=0.41]{3seds.ps}
-\caption{Left: Observed UV--IR SEDs ($\lrest=0.1$--15~$\mu$m) for
-  three galaxies with large SFR surface densities
-  ($\sigmasfr>3000$~\units).  We show stellar population fits to the
-  $\lrest=0.1$--3~$\mu$m emission (black solid line) and three
-  templates for dust emission \citep[M82 starburst, Arp 220 starburst,
-    and obscured quasar;][]{pol07}.  The starburst templates provide
-  reasonable fits to the $\lobs=12$ and 22~$\mu$m WISE photometry,
-  while the quasar template does not.  Right: HST/WFC3 F814W images
-  (probing $\lrest\approx5000$~\AA) showing that these galaxies are
-  dominated by a compact nucleus.}
-\label{fig:seds}
-\end{figure}
-% scaled to the WISE $\lobs=4.6~\mu$m flux.
-
-\begin{figure}[!t]
 \includegraphics[angle=0,scale=0.41]{profile.ps}
@@
 
-%\subsection{Photometry, Star Formation Rates, and Stellar Masses}
 \subsection{Star Formation Rates and Stellar Masses}
@@
 \begin{center}
-\includegraphics[angle=0,scale=.8]{sigmasfr.ps} %\\
-%\includegraphics[angle=0,scale=.7]{sizemass_sigmasfr.ps}
-%\caption{$\sigmasfr$--mass and size--mass relationships.}
+\includegraphics[angle=0,scale=.8]{sigmasfr.ps} 
 \caption{SFR surface densities and stellar masses for the HST--WISE
@@
 
-% The sample of gas-rich mergers includes ULIRGs
-%   \citep{vei06}, Lyman break analogs with dominant central objects
-%   \citep{ove09}, and the local compact starburst Arp 220 \citep{sco97,
-%     ken98, rod08}.  The samples of star-forming galaxies are drawn
-%   from \citet{wuy11} at $0.02<z<0.2$ (solid black contour),
-%   $0.5<z<1.5$ (dashed red countour), and $1.5<z<2.5$ (dotted purple
-%   contour), and from \citet{law12} at $2.5<z<3.6$ (dash-dotted blue
-%   contour).
-
-%\subsection{Optical Spectroscopy}
 \subsection{Outflow Kinematics and Covering Factors}
@@
 
-% MMT/Blue Channel (J1506+5402, $R\sim1000$), SDSS (J1506+5402,
-% $R\sim2000$), Magellan/MAGE (J1341-0321, $R\sim4000$), Keck/LRIS
-% (J0905+5759, $R\sim600$), and Keck/HIRES (J0905+5759, $R\sim37,000$)
-
-%\section{Analysis}
-%
-%\subsection{Star-formation Rates and Stellar Masses}
-%
-%\subsection{Morphologies and Sizes}
-%
-%\subsection{Outflow Kinematics and Covering Factors}
-
-% \begin{figure*}[!t]
-% \begin{center}
-% \includegraphics[angle=0,scale=.8]{sizemass_sigmasfr.ps}
-% \caption{size--mass relationship.}
-% \label{fig:sizemass}
-% \end{center}
-% \end{figure*}
-
-% %\begin{center}
-% \begin{deluxetable}{ccccccc}
-% \tabletypesize{\scriptsize}
-% 
-% \tablecaption{Galaxy Properties\label{tab:properties}}
-% \tablewidth{0pt}
-% 
-% \tablehead{ \colhead{Galaxy Name} & \colhead{z} & \colhead{$M_{*}$} & \colhead{$v$} & \colhead{SFR} & \colhead{$r_e$} & \colhead{$\sigmasfr$} }
-% 
-% \startdata
-% J150636.29+540220.7   & 0.608 & 11.01 & -1211 &  621 & 0.13 & 5851 \\
-% J090523.60+575912.4   & 0.712 & 10.62 & -2470 & 344 & 0.10 & 5478 \\ 
-% %J094417.84+093019.3   & 0.514 & 10.73 & -1778 & $<43.22$ & 161 & 0.15 & 1139 \\
-% J134136.79$-$032125.2   & 0.658 & 10.61 & -875  & 490 & 0.16 & 3058 \\ 
-% % J1506 has Lx=42.66
-% \enddata
-% 
-% %\tablecomments{}
-% %\tablenotetext{a}{Star-formation rate based on \citet{ken98}.  No extinction correction has been applied.}
-% 
-% \end{deluxetable}
-% %\end{center}
-
 \section{Discussion}
@@
 is being regulated by momentum input from massive stars.
-
-%  We also include measurements of
-% late-stage, gas-rich mergers at $z<0.3$ from \citet{vei06},
-% star-forming galaxies at $z<0.3$ from \citet{ove09}, and star-forming
-% galaxies at $z=1.5$--3.6 from \citet{law12}.
-
-% Points to make:
-% \begin{itemize}
-% \item \citet{ken98}, the standard reference for the relationship
-%   between SFR and gas surface density, includes Arp 200 with
-%   $\sigmasfr\approx10^3$~\units\ and
-%   $\Sigma_{H_2}\approx5\times10^{10}$~\msun~kpc$^{-2}$.  
-% \item The star clusters considered by \citet{meu97} extend into this
-%   $\sigmasfr>10^{3}$~\units\ range.
-% 
-% \end{itemize}
-
-% We show relationship between effective radius and stellar mass for our
-% WISE-HST sample in bottom panel of Figure~\ref{fig:sizemass}.  Here,
-% we include the gas-rich mergers from \citet{vei06} as well as
-% $z\sim2.3$ compact massive galaxies from \citet{van08}.  We also show
-% the size--mass relationship for elliptical galaxies at $z\sim0.1$ from
-% \citet{she03}, and the average size evolution of spheroidal ($n>2.5$)
-% galaxies from $z=2$ to $z=0.1$ from \citet{tru07}.
-
-%\subsection{A Maximum Star-Formation Rate Surface Density?}
-
-%\section{Discussion}
 
@@
 
-% ased on its \oiii\ luminosity $L(\oiii)=10^{42.1}$~erg~s$^{-1}$, the
-% expected X-ray luminosity \citep[adopting the relationship between
-%   \oiii\ and X-ray luminosity for type 1 AGNs from][]{hec05}
-
-% No evidence in spectra for unobscured AGN component.  J1506+5402 has
-% X-ray and \nev.  Agreement between SFR indicators.  Mention Balmer
-% lines and dust geometry.  SEDs well fit by star-forming tempates.
-% Most ULIRGs are starburst dominated.  Mention Pauls's paper.  There is
-% likely some ongoing AGN activity in sources like J1506+5402, but in
-% general, the AGN does not seem to be relevant energetically.  Point
-% that high-velocity outflows don't mean that an outflow is AGN driven.
-
-\subsection{The Outflow Launching Mechanism}
+\subsection{The Outflow Launching Mechanism}\label{sec:launch}
 
@@
 
-% Following \citet{hec93} and
-% \citet{hec11}, the expected terminal velocity for a cloud with column
-% density $\approx10^{21}$~cm$^{-2}$ launched from a radius
-% $\approx200$~pc and driven by momentum flux
-% $\approx2\times10^{35}$~dynes is:
-% \begin{eqnarray}\nonumber
-% v_{\infty}&=&1800~\textnormal{km~s}^{-1}
-% \left(\dot{p}\over2\times10^{35}~\textnormal{dyne}\right)^{1/2} \\
-% &&
-% \left({r\over200~\textnormal{pc}}\right)^{-1/2}
-% \left({N\over10^{21}~\textnormal{cm}^{-2}}\right)^{-1/2}
-% \label{eq:vterm}
-% \end{eqnarray}
-% The expected momentum flux from stellar winds and supernovae for a
-% starburst with $\textnormal{SFR}\approx200$~\msun~yr$^{-1}$ is
-% $\approx5$--$10\times10^{35}$~dynes \citep{lei92,hec93,lei99,vei05}
-% while the $L_{bol}/c$ radiation pressure is
-% $\approx2\times10^{35}$~dynes.  Thus, there is more than enough
-% momentum available from stellar winds and supernovae or from radiation
-% pressure to produce the outflow velocities we observe.
-
-%AGN have been invoked to launch high-velocity winds.
-
-% \subsection{Momentum Flux from Supernovae and Stellar Winds}
-% 
-% \citet{meu97} argued for a limit near 45~\units (somewhat smaller for
-% a Chabrier IMF) based on the surface brightness of starbursts measured
-% using rest-frame UV, H$\alpha$, far-IR, and radio continuum emission,
-% such that only 10\% of starbursts exceeded this limit.  They argued
-% that the momentum flux from supernovae and stellar winds expected at
-% this threshold matches the mean central pressure measured by
-% \citet{hec90} for starburst-driven winds.
-% 
-% There are also relevant arguments about ram pressure driving of
-% high-velocity winds from \citet{hec11}.
-% 
-% 
-% \subsection{The Eddington Limit from Radiation Pressure on Dust Grains}
-
-% In models where gaseous outflows are driven by radiation pressure from
-% massive stars, estimates of the maximum $\sigmasfr$ where the outward
-% force from radiation exceeds the inward force of gravity are in the
-% $\sigmasfr\sim10^3$~\units\ range \citep[e.g.,][]{tho05,hop10}.
-
-% Our galaxies exceed the \citet{meu97} limit but are roughly in line
-% with the limit from radiation pressure.
-
-% The relative importance of momentum injection versus thermal heating
-% may vary as a function of galaxy mass \citep[e.g.,][]{hop12}, with
-% thermal heating being less efficient in galaxies with larger gas
-% densities and shorter cooling times.  Regarding momentum injection,
-% \citet{sha11} have argued that radiation pressure becomes more
-% important than ram pressure at large SFRs.
-
-%\subsection{Outflows at the Escape Velocity}
-
-% This is in agreement with the predicitons from radiation pressure
-% launching winds from the most massive star clusters in a galaxy.
-
-% Question of whether other observables are plausible.  
-% \begin{itemize}
-% \item Expected velocity dispersion.  Some results have suggested that
-%   turbulence becomes large at high surface densities, and therefore
-%   the velocity dispersion should be large.  
-% \item The dynamical time for the starburst.  If gas is consumed with
-%   an efficiency of a few \% per dynamical time, how long do we expect
-%   the starburst to last?
-% \end{itemize}
-% 
-% Other points: 
-% \begin{itemize}
-% \item Is this mechanism viable for the whole sample?  We see large
-%   outflow velocities in rest of the sample, where the galaxies are
-%   more ``post'' starburst.  This fits in a scenario where the genuine
-%   post-starbursts are further along in the evolution after the outflow
-%   quenches star formation.
-% \item Will these evolve into ellipticals, or do they have enough gas
-%   to reform a disk?  If they do quench, how difficult would it be to
-%   grow in size to match the local size--mass relationship?  Could
-%   their descendants be the handful of local galaxies that don't lie on
-%   the size--mass relationship?
-% \item Is there disagreement between $L_{IR}+L_{UV}$ and H$\alpha$
-%   SFRs?  \citet{hec11} pointed out that this could be a sign of
-%   escaping ionizing photons.
-% \end{itemize}
-
 \subsection{Placing These Galaxies in Context}
 
-They are rare and thus represent an unusual or short-lived phase.  Gas
-consumption time for starbursts.  Connection to ellipticals.
-Conceivable that they could grown in size sufficiently by $z=0$?
+It is clear from Figure~\ref{fig:sigmasfr} that the high-$\sigmasfr$
+galaxies in our sample constitute a rare population, suggesting that
+they represent an unusual or short-lived phase.  Mergers of gas-rich
+galaxies are a viable mechanism for producing compact starbursts
+\citep[e.g.,][]{mih96}, and such gas-rich major mergers are rare at
+$z\sim0.6$ due to the decline in both the merger rate
+\citep[e.g.,][]{lot11} and the gas fraction \citep[e.g.,][]{tac10} of
+galaxies since $z\sim2$.  Furthermore, the high-$\sigmasfr$ galaxies
+are caught in a particular time interval where there is both vigorous
+star formation and strong feedback.  The length of this phase may be
+set by the gas consumption timescale or the timescale for feedback to
+suppress subsequent star formation.  Based on the Kennicutt--Schmidt
+(K-S) relation \citep{ken98}, a compact starburst with
+$r_e\approx100$~pc, $\textnormal{SFR}\approx300$~\msun, and
+$\sigmasfr\approx5000$~\units\ would have a gas surface density of
+$\Sigma_{gas}\sim2\times10^{11}$~\msun~kpc$^{-2}$ corresponding to
+$M_{gas}\sim5\times10^{9}$~\msun\ inside 100~pc, which would be
+consumed on a timescale $\sim30$~Myr.  This scenario could be tested
+with CO observations of molecular gas masses and kinematics for these
+extreme galaxies.
 
-Few galaxies exhibit such high-velocity outflows because few galaxies
-have such extreme SFR surface densities.
+Considering our full sample of galaxies in Figure~\ref{fig:sigmasfr},
+a vertical $\sigmasfr$ sequence is apparent.  This could be explained
+as an evolutionary sequence where the high-$\sigmasfr$ galaxies
+represent the peak of the starburst where the high-velocity outflows
+are launched, while the lower $\sigmasfr$ galaxies represent a
+subseqent, post-starburst phase.  It is interesting to note that all
+12/29 galaxies above the $\sigmasfr\approx45$~\units\ limit from
+\citet{meu97} exhibit outflows (with median centroid velocity
+$v=-1500$~\kms), while all 7/29 galaxies without detected outflows
+have $\sigmasfr<30$~\units.  If a compact starburst is a requirement
+for the production of high-velocity outflows, it may be that the
+sources without outflows have not gone through such a phase (see
+A. Robaina, et al., in preparation for a discussion of the
+relationship between galaxy morphology, outflow velocity, and stellar
+population age in this sample).
 
-Connection to models.  How such large SFRs given the powerful wind?
-
-High-velocity outflows do not imply AGN feedback.
-
-Theoretical arguments about ram v. radiation pressure.  Point that we
-are observing 10$^4$~K gas.
-
-Sample as a whole. Interesting that high-$\sigmasfr$ galaxies tend to
-have larger outflow velocities.
-
-Mention high-$\sigmasfr$ galaxies at high z.
+Finally, it is worthwhile to consider the implications of our results
+for models of massive galaxy formation.  Simulaitons of major galaxy
+mergers with large gas fractions ($f_{gas}\sim50$\%) can produce
+$\textnormal{\mstar}\sim10^{11}$~\msun\ remnants with effective radii
+$r_{e}\sim1$~kpc \citep[e.g.,][]{wuy10}, but our sample includes
+galaxies of similar mass that are smaller by almost an order of
+magnitude.  If these systems do evolve into quiescent elliptical
+galaxies, it would be quite challenging for them to grow in size from
+$r_e\sim0.1$~kpc to $r_e\sim5$~kpc to reach the local size--mass
+relation \citep{shen03} in the $t\sim6$~Gyr since $z=0.6$.  For
+comparison the compact, quiescent galaxies observed at $z\sim2$
+\citep[e.g.,][]{tru07,van08} have $t\sim10$~Gyr to grow by a factor of
+$\sim5$.  In this context, it is worth noting that the half-light
+radius (ignoring dust attenuation) at rest-frame $V$ band (where our
+HST observations probe) can be a factor of 5--10 smaller than the
+half-mass radius for a gas-rich merger at final coalescence near the
+peak of starburst activity \citep{wuy10}.  It would be worthwhile to
+test for such size discrepancies and to pronbe the radial dependence
+of the mass-to-light ratio for these galaxies by measuring sizes at
+rest-frame near-IR wavelengths.
 
 \section{Conclusions}
+
+We have measured large SFR surface densities for galaxies that exhibit
+$\gtrsim1000$~\kms\ outflows.  The largest $\sigmasfr$ values are
+comparable to the Eddington limit from radiation pressure on dust
+grains, and such compact starburst are expected to have substantial
+momentum input from both massive stars and supernovae.  There is some
+evidence for AGN activity in a fraction of these systems, but the AGN
+is generally not relevant in a bolometric sense.  High-velocity
+outflows have been previously interpreted as a signpost of AGN
+feedback, but we conclude that stellar feedback from a compact
+starburst is equally capable of producing such a signature.
 
@@
 
-% James Bullock, Xavier Prochaska, Kate Rubin, Art Wolfe, Alex Mendez
-
 \begin{thebibliography}{}
@@
   S.\ 2008, \apj, 678, 686
-% \bibitem[Baldwin et al.(1981)]{bal81} Baldwin, J.~A., Phillips, M.~M.,
-%   \& Terlevich, R.\ 1981, \pasp, 93, 5
-% \bibitem[Barton \& Cooke(2009)]{bar09} Barton, E.~J., \& Cooke,
-%   J.\ 2009, \aj, 138, 1817
-% \bibitem[Bordoloi et al.(2011)]{bor11} Bordoloi, R., et al.\ 2011,
-%   arXiv:1106.0616
-% \bibitem[Buitrago et al.(2008)]{bui08} Buitrago, F., Trujillo, I.,
-%   Conselice, C.~J., Bouwens, R.~J., Dickinson, M., \& Yan, H.\ 2008,
-%   \apjl, 687, L61
-% \bibitem[Coil et al.(2011)]{coi11} Coil, A.~L., Weiner, B.~J., Holz,
-%   D.~E., et al.\ 2011, \apj, 743, 46
 \bibitem[Chary \& Elbaz(2001)]{cha01} Chary, R., \& Elbaz, D.\ 2001,
   \apj, 556, 562
-% \bibitem[Chen et al.(2010)]{hchen10} Chen, H.-W., Wild, V., Tinker,
-%   J.~L., Gauthier, J.-R., Helsby, J.~E., Shectman, S.~A., \& Thompson,
-%   I.~B.\ 2010, \apjl, 724, L176
-% \bibitem[Chen et al.(2010b)]{ychen10} Chen, Y.-M., Tremonti, C.~A.,
-%   Heckman, T.~M., Kauffmann, G., Weiner, B.~J., Brinchmann, J., \&
-%   Wang, J.\ 2010, \aj, 140, 445
 \bibitem[Chevalier \& Clegg(1985)]{che85} Chevalier, R.~A., \& Clegg,
   A.~W.\ 1985, \nat, 317, 44
-% \bibitem[Coil et al.(2011)]{coi11} Coil, A.~L., Weiner, B.~J., Holz,
-%   D.~E., Cooper, M.~C., Yan, R., \& Aird, J.\ 2011, arXiv:1104.0681
-\bibitem[Crenshaw et al.(2003)]{cre03} Crenshaw, D.~M., Kraemer,
-  S.~B., \& George, I.~M.\ 2003, \araa, 41, 117
-% \bibitem[Croton et al.(2006)]{cro06} Croton, D.~J., et al.\ 2006,
-%   \mnras, 365, 11
 \bibitem[Dale \& Helou(2002)]{dal02} Dale, D.~A., \& Helou, G.\ 2002,
   \apj, 576, 159
-% \bibitem[Dekel \& Birnboim(2006)]{dek06} Dekel, A., \& Birnboim,
-%   Y.\ 2006, \mnras, 368, 2
 \bibitem[de Vaucouleurs(1948)]{dev48} de Vaucouleurs, G.\ 1948,
@@
   M., et al.\ 2010, \aap, 519, A92
-\bibitem[Granato et al.(2004)]{gra04} Granato, G.~L., De Zotti, G.,
-  Silva, L., Bressan, A., \& Danese, L.\ 2004, \apj, 600, 580
-\bibitem[Heckman et al.(1990)]{hec90} Heckman, T.~M., Armus, L., \&
-  Miley, G.~K.\ 1990, \apjs, 74, 833
 \bibitem[Heckman et al.(1993)]{hec93} Heckman, T.~M., Lehnert, M.~D.,
@@
   \apj, 730, 5
-% \bibitem[Hopkins et al.(2009)]{hop09} Hopkins, P.~F., Bundy, K.,
-%   Murray, N., Quataert, E., Lauer, T.~R., \& Ma, C.-P.\ 2009, \mnras,
-%   398, 898
-%\bibitem[Hopkins et al.(2009)]{hop09} Hopkins, P.~F., Hernquist, L.,
-%  Cox, T.~J., Keres, D., \& Wuyts, S.\ 2009, \apj, 691, 1424
 \bibitem[Hopkins et al.(2009)]{hop09} Hopkins, P.~F., Cox, T.~J.,
   Dutta, S.~N., et al.\ 2009, \apjs, 181, 135
-% \bibitem[Hopkins et al.(2010a)]{hop10a} Hopkins, P.~F.,
-%   Bundy, K., Hernquist, L., Wuyts, S., \& Cox, T.~J.\ 2010, \mnras,
-%   401, 1099
 \bibitem[Hopkins et al.(2010)]{hop10} Hopkins, P.~F., Murray, N.,
   Quataert, E., \& Thompson, T.~A.\ 2010, \mnras, 401, L19
-% %\bibitem[Hopkins et al.(2011)]{hop11} Hopkins, P.~F., Quataert, E., \&
-% %  Murray, N.\ 2011, arXiv:1101.4940
-% \bibitem[Hopkins et al.(2011)]{hop11} Hopkins, P.~F., Quataert, E., \&
-%   Murray, N.\ 2011, arXiv:1110.4638
-\bibitem[Hopkins et al.(2012)]{hop12} Hopkins, P.~F., Quataert, E., \&
-  Murray, N.\ 2012, \mnras, arXiv:1110.4638
-% \bibitem[Kacprzak et al.(2010)]{kac10} Kacprzak, G.~G., Churchill,
-%   C.~W., Ceverino, D., Steidel, C.~C., Klypin, A., \& Murphy,
-%   M.~T.\ 2010, \apj, 711, 533
-% \bibitem[Kacprzak et al.(2011a)]{kac11a} Kacprzak, G.~G., Churchill,
-%   C.~W., Barton, E.~J., \& Cooke, J.\ 2011, \apj, 733, 105
-% \bibitem[Kacprzak et al.(2011b)]{kac11b} Kacprzak, G.~G., Churchill,
-%   C.~W., Evans, J.~L., Murphy, M.~T., \& Steidel, C.~C.\ 2011,
-%   arXiv:1106.3068
-% \bibitem[Kauffmann et al.(2003)]{kau03} Kauffmann, G., Heckman, T.~M.,
-%   Tremonti, C., et al.\ 2003, \mnras, 346, 1055
-% \bibitem[Kennicutt(1998)]{ken98} Kennicutt, R.~C., Jr.\ 1998, \araa,
-%   36, 189
 \bibitem[Kennicutt(1998)]{ken98} Kennicutt, R.~C., Jr.\ 1998, \apj,
   498, 541
-% \bibitem[Kere{\v s} et al.(2005)]{ker05} Kere{\v s}, D., Katz, N.,
-%   Weinberg, D.~H., \& Dav{\'e}, R.\ 2005, \mnras, 363, 2
-% \bibitem[Kere{\v s} et al.(2009)]{ker09} Kere{\v s}, D., Katz, N.,
-%   Dav{\'e}, R., Fardal, M., \& Weinberg, D.~H.\ 2009, \mnras, 396,
-%   2332
-% \bibitem[Kobulnicky \& Kewley(2004)]{kob04} Kobulnicky, H.~A., \&
-%   Kewley, L.~J.\ 2004, \apj, 617, 240
 \bibitem[Kormendy et al.(2009)]{kor09} Kormendy, J., Fisher, D.~B.,
   Cornell, M.~E., \& Bender, R.\ 2009, \apjs, 182, 216
-% \bibitem[Kriek et al.(2010)]{kri10} Kriek, M., et al.\ 2010, \apjl,
-%   722, L64
-\bibitem[Law et al.(2012)]{law12} Law, D.~R., Steidel, C.~C., Shapley,
-  A.~E., et al.\ 2012, \apj, 745, 85
 \bibitem[Lehnert \& Heckman(1996)]{leh96} Lehnert, M.~D., \& Heckman,
   T.~M.\ 1996, \apj, 472, 546
-% \bibitem[Lehnert \& Heckman(1996)]{leh96} Lehnert, M.~D., \& Heckman,
-%   T.~M.\ 1996, \apj, 462, 651
 \bibitem[Leitherer et al.(1992)]{lei92} Leitherer, C., Robert, C., \&
@@
   Goldader, J.~D., et al.\ 1999, \apjs, 123, 3
+\bibitem[Lotz et al.(2011)]{lot11} Lotz, J.~M., Jonsson, P., Cox,
+  T.~J., et al.\ 2011, \apj, 742, 103
 \bibitem[Martin(2005)]{mar05} Martin, C.~L.\ 2005, \apj, 621, 227
-% \bibitem[Martin(2006)]{mar06} Martin, C.~L.\ 2006, \apj, 647, 222
-% \bibitem[Martin \& Bouch{\'e}(2009)]{mar09} Martin, C.~L., \&
-%   Bouch{\'e}, N.\ 2009, \apj, 703, 1394
 \bibitem[Martin et al.(2005)]{mar05galex} Martin, D.~C., Fanson, J.,
   Schiminovich, D., et al.\ 2005, \apjl, 619, L1
-% \bibitem[McIntosh et al.(2005)]{mci05} McIntosh, D.~H., et al.\ 2005,
-%   \apj, 632, 191
 \bibitem[Meurer et al.(1997)]{meu97} Meurer, G.~R., Heckman, T.~M.,
   Lehnert, M.~D., Leitherer, C., \& Lowenthal, J.\ 1997, \aj, 114, 54
-% \bibitem[Morrissey et al.(2007)]{mor07} Morrissey, P., Conrow, T.,
-%   Barlow, T.~A., et al.\ 2007, \apjs, 173, 682
+\bibitem[Mihos \& Hernquist(1996)]{mih96} Mihos, J.~C., \& Hernquist,
+  L.\ 1996, \apj, 464, 641
 \bibitem[Moustakas et al.(2011)]{mou11} Moustakas, J., Zaritsky, D.,
@@
   Thompson, T.~A.\ 2011, \apj, 735, 66
-% \bibitem[Nath \& Silk(2009)]{nat09} Nath, B.~B., \& Silk, J.\ 2009,
-%   \mnras, 396, L90
-% \bibitem[Nestor et al.(2011)]{nes11} Nestor, D.~B., Johnson, B.~D.,
-%   Wild, V., M{\'e}nard, B., Turnshek, D.~A., Rao, S., \& Pettini,
-%   M.\ 2011, \mnras, 412, 1559
-% \bibitem[Oke(1990)]{oke90} Oke, J.~B.\ 1990, \aj, 99, 1621
-% \bibitem[Oke et al.(1995)]{oke95} Oke, J.~B., et al.\ 1995, \pasp,
-%   107, 375
-% \bibitem[Oppenheimer \& Dav{\'e}(2006)]{opp06} Oppenheimer, B.~D., \&
-%   Dav{\'e}, R.\ 2006, \mnras, 373, 1265
-% \bibitem[Osterbrock(1989)]{ost89} Osterbrock, D.~E.\ 1989,
-%   Astrophysics of Gaseous Nebulae and Active Galactic Nuclei (Mill
-%   Valley, CA: University Science Books) 
 \bibitem[Overzier et al.(2009)]{ove09} Overzier, R.~A., Heckman,
   T.~M., Tremonti, C., et al.\ 2009, \apj, 706, 203
-% \bibitem[Pagel et al.(1979)]{pag79} Pagel, B.~E.~J., Edmunds, M.~G.,
-%   Blackwell, D.~E., Chun, M.~S., \& Smith, G.\ 1979, \mnras, 189, 95
 \bibitem[Peng et al.(2002)]{pen02} Peng, C.~Y., Ho, L.~C., Impey,
@@
   C.~D., \& Rix, H.-W.\ 2010, \aj, 139, 2097
-% \bibitem[Pettini et al.(2001)]{pet01} Pettini, M., Shapley, A.~E.,
-%   Steidel, C.~C., Cuby, J.-G., Dickinson, M., Moorwood, A.~F.~M.,
-%   Adelberger, K.~L., \& Giavalisco, M.\ 2001, \apj, 554, 981
 \bibitem[Polletta et al.(2007)]{pol07} Polletta, M., Tajer, M.,
   Maraschi, L., et al.\ 2007, \apj, 663, 81
-% \bibitem[Prochaska \& Hennawi(2009)]{pro09} Prochaska, J.~X., \&
-%   Hennawi, J.~F.\ 2009, \apj, 690, 1558
-% \bibitem[Prochaska et al.(2011a)]{pro11a} Prochaska, J.~X., Kasen, D.,
-%   \& Rubin, K.\ 2011, arXiv:1102.3444
-% \bibitem[Prochaska et al.(2011b)]{pro11b} Prochaska,
-%   J.~X., Weiner, B., Chen, H.~-., Mulchaey, J.~S., \& Cooksey,
-%   K.~L.\ 2011, arXiv:1103.1891
+\bibitem[Robaina et al.(2010)]{rob10} Robaina, A.~R., Bell, E.~F., van
+  der Wel, A., et al.\ 2010, \apj, 719, 844
 \bibitem[Rodr{\'{\i}}guez Zaur{\'{\i}}n et al.(2008)]{rod08}
@@
   Weiner, B.~J., et al.\ 2009, \apj, 692, 556
-% \bibitem[Rubin et al.(2010a)]{rub10a} Rubin, K.~H.~R., Prochaska, J.~X.,
-%   Koo, D.~C., Phillips, A.~C., \& Weiner, B.~J.\ 2010, \apj, 712, 574
 \bibitem[Rubin et al.(2010)]{rub10} Rubin, K.~H.~R., Weiner, B.~J.,
@@
   J.~A.\ 2010, \apj, 719, 1503
-% \bibitem[Rubin et al.(2011)]{rub11} Rubin, K.~H.~R., Prochaska, J.~X.,
-%   M{\'e}nard, B., Murray, N., Kasen, D., Koo, D.~C., \& Phillips,
-%   A.~C.\ 2011, \apj, 728, 55
 \bibitem[Rujopakarn et al.(2011)]{ruj11} Rujopakarn, W.,
@@
 \bibitem[Rupke et al.(2005)]{rup05} Rupke, D.~S., Veilleux, S., \&
-  Sanders, D.~B.\ 2005, \apjs, 160, 115 % analysis and discussion
-% \bibitem[Rupke \& Veilleux(2011)]{rup11} Rupke, D.~S.~N., \& Veilleux,
-%   S.\ 2011, \apjl, 729, L27
-% \bibitem[Sato et al.(2009)]{sat09} Sato, T., Martin, C.~L., Noeske,
-%   K.~G., Koo, D.~C., \& Lotz, J.~M.\ 2009, \apj, 696, 214
+  Sanders, D.~B.\ 2005, \apjs, 160, 115 
 \bibitem[Schlegel et al.(1998)]{sch98} Schlegel, D.~J., Finkbeiner,
   D.~P., \& Davis, M.\ 1998, \apj, 500, 525
-% \bibitem[Schwartz \& Martin(2004)]{sch04} Schwartz, C.~M., \& Martin,
-%   C.~L.\ 2004, \apj, 610, 201
 \bibitem[Scoville et al.(1997)]{sco97} Scoville, N.~Z., Yun, M.~S., \&
   Bryant, P.~M.\ 1997, \apj, 484, 702
-\bibitem[Sharma \& Nath(2011)]{sha11} Sharma, M., \& Nath,
-  B.~B.\ 2011, arXiv:1112.3447
 \bibitem[Shapley et al.(2003)]{sha03} Shapley, A.~E., Steidel, C.~C.,
@@
   \aap, 331, L1
-% \bibitem[Springel \& Hernquist(2003)]{spr03} Springel, V., \&
-%   Hernquist, L.\ 2003, \mnras, 339, 312
-% \bibitem[Steidel et al.(2002)]{ste02} Steidel, C.~C., Kollmeier,
-%   J.~A., Shapley, A.~E., Churchill, C.~W., Dickinson, M., \& Pettini,
-%   M.\ 2002, \apj, 570, 526
 \bibitem[Steidel et al.(2010)]{ste10} Steidel, C.~C., Erb, D.~K.,
@@
   Rudie, G.~C., \& Rakic, O.\ 2010, \apj, 717, 289
-% \bibitem[Stewart et al.(2011a)]{ste11a} Stewart, K.~R., Kaufmann, T.,
-%   Bullock, J.~S., Barton, E.~J., Maller, A.~H., Diemand, J., \&
-%   Wadsley, J.\ 2011, \apjl, 735, L1
-% \bibitem[Stewart et al.(2011b)]{ste11b} Stewart, K.~R., Kaufmann, T.,
-%   Bullock, J.~S., Barton, E.~J., Maller, A.~H., Diemand, J., \&
-%   Wadsley, J.\ 2011, arXiv:1103.4388
-% \bibitem[Strickland et al.(2004)]{str04} Strickland, D.~K., Heckman,
-%   T.~M., Colbert, E.~J.~M., Hoopes, C.~G., \& Weaver, K.~A.\ 2004,
-%   \apjs, 151, 193
-% \bibitem[Taylor et al.(2010)]{tay10} Taylor, E.~N., Franx, M.,
-%   Glazebrook, K., Brinchmann, J., van der Wel, A., \& van Dokkum,
-%   P.~G.\ 2010, \apj, 720, 723
+\bibitem[Tacconi et al.(2010)]{tac10} Tacconi, L.~J., Genzel, R.,
+  Neri, R., et al.\ 2010, \nat, 463, 781
 \bibitem[Thompson et al.(2005)]{tho05} Thompson, T.~A., Quataert, E.,
@@
   \& Diamond-Stanic, A.~M.\ 2007, \apjl, 663, L77
-% %\bibitem[Tremonti et al.(2012)]{tre12} Tremonti, C.~A., et al.\ 2012,
-% %  in prep
 \bibitem[Trujillo et al.(2007)]{tru07} Trujillo, I., Conselice, C.~J.,
@@
   al.\ 2008, \apjl, 677, L5
-% \bibitem[van Dokkum et al.(2010)]{van10} van Dokkum, P.~G., et
-%   al.\ 2010, \apj, 709, 1018
-% \bibitem[Vogt et al.(1994)]{vog94} Vogt, S.~S., et al.\ 1994,
-%   \procspie, 2198, 362
 \bibitem[Veilleux et al.(2005)]{vei05} Veilleux, S., Cecil, G., \&
@@
   P.~R.~M., Mainzer, A.~K., et al.\ 2010, \aj, 140, 1868
-% \bibitem[Wuyts et al.(2010)]{wuy10} Wuyts, S., Cox, T.~J., Hayward,
-%   C.~C., Franx, M., Hernquist, L., Hopkins, P.~F., Jonsson, P., \& van
-%   Dokkum, P.~G.\ 2010, \apj, 722, 1666
-% \bibitem[Wuyts et al.(2011)]{wuy11} Wuyts, S., et al.\ 2011,
-%   arXiv:1107.0317
+\bibitem[Wuyts et al.(2010)]{wuy10} Wuyts, S., Cox, T.~J., Hayward,
+  C.~C., et al.\ 2010, \apj, 722, 1666
 \bibitem[Wuyts et al.(2011)]{wuy11} Wuyts, S., F{\"o}rster Schreiber,
   N.~M., van der Wel, A., et al.\ 2011, \apj, 742, 96
-% \bibitem[Zhang \& Thompson(2010)]{zha10} Zhang, D., \& Thompson,
-%   T.~A.\ 2010, arXiv:1005.4691
-% \bibitem[Zirm et al.(2007)]{zir07} Zirm, A.~W., et al.\ 2007, \apj,
-%   656, 66
 \end{thebibliography}
 
-\clearpage
-
-%\clearpage
-
-% \clearpage
-% 
-% \begin{figure*}[!t]
-% \begin{center}
-% \includegraphics[angle=0,scale=.60]{j0905_hires_mg.ps}
-% \caption{Keck/HIRES spectra.}
-% \label{fig:hires}
-% \end{center}
-% \end{figure*}
-
-%\clearpage
-
 \end{document}

### 2012-04-20 trunk/tex/sigmasfr/ms.tex
cut references, modified figure 1

@@
 such as feedback from an accreting supermassive black hole
-\citep[e.g.,][]{sil98,dim05,deb12}, could have been responsible for
+\citep[e.g.,][]{sil98,dim05}, could have been responsible for
 launching the winds \citep[see][for a recent review]{fab12}.
@@
 Hubble Space Telescope (HST) with star-formation rates and stellar
-masses estimated from WISE, Spitzer, SDSS, and GALEX photometry.
+masses estimated using photometry from the Wide-field Infrared Survey
+Explorer (WISE), the Spitzer Space Telescope, the Sloan Digital Sky
+Survey (SDSS), and the Galaxy Evolution Explorer (GALEX).
 
@@
   ($\sigmasfr>3000$~\units).  We show stellar population fits to the
-  $\lrest=0.1$--3~$\mu$m emission (black solid line) and three
-  templates for dust emission \citep[M82 starburst, Arp 220 starburst,
-    and obscured quasar;][]{pol07}.  The starburst templates provide
-  reasonable fits to the $\lobs=12$ and 22~$\mu$m WISE photometry,
-  while the quasar template does not.  Right: HST/WFC3 F814W images
-  (probing $\lrest\approx5000$~\AA) showing that these galaxies are
-  dominated by a compact nucleus.}
+  $\lrest=0.1$--3~$\mu$m emission (black solid line) and two templates
+  for dust emission \citep[M82 starburst, Arp 220 starburst;][]{pol07}
+  scaled to match the $\lobs=4.6~\mu$m band.  The starburst templates
+  provide reasonable fits to the $\lobs=12$ and 22~$\mu$m WISE
+  photometry, while a quasar template does not.  Right: HST/WFC3 F814W
+  images (probing $\lrest\approx5000$~\AA) showing that these galaxies
+  are dominated by a compact nucleus.}
 \label{fig:seds}
@@
 produce science mosaics with $0.02\arcsec$ pixels.  For each galaxy,
-we use GALFIT \citep{pen02,pen10} to model the two-dimensional surface
+we use GALFIT \citep{pen02} to model the two-dimensional surface
 brightness profile with a single Sersic component, using stars in the
@@
 model.  In cases where the best-fit model returns $n>4$, we also fit
-an $n=4$ de Vaucouleurs model \citep{dev48}, yielding a larger $r_e$
-value (due to the covariance between $n$ and $r_e$), and we use these
-these larger effective radii in our analysis.
+an $n=4$ de Vaucouleurs model, yielding a larger $r_e$ value (due to
+the covariance between $n$ and $r_e$), and we use these these larger
+effective radii in our analysis.
 
@@
 
-We gathered photometry from the All-Sky Release of the Wide-field
-Infrared Survey Explorer \citep[WISE,][]{wri10}, the Seventh Data
-Release of the Sloan Digital Sky Survey \citep[SDSS,][]{aba09}, and
-General Release 6 from the Galaxy Evolution Explorer
-\citep[GALEX,][]{mar05galex}.  We also obtained $5\times30$~sec
-dithered exposures at 3.6~$\mu$m and 4.5~$\mu$m for all sources with
-the Infrared Array Camera \citep{faz04} on the Spitzer Space Telescope
-\citep{wer04} as part of General Observer program 60145 (PI:
-C. Tremonti).  We used the post--basic calibrated data to perform
-aperture photometry on all sources, and we also used the
+% We gathered photometry from the All-Sky Release of the Wide-field
+% Infrared Survey Explorer \citep[WISE,][]{wri10}, the Seventh Data
+% Release of the Sloan Digital Sky Survey \citep[SDSS,][]{aba09}, and
+% General Release 6 from the Galaxy Evolution Explorer
+% \citep[GALEX,][]{mar05galex}.  
+We gathered photometry from the WISE All-Sky Release, the SDSS Seventh
+Data Release, and GALEX General Release 6.  We also obtained
+$5\times30$~sec dithered exposures at 3.6~$\mu$m and 4.5~$\mu$m for
+all sources with the Infrared Array Camera on the Spitzer Space
+Telescope as part of General Observer program 60145 (PI: C. Tremonti).
+We used the post--basic calibrated data to perform aperture photometry
+on all sources, and we also used the
 APEX\footnote{http://irsa.ipac.caltech.edu/data/SPITZER/docs/dataanalysistools/tools/mopex/}
 point-source extraction software for photometry of sources in crowded
-fields.  All the photometry was corrected for Galactic extinction
-based on the \citet{sch98} dust maps.  We show spectral energy
-distributions (SEDs) for the three high-$\sigmasfr$ galaxies in
-Figure~\ref{fig:seds}.
+fields.  We show spectral energy distributions (SEDs) for the three
+high-$\sigmasfr$ galaxies in Figure~\ref{fig:seds}.
+
+% All the photometry was corrected for Galactic extinction
+% based on the \citet{sch98} dust maps.
 
@@
 luminous galaxies in the local universe
-\citep[e.g.,][]{cha01,dal02,rie09}.  If we used the most luminous
+\citep[e.g.,][]{rie09}.  If we used the most luminous
 local templates for the 8/29 sources with SFRs in the ULIRG regime
@@
 by HST.  This source also has a weak \nev~$\lambda3426$ emission line,
-which is associated with AGN activity \citep[e.g.,][]{abe08,gil10}.
-It was observed with the Chandra X-ray Observatory (proposal ID
-11700896, PI: C. Tremonti) and had four detected counts, corresponding
-to a 0.5--8.0~keV X-ray luminosity of $10^{42.7}$~erg~s$^{-1}$ (see
-P. Sell et al., in preparation for more details on the 12/29 galaxies
-with Chandra observations).  Using the relationship between 2--10~keV
-X-ray and 12.3~$\mu$m mid-IR luminosity for AGNs from \citet{gan09},
-one would expect a source with
+which is associated with AGN activity \citep[e.g.,][]{gil10}.  It was
+observed with the Chandra X-ray Observatory (proposal ID 11700896, PI:
+C. Tremonti) and had four detected counts, corresponding to a
+0.5--8.0~keV X-ray luminosity of $10^{42.7}$~erg~s$^{-1}$ (see P. Sell
+et al., in preparation for more details on the 12/29 galaxies with
+Chandra observations).  Using the relationship between 2--10~keV X-ray
+and 12.3~$\mu$m mid-IR luminosity for AGNs from \citet{gan09}, one
+would expect a source with
 $L_{\textnormal{\scriptsize{X}}}\approx5\times10^{42}$~erg~s$^{-1}$ to
@@
 mid-IR AGN contribution would only be relevant at the $\lesssim$30\%
-level.  Thus, similar to local ULIRGs \citep[e.g.,][]{far07}, the
-bolometric output of the galaxies in our sample is dominated by star
-formation, and we conclude that our results regarding large
+level.  We conclude that the bolometric output of the galaxies in our
+sample is dominated by star and we that our results regarding large
 $\sigmasfr$ values are not affected by AGN contamination.
+
+% Thus, similar to local ULIRGs \citep[e.g.,][]{far07}, the
+% bolometric output of the galaxies in our sample is dominated by star
+% formation, and we conclude that our results regarding large
+% $\sigmasfr$ values are not affected by AGN contamination.
 
@@
 pressure $\dot{p}\approx5$--$10\times10^{35}$~dyne from stellar winds
-and supernovae \citep[e.g.,][]{lei92,hec93,lei99,vei05}.  Furthermore,
+and supernovae \citep[e.g.,][]{lei92,lei99,vei05}.  Furthermore,
 \citet{hec11} noted that such a large momentum injection
@@
 $r_e\sim0.1$~kpc to $r_e\sim5$~kpc to reach the local size--mass
-relation \citep{shen03} in the $t\sim6$~Gyr since $z=0.6$.  For
+relation \citep{she03} in the $t\sim6$~Gyr since $z=0.6$.  For
 comparison the compact, quiescent galaxies observed at $z\sim2$
@@
 \begin{thebibliography}{}
-\bibitem[Abazajian et al.(2009)]{aba09} Abazajian, K.~N.,
-  Adelman-McCarthy, J.~K., Ag{\"u}eros, M.~A., et al.\ 2009, \apjs,
-  182, 543
-\bibitem[Abel \& Satyapal(2008)]{abe08} Abel, N.~P., \& Satyapal,
-  S.\ 2008, \apj, 678, 686
+%\bibitem[Abazajian et al.(2009)]{aba09} Abazajian, K.~N.,
+%  Adelman-McCarthy, J.~K., Ag{\"u}eros, M.~A., et al.\ 2009, \apjs,
+%  182, 543
+%\bibitem[Abel \& Satyapal(2008)]{abe08} Abel, N.~P., \& Satyapal,
+%  S.\ 2008, \apj, 678, 686
 \bibitem[Chary \& Elbaz(2001)]{cha01} Chary, R., \& Elbaz, D.\ 2001,
@@
   A.~W.\ 1985, \nat, 317, 44
-\bibitem[Dale \& Helou(2002)]{dal02} Dale, D.~A., \& Helou, G.\ 2002,
-  \apj, 576, 159
-\bibitem[de Vaucouleurs(1948)]{dev48} de Vaucouleurs, G.\ 1948,
-  Annales d'Astrophysique, 11, 247
-\bibitem[Debuhr et al.(2012)]{deb12} Debuhr, J., Quataert, E., \& Ma,
-  C.-P.\ 2012, \mnras, 420, 2221
+%\bibitem[Dale \& Helou(2002)]{dal02} Dale, D.~A., \& Helou, G.\ 2002,
+%  \apj, 576, 159
+%\bibitem[de Vaucouleurs(1948)]{dev48} de Vaucouleurs, G.\ 1948,
+%  Annales d'Astrophysique, 11, 247
+%\bibitem[Debuhr et al.(2012)]{deb12} Debuhr, J., Quataert, E., \& Ma,
+%  C.-P.\ 2012, \mnras, 420, 2221
 \bibitem[Diamond-Stanic et al.(2009)]{dia09} Diamond-Stanic, A.~M.,
@@
   arXiv:1204.4114
-\bibitem[Farrah et al.(2007)]{far07} Farrah, D., Bernard-Salas, J.,
-  Spoon, H.~W.~W., et al.\ 2007, \apj, 667, 149
-\bibitem[Fazio et al.(2004)]{faz04} Fazio, G.~G., Hora, J.~L., Allen,
-  L.~E., et al.\ 2004, \apjs, 154, 10
+%\bibitem[Farrah et al.(2007)]{far07} Farrah, D., Bernard-Salas, J.,
+%  Spoon, H.~W.~W., et al.\ 2007, \apj, 667, 149
+%\bibitem[Fazio et al.(2004)]{faz04} Fazio, G.~G., Hora, J.~L., Allen,
+%x  L.~E., et al.\ 2004, \apjs, 154, 10
 \bibitem[Gandhi et al.(2009)]{gan09} Gandhi, P., Horst, H., Smette,
@@
   M., et al.\ 2010, \aap, 519, A92
-\bibitem[Heckman et al.(1993)]{hec93} Heckman, T.~M., Lehnert, M.~D.,
-  \& Armus, L.\ 1993, The Environment and Evolution of Galaxies, 188,
-  455
+%\bibitem[Heckman et al.(1993)]{hec93} Heckman, T.~M., Lehnert, M.~D.,
+%  \& Armus, L.\ 1993, The Environment and Evolution of Galaxies, 188,
+%  455
 \bibitem[Heckman et al.(2000)]{hec00} Heckman, T.~M., Lehnert, M.~D.,
@@
 \bibitem[Martin(2005)]{mar05} Martin, C.~L.\ 2005, \apj, 621, 227
-\bibitem[Martin et al.(2005)]{mar05galex} Martin, D.~C., Fanson, J.,
-  Schiminovich, D., et al.\ 2005, \apjl, 619, L1
+%\bibitem[Martin et al.(2005)]{mar05galex} Martin, D.~C., Fanson, J.,
+%  Schiminovich, D., et al.\ 2005, \apjl, 619, L1
 \bibitem[Meurer et al.(1997)]{meu97} Meurer, G.~R., Heckman, T.~M.,
@@
   C.~D., \& Rix, H.-W.\ 2002, \aj, 124, 266
-\bibitem[Peng et al.(2010)]{pen10} Peng, C.~Y., Ho, L.~C., Impey,
-  C.~D., \& Rix, H.-W.\ 2010, \aj, 139, 2097
+%\bibitem[Peng et al.(2010)]{pen10} Peng, C.~Y., Ho, L.~C., Impey,
+%  C.~D., \& Rix, H.-W.\ 2010, \aj, 139, 2097
 \bibitem[Polletta et al.(2007)]{pol07} Polletta, M., Tajer, M.,
   Maraschi, L., et al.\ 2007, \apj, 663, 81
-\bibitem[Robaina et al.(2010)]{rob10} Robaina, A.~R., Bell, E.~F., van
-  der Wel, A., et al.\ 2010, \apj, 719, 844
 \bibitem[Rodr{\'{\i}}guez Zaur{\'{\i}}n et al.(2008)]{rod08}
@@
   Sanders, D.~B.\ 2005, \apjs, 160, 115 
-\bibitem[Schlegel et al.(1998)]{sch98} Schlegel, D.~J., Finkbeiner,
-  D.~P., \& Davis, M.\ 1998, \apj, 500, 525
+%\bibitem[Schlegel et al.(1998)]{sch98} Schlegel, D.~J., Finkbeiner,
+%  D.~P., \& Davis, M.\ 1998, \apj, 500, 525
 \bibitem[Scoville et al.(1997)]{sco97} Scoville, N.~Z., Yun, M.~S., \&
@@
   \apj, 692, 187
-\bibitem[Werner et al.(2004)]{wer04} Werner, M.~W., Roellig, T.~L.,
-  Low, F.~J., et al.\ 2004, \apjs, 154, 1
-\bibitem[Wright et al.(2010)]{wri10} Wright, E.~L., Eisenhardt,
-  P.~R.~M., Mainzer, A.~K., et al.\ 2010, \aj, 140, 1868
+%\bibitem[Werner et al.(2004)]{wer04} Werner, M.~W., Roellig, T.~L.,
+%  Low, F.~J., et al.\ 2004, \apjs, 154, 1
+%\bibitem[Wright et al.(2010)]{wri10} Wright, E.~L., Eisenhardt,
+%  P.~R.~M., Mainzer, A.~K., et al.\ 2010, \aj, 140, 1868
 \bibitem[Wuyts et al.(2010)]{wuy10} Wuyts, S., Cox, T.~J., Hayward,

### 2012-04-20 trunk/tex/sigmasfr/ms.tex
version sent around on fri, apr 20

@@
 It has been argued that such feedback imposes a limit on the maximum
-star-formation rate surface density ($\sigmasfr$) for starbursts
+star-formation rate (SFR) surface density ($\sigmasfr$) for starbursts
 \citep[e.g.,][]{leh96,meu97,mur05,tho05} and the maximum stellar
@@
 outflows in these galaxies could have been driven by feedback from
-starbursts with very large star-formation rate (SFR) surface densities
-($\sigmasfr$).  Our analysis combines galaxy sizes obtained with the
-Hubble Space Telescope (HST) with star-formation rates and stellar
-masses estimated using photometry from the Wide-field Infrared Survey
-Explorer (WISE), the Spitzer Space Telescope, the Sloan Digital Sky
-Survey (SDSS), and the Galaxy Evolution Explorer (GALEX).
+starbursts with very large SFR surface densities.  Our analysis
+combines galaxy sizes obtained with the Hubble Space Telescope (HST)
+with SFRs and stellar masses estimated using photometry from the
+Wide-field Infrared Survey Explorer (WISE), the Spitzer Space
+Telescope, the Sloan Digital Sky Survey (SDSS), and the Galaxy
+Evolution Explorer (GALEX).
 
@@
 We used the post--basic calibrated data to perform aperture photometry
-on all sources, and we also used the
-APEX\footnote{http://irsa.ipac.caltech.edu/data/SPITZER/docs/dataanalysistools/tools/mopex/}
-point-source extraction software for photometry of sources in crowded
+on all sources and point-source photometry on sources in crowded
 fields.  We show spectral energy distributions (SEDs) for the three
@@
 
-We estimate IR-based star-formation rates for the 25/29 galaxies with
-WISE 12 or 22~$\mu$m detections by fitting \citet{cha01} templates to
-their 12 and 22~$\mu$m fluxes.  For the 14/29 galaxies with 22~$\mu$m
+We estimate IR-based SFRs for the 25/29 galaxies with WISE 12 or
+22~$\mu$m detections by fitting \citet{cha01} templates to their 12
+and 22~$\mu$m fluxes.  For the 14/29 galaxies with 22~$\mu$m
 detections, this yields SFRs that agree with those obtained from the
@@
 imply large total-IR to mid-IR ratios, characteristic of the most
-luminous galaxies in the local universe
-\citep[e.g.,][]{rie09}.  If we used the most luminous
-local templates for the 8/29 sources with SFRs in the ULIRG regime
-($\sfrir>200$~\msun~yr$^{-1}$), we would obtain SFRs that are larger
-by 0.5~dex than the values we adopt for this paper.
+luminous galaxies in the local universe \citep[e.g.,][]{rie09}.  If we
+used the most luminous local templates for the 8/29 sources with SFRs
+in the ULIRG regime ($\sfrir>200$~\msun~yr$^{-1}$), we would obtain
+SFRs that are larger by 0.5~dex than the values we adopt for this
+paper.
 
-We also estimate star-formation rates and stellar masses based on
-stellar population fits to the $\lrest=0.1$--3~$\mu$m SEDs using the
-method of \citet{mou11}.  For galaxies with
-$\sfrir>50$~\msun~yr$^{-1}$, there is agreement between these UV-based
-SFR estimates and $\sfrir$ with a scatter of 0.32~dex.  For an SMC
-dust law, we find a median attenuation of $A_V=0.4$~mag.
+We also estimate SFRs and stellar masses based on stellar population
+fits to the $\lrest=0.1$--3~$\mu$m SEDs using the method of
+\citet{mou11}.  For galaxies with $\sfrir>50$~\msun~yr$^{-1}$, there
+is agreement between these UV-based SFR estimates and $\sfrir$ with a
+scatter of 0.32~dex.  For an SMC dust law, we find a median
+attenuation of $A_V=0.4$~mag.
 
@@
   sample described in this paper (black circles, with symbol size
-  proportional to outflow velocity), along with samples of gas-rich
-  mergers (orange squares) and star-forming galaxies (shown with 68\%,
-  95\%, and 99.7\% contours).  We mark the empirical threshold for
-  launching winds \citep[dotted line,
+  proportional to outflow velocity), along with samples of $z<0.3$
+  gas-rich mergers (orange squares) and $z\sim1$ star-forming galaxies
+  (shown with 68\%, 95\%, and 99.7\% contours).  We mark the empirical
+  threshold for launching winds \citep[dotted line,
     $\sigmasfr\approx0.1$~\units;][]{hec02}, the 90th-percentile
@@
 high-$\sigmasfr$ sources in Figure~\ref{fig:spectra} based on data
-from MMT/Blue Channel and SDSS (J1506+5402), Magellan/MAGE
+from MMT/Blue Channel and SDSS (J1506+5402), Magellan/MagE
 (J1341-0321), and Keck/LRIS and Keck/HIRES (J0905+5759).  The spectra
@@
 
-The compact sizes ($r_e\approx100$~pc) and large star formation rates
+The compact sizes ($r_e\approx100$~pc) and large SFRs
 ($\textnormal{SFR}\approx300$~\msun) for the galaxies described above
-implies extremely large star-formation rate surface densities
+implies extremely large SFR surface densities
 ($\sigmasfr\approx5000$~\units).  To place these galaxies in context,
@@
 level.  We conclude that the bolometric output of the galaxies in our
-sample is dominated by star and we that our results regarding large
-$\sigmasfr$ values are not affected by AGN contamination.
+sample is dominated by star formation and we that our results
+regarding large $\sigmasfr$ values are not affected by AGN
+contamination.
 
@@
 It is worth considering whether the high-velocity outflows we observe
-were produced by the compact starburst.  \citet{mur11} argued that
-massive star clusters with large gas surface densities are the ideal
-launching point for galactic-scale outflows driven by radiation
-pressure, and that the outflow velocity should scale with escape
-velocity of the most massive star clusters in a galaxy.  The
+could have been produced by the compact starburst.  \citet{mur11}
+argued that massive star clusters with large gas surface densities are
+the ideal launching point for galactic-scale outflows driven by
+radiation pressure, and that the outflow velocity should scale with
+escape velocity of the most massive star clusters in a galaxy.  The
 $\gtrsim1000$~\kms\ outflow velocities we observe correspond
@@
 galaxies since $z\sim2$.  Furthermore, the high-$\sigmasfr$ galaxies
-are caught in a particular time interval where there is both vigorous
-star formation and strong feedback.  The length of this phase may be
-set by the gas consumption timescale or the timescale for feedback to
-suppress subsequent star formation.  Based on the Kennicutt--Schmidt
-(K-S) relation \citep{ken98}, a compact starburst with
-$r_e\approx100$~pc, $\textnormal{SFR}\approx300$~\msun, and
+in our sample are caught in a particular time interval where there is
+both vigorous star formation and strong feedback.  The length of this
+phase may be set by the gas consumption timescale or the timescale for
+feedback to suppress subsequent star formation.  Based on the
+Kennicutt--Schmidt (K-S) relation \citep{ken98}, a compact starburst
+with $r_e\approx100$~pc, $\textnormal{SFR}\approx300$~\msun, and
 $\sigmasfr\approx5000$~\units\ would have a gas surface density of
@@
 as an evolutionary sequence where the high-$\sigmasfr$ galaxies
-represent the peak of the starburst where the high-velocity outflows
+represent the peak of the starburst when the high-velocity outflows
 are launched, while the lower $\sigmasfr$ galaxies represent a
-subseqent, post-starburst phase.  It is interesting to note that all
+subsequent, post-starburst phase.  It is interesting to note that all
 12/29 galaxies above the $\sigmasfr\approx45$~\units\ limit from
@@
 Finally, it is worthwhile to consider the implications of our results
-for models of massive galaxy formation.  Simulaitons of major galaxy
+for models of massive galaxy formation.  Simulations of major galaxy
 mergers with large gas fractions ($f_{gas}\sim50$\%) can produce
@@
 magnitude.  If these systems do evolve into quiescent elliptical
-galaxies, it would be quite challenging for them to grow in size from
-$r_e\sim0.1$~kpc to $r_e\sim5$~kpc to reach the local size--mass
+galaxies, it would be extremely challenging for them to grow in size
+from $r_e\sim0.1$~kpc to $r_e\sim5$~kpc to reach the local size--mass
 relation \citep{she03} in the $t\sim6$~Gyr since $z=0.6$.  For
@@
 peak of starburst activity \citep{wuy10}.  It would be worthwhile to
-test for such size discrepancies and to pronbe the radial dependence
-of the mass-to-light ratio for these galaxies by measuring sizes at
+test for such size discrepancies and to probe the radial dependence of
+the mass-to-light ratio for these galaxies by measuring sizes at
 rest-frame near-IR wavelengths.
@@
 grains, and such compact starburst are expected to have substantial
-momentum input from both massive stars and supernovae.  There is some
+momentum input from massive stars and supernovae.  There is some
 evidence for AGN activity in a fraction of these systems, but the AGN
-is generally not relevant in a bolometric sense.  High-velocity
+is generally not relevant in a bolometric sense.  While high-velocity
 outflows have been previously interpreted as a signpost of AGN
-feedback, but we conclude that stellar feedback from a compact
-starburst is equally capable of producing such a signature.
+feedback, we conclude that stellar feedback from a compact starburst
+is equally capable of producing such a signature.
 

### 2012-05-08 tex/sigmasfr/ms.tex
pre submission version

--- 2012-04-17 trunk/tex/sigmasfr/ms.tex
@@
 \newcommand{\oii}{[\textrm{O}~\textsc{ii}]}
+\newcommand{\hii}{\textrm{H}~\textsc{ii}}
 \newcommand{\oiii}{[\textrm{O}~\textsc{iii}]}
@@
 \newcommand{\sigmasfr}{\Sigma_{\textnormal{\scriptsize{SFR}}}}
-\newcommand {\apgt} {\ {\raise-.5ex\hbox{$\buildrel>\over\sim$}}\ }
-\newcommand {\aplt} {\ {\raise-.5ex\hbox{$\buildrel<\over\sim$}}\ }
+\newcommand{\sfrir}{\textnormal{SFR}_{\textnormal{\scriptsize{IR}}}}
 
-\shorttitle{Compact Starbursts Revealed by HST and WISE}
+\shorttitle{Compact Starbursts Driving High-Velocity Outflows}
 \shortauthors{Diamond-Stanic et al.}
@@
 
-%\title{HST and WISE Reveal Compact Starbursts Driving 1000
-%  \kms\ Outflows}
-
-\title{In the Crucible: Massive Compact Galaxies with High-Velocity
-  Outflows and Eddington-Limited Star Formation}
+\title{High-Velocity Outflows Without AGN Feedback:
+  \\ Eddington-Limited Star Formation in Compact Massive Galaxies}
 
@@
   Alison L. Coil\altaffilmark{1}, Ryan C. Hickox\altaffilmark{4}, Aday
-  Robaina\altaffilmark{5}, Gregory H. Rudnick\altaffilmark{6}, \& Paul
-  Sell\altaffilmark{3} }
+  R. Robaina\altaffilmark{5}, Gregory H. Rudnick\altaffilmark{6}, \&
+  Paul H. Sell\altaffilmark{3} }
 
@@
 
-Based on infrared photometry from the Wide-field Infrared Survey
-Explorer (WISE) and optical morphologies from the Hubble Space
-Telescope (HST), we present the discovery of compact, obscured star
-formation in galaxies that exhibit $1000$~\kms\ outflows.  The implied
-star formation rate (SFR) surface densities approach
-$\sigmasfr=5000$~\msun~yr$^{-1}$~kpc$^{-2}$, and we argue that
-feedback associated with this starburst event is a likely mechanism
-for launching the high-velocity outflows.
+We present the discovery of compact, obscured star formation in
+galaxies at $z\sim0.6$ that exhibit $\gtrsim1000$~\kms\ outflows.
+Using optical morphologies from the Hubble Space Telescope and
+infrared photometry from the Wide-field Infrared Survey Explorer, we
+estimate star formation rate (SFR) surface densities that approach
+$\sigmasfr\approx3000$~\units, comparable to the Eddington limit from
+radiation pressure on dust grains.  We argue that feedback associated
+with a compact starburst in the form of radiation pressure from
+massive stars and ram pressure from supernovae and stellar winds is
+sufficient to produce the high-velocity outflows we observe, without
+the need to invoke feedback from an active galactic nucleus.
 
@@
 The central regions of elliptical galaxies are thought to form in
-compact starbursts \citep[e.g.,][]{kor09,hop09}.  Feedback associated
-with such starbursts can produce outflows driven by thermal energy
-from supernova explosions \citep[e.g.,][]{che85}, stellar winds
-\citep[e.g.,][]{lei92}, and momentum input from both supernova ram
-pressure and radiation pressure on dust grains \citep[e.g.,][]{mur05}.
-It has been argued that such feedback imposes a limit on the maximum
-star-formation rate surface density ($\sigmasfr$) for starbursts
-\citep[e.g.,][]{leh96,meu97,mur05,tho05} and the maximum stellar
-surface density for elliptical galaxies and star clusters
-\citep[e.g.,][]{hop10}.
-
-% The relative importance of momentum injection versus thermal heating
-% may vary as a function of galaxy mass \citep[e.g.,][]{hop12}, with
-% thermal heating being less efficient in galaxies with larger gas
-% densities and shorter cooling times.  Massive star clusters with large
-% gas surface densities are a potential launching point for
-% galactic-scale outflows driven by radiation pressure
-% \citep[e.g.,][]{mur11}.
+compact starbursts \citep{kor09,hop09}.  Feedback associated with such
+starbursts can produce outflows driven by thermal energy from
+supernova explosions \citep{che85}, stellar winds \citep{lei92}, and
+momentum input from both supernova ram pressure and radiation pressure
+on dust grains \citep{mur05}.  It has been argued that such feedback
+imposes a limit on the maximum star-formation rate (SFR) surface
+density ($\sigmasfr$) for starbursts \citep{leh96,meu97,mur05,tho05}
+and the maximum stellar surface density for elliptical galaxies and
+star clusters \citep{hop10}.
 
@@
 redshifts and generally exhibit outflow velocities in the
-100--500~\kms\ range
-\citep[e.g.,][]{hec00,sha03,mar05,rup05,wei09,rub10,ste10}.  Thus, the
-discovery of $|v|>1000$~\kms\ outflows in a sample of massive
+100--500~\kms\ range, which can be attributed to the stellar processes
+described above \citep{hec00,sha03,mar05,rup05,wei09,rub10}.  Outflows
+with significantly higher velocities ($|v|>1000$~\kms) were discovered
+by \citet{tre07} in a sample of massive
 ($\textnormal{\mstar}\approx10^{11}$~\msun) post-starburst galaxies at
-$z\sim0.6$ by \citet{tre07} suggested that a more energetic source,
-such as feedback from an accreting supermassive black hole
-\citep[e.g.,][]{sil98,dim05,deb12}, could have been responsible for
-launching the winds.
+$z\sim0.6$, and it was suggested that a more energetic source such as
+feedback from an accreting supermassive black hole \citep{sil98,dim05}
+may be responsible for launching the winds \citep[see][for a recent
+  review]{fab12}.
 
@@
 for a positive correlation between outflow velocity and starburst
-luminosity \citep[e.g.,][]{mar05,rup05,tre07}, albeit with significant
-scatter.  Furthermore, \citet{hec11} recently found outflows with
-maximum velocities reaching $-1500$~\kms\ in a sample of local
-starbursts with compact nuclei, and argued that such velocities could
-be explained by feedback from massive stars.
+luminosity \citep{mar05,rup05,tre07}, albeit with significant scatter.
+Furthermore, \citet{hec11} recently found outflows with maximum
+velocities reaching $1500$~\kms\ in a sample of local starbursts with
+compact nuclei, and argued that such velocities could be explained by
+a wind that is launched from $r_0\sim100$~pc and driven by feedback
+from massive stars and supernovae.
 
-% $|v|\gtrsim1000$~\kms\
+In this Letter, we measure sizes and SFRs for a sample of massive
+galaxies at $z\sim0.6$ that exhibit $\gtrsim1000$~\kms\ outflows,
+expanding on the initial study by \citet{tre07}.  We seek to test
+whether the energetic outflows in these galaxies could have been
+driven by feedback from starbursts with very large SFR surface
+densities.  Our analysis combines galaxy sizes measured with the
+Hubble Space Telescope (HST) with SFRs and stellar masses estimated
+from Wide-field Infrared Survey Explorer (WISE), Spitzer Space
+Telescope, Sloan Digital Sky Survey (SDSS), and Galaxy Evolution
+Explorer (GALEX) photometry.
 
-In this Letter, we present results for a sample of massive galaxies at
-$z\sim0.6$ that exhibit $|v|\apgt1000$~\kms\ outflows, expanding on
-the sample from \citet{tre07}.  We seek to test whether the energetic
-outflows in these galaxies could have been driven by feedback from
-starbursts with very large star-formation rate (SFR) surface densities
-($\sigmasfr$).  Our analysis combines galaxy sizes obtained with the
-Hubble Space Telescope (HST) with star-formation rates and stellar
-masses estimated from WISE, Spitzer, SDSS, and GALEX photometry.
+% we focus our analysis on the galaxies with the most extreme
+% $\sigmasfr$ values.
 
-% For example, there is evidence for a positive correlation between
-% outflow velocity and starburst luminosity \citep[e.g.,][]{mar05},
-% albeit with significant scatter.  Furthermore, \citet{hec11} recently
-% found outflows reaching velocities of $-1500$~\kms\ in a sample of
-% local starbursts with compact nuclei, and argued their higher
-% velocities could be explained by feedback exerted by a large number of
-% massive stars that are confined to a small radius.
-
-% [which has been invoked theoretically as
-%  a mechanism to quench star formation in galaxies,
-
-% Winds are also common in active galactic nuclei (AGNs) with velocities
-% in the 1000--20,000~\kms range \citep[e.g., ][]{cre03}, although it is
-% unclear whether AGN feedback plays an important role in regulating
-% star formation in galaxies.  There is clear observational evidence
-% that active galactic nuclei (AGNs) produce outflows
-% \citep[e.g.,][]{cre03} and that the outflowing gas can extend to
-% $>$kpc scales \citep[e.g.,][]{rup11}, it is unclear whether such
-% feedback plays an important role globally in quenching star formation.
-
-% Feedback from massive stars and active black holes has important
-% implications for galaxy evolution (e.g., luminosity function, star
-% formation, galaxy color bi-modality, mass-metallicity relation,
-% enrichment of IGM).
-
-% Feedback from accreting supermassive black holes has also been invoked
-% theoretically as a mechanism for quenching star formation in galaxies
-% \citep[e.g.,][]{sil98,gra04,dim05}.  There is clear observational
-% evidence that active galactic nuclei (AGNs) produce outflows
-% \citep[e.g.,][]{cre03} and that the outflowing gas can extend to
-% $>$kpc scales \citep[e.g.,][]{rup11}, but it is unclear whether such
-% feedback plays an important role globally in quenching star formation
-% and shaping the galaxy mass function.
-
-% and optical spectra ($\lrest=2500$-5200~\AA)
-
-%  The spectral region surrounding the
-%  \mgii~$\lambda\lambda2796,2803$ absorption alines, which are used to
-%  measure outflow velocities, is highlighted in both wavelength and
-%  velocity space.
-
-%  and are scaled to match the WISE channel 2 photometry ($\lobs=4.6$~$\mu$m)
-% (\mgii~$\lambda2796$ is plotted in blue and \mgii~$\lambda2803$ is plotted in red)
+\begin{figure}[!t]
+\includegraphics[angle=0,scale=0.41]{f1.ps}
+\caption{Left: Observed UV--IR SEDs ($\lrest=0.1$--15~$\mu$m) for
+  three galaxies with the largest SFR surface densities
+  ($\sigmasfr\approx3000$~\units).  The top two SEDs are offset by 5
+  and 10 magnitudes, respectively.  We show stellar population fits to
+  the $\lrest=0.1$--3~$\mu$m emission (black solid line) and three
+  templates for dust emission \citep[M82 starburst, blue dashed line;
+    Arp 220 starburst, green dot-dashed line; obscured quasar, red
+    dotted line;][]{pol07} scaled to match the $\lobs=4.6~\mu$m band.
+  The starburst templates provide reasonable fits to the $\lobs=12$
+  and 22~$\mu$m WISE photometry, while the quasar template does not.
+  Right: HST/WFC3 F814W images (probing $\lrest\approx5000$~\AA)
+  showing that these galaxies are dominated by a compact nucleus.}
+\label{fig:seds}
+\end{figure}
 
@@
 
-\subsection{HST/WFC3 Imaging}
+\subsection{Morphologies and Sizes}
 
-Our sample derives from 29 galaxies targeted for HST/WFC3 imaging in
-programs 12019 and 12272 (PI: C. Tremonti).  Using the F814W filter on
-the UVIS channel, which has $0.04\arcsec$ pixels and
-$\textnormal{FWHM}=0.074\arcsec$, we obtained $4\times10$~min
-exposures in a single orbit for each galaxy.  The dithered images were
-processed with
+We observed 29 galaxies with HST (programs 12019 and 12272) selected
+from a parent sample of $\sim10^3$ galaxies at $0.35<z<1.0$ with
+post-starburst spectral features: B or A-star dominated stellar
+continua and moderately weak nebular emission
+($\textnormal{EW}(\oii)<20$~\AA; see C. Tremonti, et al., in
+preparation for more details).  The galaxies targeted with HST were
+those with the youngest derived post-burst ages
+$t_{burst}\lesssim300$~Myr.  Thus, by design, this sample has bluer
+$U-B$ colors and stronger emission lines than typical post-starburst
+samples \citep{coi11}.  Our subsequent UV--IR SED analysis (see
+Section~\ref{sec:seds}) reveals significant ongoing star formation
+($\textnormal{SFR}>50$~\msun~yr$^{-1}$) in the 14/29 galaxies with
+WISE 22~$\mu$m detections, calling into question the post-starburst
+nature of roughly half of the HST sample.
+
+Using the F814W filter on the WFC3/UVIS channel, which has
+$0.04\arcsec$ pixels, we obtained $4\times10$~min exposures in a
+single orbit for each galaxy.  The dithered images were processed with
 MultiDrizzle\footnote{http://stsdas.stsci.edu/multidrizzle/} to
 produce science mosaics with $0.02\arcsec$ pixels.  For each galaxy,
-we use GALFIT \citep{pen02,pen10} to model the two-dimensional surface
-brightness profile with a single Sersic component, using stars in the
-images to construct the model point-spread function (PSF).  The Sersic
-index (n) and effective radius ($r_e$) are free parameters in the
-model.  In cases where the best-fit model returns $n>4$, we also fit
-an $n=4$ de Vaucouleurs model \citep{dev48}, yielding a larger $r_e$
-value (due to the covariance between $n$ and $r_e$), and we use these
-these larger effective radii in our analysis.
+we use GALFIT \citep{pen02} to model the two-dimensional surface
+brightness profile with a single Sersic component (characterized by
+Sersic index $n$ and effective radius $r_e$), using stars in the
+images to construct the model point-spread function (PSF).  In cases
+where the best-fit model returns $n>4$, we also fit an $n=4$ de
+Vaucouleurs model, yielding a larger $r_e$ value (due to the
+covariance between $n$ and $r_e$), and we use these these larger
+effective radii in our analysis.
 
-For this paper, we are most interested in the galaxies with the
-largest $\sigmasfr$ values, which also have the smallest effective
-radii.  We show the HST images for three high-$\sigmasfr$ galaxies in
-Figure~\ref{fig:seds}.  In all three cases, the single-component model
-GALFIT accounts for $>85\%$ of the total flux.  The residuals show
-diffuse emission that is consistent with these systems being
-late-stage galaxy mergers after final coalescence, although we defer a
-detailed comparison of the observed morphologies with expectations
+In this Letter, we highlight the galaxies with the smallest $r_e$ and
+largest $\sigmasfr$ values because such extreme starbursts could
+conceivably produce the high-velocity outflows we observe (see
+Section~\ref{sec:discussion}).  We show HST images for the three
+highest $\sigmasfr$ galaxies in Figure~\ref{fig:seds}.  In all three
+cases, the single-component GALFIT model accounts for $>85\%$ of the
+total flux.  The residuals show diffuse emission that is consistent
+with these systems being late-stage galaxy mergers, although we defer
+a detailed comparison of the observed morphologies with expectations
 from merger simulations to future work.
@@
 100~pc), we also show the observed one-dimensional surface brightness
-profile in the bottom-right panel of Figure~\ref{fig:profile}.  We
-compare to the profiles of six stars in the same image, the best-fit
-de Vaucouleurs model, and a de Vaucoulerus model with a larger
-effective radius ($r_e=0.04\arcsec$, the native WFC3/UVIS pixel size,
-which corresponds to a physical scale of 290~pc).  This comparison
-illustrates that this galaxy, while only marginally resolved with an
-effective radius that is $\sim20\%$ of the image FWHM, is clearly more
-extended than a point source.
+profile in Figure~\ref{fig:profile}.  We compare to the profiles of
+six stars in the same image, the best-fit de Vaucouleurs model, and a
+de Vaucouleurs model with $r_e=0.04\arcsec$ (the native WFC3/UVIS
+pixel size, which corresponds to a physical scale of 290~pc).  This
+comparison illustrates that this galaxy, while only marginally
+resolved with an $r_e$ that is $\sim20\%$ of the image FWHM, is
+clearly more extended than a point source.
 
-For such a compact source, there is significant uncertainty in our
-$r_e$ measurement given uncertainties in the model PSF.  To quantify
-this uncertainty, we used TinyTim to generate a model PSF that is
-artificially narrower than the stars in the image (convolving the
-output of tiny2 with a $\textnormal{FWHM}=0.04\arcsec$ Gaussian,
-whereas the image FWHM is $0.074\arcsec$) and found that this
-increased the effective radius in the GALFIT model by a factor of two.
-We also fit a two-component PSF+Sersic model, but found that the
-Sersic component dominates the fit, yielding a similar effective
-radius.  Furthermore, the spectrum of the galaxy shows no evidence for
-an AGN contribution to the $I$-band continuum (see
-Figure~\ref{fig:spectra}), so there is no clear motivation for
-including an unresolved, point-source component in the model.  We
-conclude that this galaxy is quite compact and that our $r_e$ estimate
-of 100~pc, while uncertain, is likely accurate within a factor of two.
+For such a compact source, there is uncertainty in our $r_e$
+measurement given uncertainties in the model PSF.  To quantify this,
+we used TinyTim to generate a model PSF that is narrower than the
+stars in the image (convolving with a $\textnormal{FWHM}=0.04\arcsec$
+Gaussian, whereas the image FWHM is $0.074\arcsec$) and found that
+this increased the $r_e$ in the GALFIT model by a factor of two.  We
+also fit a two-component PSF+Sersic model, but found that the Sersic
+component dominates the fit, yielding a similar $r_e$.  Furthermore,
+the spectrum of the galaxy shows no evidence for an AGN contribution
+to the optical continuum (see Figure~\ref{fig:spectra}), so there is
+no clear motivation for including an unresolved, point-source
+component in the model.  We conclude that this galaxy is quite compact
+and that our $r_e$ estimate is accurate within a factor of two.
 
 \begin{figure}[!t]
-%\includegraphics[angle=90,scale=0.68]{sigmasfr_datafigure.ps}
-\includegraphics[angle=0,scale=0.41]{3seds.ps}
-\caption{Left: Observed UV--IR SEDs ($\lrest=0.1$--15~$\mu$m) for
-  three galaxies with large SFR surface densities
-  ($\sigmasfr>3000$~\units).  We show stellar population fits to the
-  $\lrest=0.1$--3~$\mu$m emission (black solid line) and three
-  templates for dust emission \citep[M82 starburst, Arp 220 starburst,
-    and obscured quasar;][]{pol07}.  The starburst templates provide
-  reasonable fits to the $\lobs=12$ and 22~$\mu$m WISE photometry,
-  while the quasar template does not.  Right: HST/WFC3 F814W images
-  (probing $\lrest\approx5000$~\AA) showing that these galaxies are
-  dominated by a compact nucleus.}
-\label{fig:seds}
-\end{figure}
-% scaled to the WISE $\lobs=4.6~\mu$m flux.
-
-\begin{figure}[!t]
-\includegraphics[angle=0,scale=0.41]{profile.ps}
-\label{fig:profile}
+\includegraphics[angle=0,scale=0.41]{f2.ps}
 \caption{One-dimensional surface brightness profile for J0905+5759,
@@
   profile is shown as the solid black line, and the profiles of six
-  stars in the same image are shown in blue.  The best-fit de
-  Vaucouleurs profile with $r_e=100$~pc is shown as a dashed red line,
-  and for comparison a broader profile with $r_e=0.04\arcsec=290$~pc
-  is shown as the dotted green line.  This galaxy is quite compact,
-  but is more extended than a point source.}
+  stars in the same image are shown in blue, normalized to the same
+  central surface brightness.  The best-fit de Vaucouleurs profile
+  with $r_e=100$~pc is shown as a dashed red line, and for comparison
+  a broader profile with $r_e=0.04\arcsec=290$~pc is shown as the
+  dotted green line.  This galaxy is quite compact, but is more
+  extended than a point source.}
+\label{fig:profile}
 \end{figure}
 
-\subsection{Photometry, Stellar Masses, and Star-formation rates}
+\subsection{Star Formation Rates and Stellar Masses}\label{sec:seds}
 
-We gathered photometry from the All-Sky Release of the Wide-field
-Infrared Survey Explorer \citep[WISE,][]{wri10}, the Seventh Data
-Release of the Sloan Digital Sky Survey \citep[SDSS,][]{aba09}, and
-General Release 6 from the Galaxy Evolution Explorer (GALEX).  We also
-obtained $5\times30$~sec dithered exposures in the 3.6~$\mu$m and
-4.5~$\mu$m for all sources with the Infrared Array Camera
-\citep{faz04} on the Spitzer Space Telescope \citep{wer04} as part of
-General Observer program 60145 (PI: C. Tremonti).  We used the
-post--basic calibrated data to perform aperture photometry on all
-sources, and we also used the
-APEX\footnote{http://irsa.ipac.caltech.edu/data/SPITZER/docs/dataanalysistools/tools/mopex/}
-point-source extraction software for photometry of sources in crowded
-fields.  All the photometry was corrected for Galactic extinction
-based on the \citet{sch98} dust maps.  We show spectral energy
-distributions (SEDs) for the three high-$\sigmasfr$ galaxies in
-Figure~\ref{fig:seds}.
+% We gathered photometry from the All-Sky Release of the Wide-field
+% Infrared Survey Explorer \citep[WISE,][]{wri10}, the Seventh Data
+% Release of the Sloan Digital Sky Survey \citep[SDSS,][]{aba09}, and
+% General Release 6 from the Galaxy Evolution Explorer
+% \citep[GALEX,][]{mar05galex}.  
+We gathered photometry from the WISE All-Sky Release, the SDSS Seventh
+Data Release, and GALEX General Release 6.  We also obtained
+$5\times30$~sec dithered exposures at 3.6~$\mu$m and 4.5~$\mu$m for
+all sources with the Infrared Array Camera on the Spitzer Space
+Telescope as part of GO program 60145.  We used the post--basic
+calibrated data to perform aperture photometry on all sources and
+point-source photometry on sources in crowded fields.  We show
+spectral energy distributions (SEDs) for the three highest $\sigmasfr$
+galaxies in Figure~\ref{fig:seds}.
 
-We estimate IR-based star-formation rates for the 25/29 galaxies with
-WISE 12~$\mu$m detections by fitting \citet{cha01} templates to their
-12 and 22~$\mu$m fluxes.  For the 14/29 galaxies with 22~$\mu$m
-detections, the method of \citet{ruj12} yields SFRs that agree with
-the above values within 0.05~dex.  We note that the shape of the IR
-SED for star-forming galaxies depends on the surface density of star
-formation \citep[e.g.,][]{ruj11,elb11}, with more compact starbursts
-having larger total-IR (8--1000~$\mu$m) to mid-IR (8--24~$\mu$m)
-ratios.  The extreme $\sigmasfr$ values of our sample imply large
-total-IR to mid-IR ratios, characteristic of the most luminous
-galaxies in the local universe \citep[e.g.,][]{cha01,dal02,rie09}.
-For the 8/29 sources where we estimate $SFR_{IR}>200$~\msun~yr$^{-1}$
-above, using the most luminous local templates would yield SFRs that
-are larger by 0.5~dex.
+% All the photometry was corrected for Galactic extinction
+% based on the \citet{sch98} dust maps.
 
-We also estimate star-formation rates and stellar masses based on
-stellar population fits to the $\lrest=0.1$--3~$\mu$m SEDs using the
-method of \citet{mou11}.  For galaxies with
-$SFR_{IR}>50$~\msun~yr$^{-1}$, there is agreement between these
-UV-optical-based estimates and $SFR_{IR}$ with a scatter of 0.32~dex.
+We estimate IR-based SFRs for the 25/29 galaxies with WISE 12 or
+22~$\mu$m detections by fitting \citet{cha01} templates to their 12
+and 22~$\mu$m fluxes.  For the 14/25 galaxies with 22~$\mu$m
+detections, this yields SFRs that agree with those obtained from the
+\citet{ruj12} method based on 24~$\mu$m luminosity with a scatter of
+0.05~dex.  We note that several authors have shown that the shape of
+the IR SED for star-forming galaxies depends on $\sigmasfr$
+\citep{ruj11,elb11}, with more compact starbursts having larger
+total-IR (8--1000~$\mu$m) to mid-IR (8--24~$\mu$m) ratios,
+characteristic of the most luminous galaxies in the local universe
+\citep{rie09}.  If we used the most luminous local templates for the
+8/25 sources with SFRs in the ULIRG regime
+($\sfrir>100$~\msun~yr$^{-1}$), we would obtain SFRs that are larger
+by 0.5~dex than the values we adopt for this paper.
+
+We also estimate SFRs and stellar masses based on stellar population
+fits to the $\lrest=0.1$--3~$\mu$m SEDs using the method of
+\citet{mou11}.  For the 14/25 galaxies with
+$\sfrir>50$~\msun~yr$^{-1}$, there is agreement between these UV-based
+SFR estimates and $\sfrir$ with a scatter of 0.32~dex.  For an SMC
+dust law, we find a median attenuation of $A_V=0.4$~mag.  We note that
+the observed H$\beta$ luminosities, uncorrected for dust extinction,
+are typically factors of 10--$20\times$ smaller than expected from the
+UV and IR SFRs.  This can be reconciled by either strong differential
+dust attenuation (i.e., $A_V\approx2$--3~mag for the line-emitting
+region), escaping ionizing photons from matter-bounded \hii\ regions,
+or a recently quenched starburst ($t>5~$Myr) with a small ratio of
+ionizing ($\lambda<912$~\AA) to non-ionizing UV photons.
 
 \begin{figure}[!t]
-\includegraphics[angle=0,scale=0.41]{spectra.ps}
+\includegraphics[angle=0,scale=0.41]{f3.ps}
 \caption{Spectra covering $\lrest=2500$--5200~\AA\ for the three
-  galaxies shown in Figure~\ref{fig:seds}.  These spectra are
-  dominated by light from the young stellar population and exhibit
-  \oii~$\lambda3727$, H$\beta$~$\lambda4861$, and \oiii~$\lambda5007$
-  emission lines.  The panels on the right zoom on the
-  \mgii~$\lambda\lambda2796,2803$ spectral region in both wavelength
-  and velocity space.  The spectrum in the bottom panel has sufficient
-  spectral resolution ($\textnormal{FWHM}\approx8$~\kms) to resolve
-  the intrinsic shape of the absorption-line profile, revealing that
-  the gas near the centroid velocity has unity covering factor.}
+  galaxies shown in Figure~\ref{fig:seds}.  For clarity the top two
+  spectra are offset by $+10$ and $+20$ units.  These spectra are
+  dominated by the light of a young stellar population but have
+  relatively weak nebular emission lines (\oii~$\lambda3727$,
+  H$\beta$~$\lambda4861$, \oiii~$\lambda5007$) and strong
+  \mgii~$\lambda\lambda2796,2803$ absorption arising from the
+  interstellar medium.  The absense of broad \mgii\ or H$\beta$
+  emission lines rules out a significant contribution to the optical
+  continuum light from an AGN.  The panels on the right highlight the
+  region around the \mgii\ doublet in both wavelength and velocity
+  space to illustrate the outflow kinematics.  The spectrum in the
+  bottom panel has sufficient spectral resolution
+  ($\textnormal{FWHM}\approx8$~\kms) to resolve the intrinsic shape of
+  the absorption-line profile, revealing that the gas near the
+  centroid velocity ($v=-2470$~\kms) covers the entire galaxy.}
 \label{fig:spectra}
@@
 \begin{center}
-\includegraphics[angle=0,scale=.8]{sigmasfr.ps} %\\
-%\includegraphics[angle=0,scale=.7]{sizemass_sigmasfr.ps}
-%\caption{$\sigmasfr$--mass and size--mass relationships.}
+\includegraphics[angle=0,scale=.8]{f4.ps} 
 \caption{SFR surface densities and stellar masses for the HST--WISE
   sample described in this paper (black circles, with symbol size
-  proportional to outflow velocity), along with samples of gas-rich
-  mergers (orange squares) and star-forming galaxies (shown with 68\%
-  contours).  We mark the empirical threshold for launching winds
-  \citep[dotted line, $\sigmasfr=0.1$~\units;][]{hec02}, the
-  90th-percentile starburst intensity limit from \citet{meu97} (dashed
-  line, $\sigmasfr=45$~\units), and the Eddington limit from radiation
+  proportional to outflow velocity), along with samples of $z<0.3$
+  gas-rich mergers (orange squares) and $z\sim1$ star-forming galaxies
+  (shown with 68\%, 95\%, and 99.7\% contours).  We mark the empirical
+  threshold for launching winds \citep[dotted line,
+    $\sigmasfr\approx0.1$~\units;][]{hec02}, the 90th-percentile
+  starburst intensity limit from \citet{meu97} (dashed line,
+  $\sigmasfr\approx25$~\units), and the Eddington limit from radiation
   pressure on dust grains \citep[solid line,
-    $\sigmasfr\approx2000$~\units;][]{mur05,tho05,hop10}.  Our
-  HST--WISE sample overlaps with the region characterized by gas-rich
-  mergers, and extends to very large SFR surface densities near the
-  Eddington limit.  The sample of gas-rich mergers includes ULIRGs
-  \citep{vei06}, Lyman break analogs with dominant central objects
-  \citep{ove09}, and the local compact starburst Arp 220 \citep{sco97,
-    ken98, rod08}.  The samples of star-forming galaxies are drawn
-  from \citet{wuy11} at $0.02<z<0.2$ (solid black contour),
-  $0.5<z<1.5$ (dashed red countour), and $1.5<z<2.5$ (dotted purple
-  contour), and from \citet{law12} at $2.5<z<3.6$ (dash-dotted blue
-  contour). }
+    $\sigmasfr\approx3000$~\units;][]{mur05,tho05,hop10}.  The
+  representative error bar in the top-right portion of the plot
+  corresponds to uncertainties of 0.3~dex in $\sigmasfr$ and 0.2~dex
+  in stellar mass.  Our HST--WISE sample overlaps with the region
+  characterized by gas-rich mergers, and extends to very large SFR
+  surface densities near the Eddington limit, suggesting growth that
+  is limited by momentum injection from massive stars.}
 \label{fig:sigmasfr}
@@
 
-\subsection{Optical Spectroscopy}
+\subsection{Outflow Kinematics and Covering Factors}
 
-We present low-resolution $R=1000-3000$ spectroscopy from MMT/Blue
-Channel and SDSS (J1506+5402), Magellan/MagE (J1341-0321), and
-Keck/LRIS (J0905+5759) in Figure~\ref{fig:spectra.}.  We also
-highlight the \mgii~$\lambda\lambda2796,2803$ absorption lines, which
-are used use to measure outflow velocities.
+We present $\lrest=2500$--5200~\AA\ spectroscopy for three
+high-$\sigmasfr$ sources in Figure~\ref{fig:spectra} based on data
+from MMT/Blue Channel and SDSS (J1506+5402), Magellan/MagE
+(J1341-0321), and Keck/LRIS and Keck/HIRES (J0905+5759).  The spectra
+are dominated by light from a young ($t<50$~Myr) stellar population.
+We highlight the interstellar medium \mgii~$\lambda\lambda2796,2803$
+absorption lines, which are used to measure outflow velocities.  At
+low spectral resolution (e.g., the top right panel of
+Figure~\ref{fig:spectra}) it is not possible to determine the
+intrinsic shape of the absorption line profile and therefore the
+covering factor of the outflowing gas.  However, the Keck/HIRES
+spectrum of J0905+5759 ($\textnormal{FWHM}\approx8$~\kms) reveals that
+the gas covers the entire continuum source near the velocity centroid
+($v=-2470$~\kms) indicating a galaxy-wide outflow.
 
-For J0905+5759 we show the \mgii\ absorption-line profiles from
-$R\approx37,000$ spectra obtained with Keck/HIRES.  The oscillator
-strength of \mgii~$\lambda$2796 is twice that of \mgii~$\lambda$2803,
-but the equivalent widths of the two lines and the shapes of the line
-profiles are quite similar, indicating that both lines are optically
-thick.  The fact that the absorption line profile approaches zero near
-the velocity centroid $v=-2470$~\kms\ indicates that the outflowing
-gas covers the entire continuum source at these velocities.
+\section{Discussion}\label{sec:discussion}
 
-%\section{Analysis}
-%
-%\subsection{Star-formation Rates and Stellar Masses}
-%
-%\subsection{Morphologies and Sizes}
-%
-%\subsection{Outflow Kinematics and Covering Factors}
+The compact sizes ($r_e\approx100$~pc) and large SFRs
+($\textnormal{SFR}\approx200$~\msun) for the three galaxies described
+above imply extremely large SFR surface densities
+($\sigmasfr\approx3000$~\units).  To place these galaxies in context,
+we plot $\sigmasfr$ versus stellar mass for the 25/29 galaxies
+detected by WISE in Figure~\ref{fig:sigmasfr}.  We include comparison
+samples of $\sim10^5$ star-forming galaxies at $0.5<z<1.5$ from
+\citet{wuy11} and a few dozen gas-rich mergers at $z<0.3$ including 32
+ULIRGs from \citet{vei06}, five Lyman break analogs with dominant
+central objects from \citet{ove09}, and the local compact starburst
+Arp 220 \citep{sco97, ken98, rod08}.  We also mark the empirical
+threshold for launching winds
+\citep[$\sigmasfr\approx0.1$~\units,][]{hec02}, the 90th percentile
+limit for the surface brightness of starbursts over a wide range in
+redshift measured using UV, H$\alpha$, far-IR, and radio continuum
+emission \citep[$\sigmasfr\approx25$~\units\ for a Chabrier
+  IMF,][]{meu97}, and the theoretical limit for a starburst limited by
+feedback from radiation pressure
+\citep[$\sigmasfr\approx3000$~\units,][]{mur05,tho05,hop10}.  The most
+luminous, compact starbursts in our sample exhibit SFR surface
+densities that reach the Eddington limit, suggesting that their growth
+is being regulated by momentum input from massive stars.
 
-% \begin{figure*}[!t]
-% \begin{center}
-% \includegraphics[angle=0,scale=.8]{sizemass_sigmasfr.ps}
-% \caption{size--mass relationship.}
-% \label{fig:sizemass}
-% \end{center}
-% \end{figure*}
+\subsection{Constraints on Ongoing AGN Activity}
 
-% %\begin{center}
-% \begin{deluxetable}{ccccccc}
-% \tabletypesize{\scriptsize}
-% 
-% \tablecaption{Galaxy Properties\label{tab:properties}}
-% \tablewidth{0pt}
-% 
-% \tablehead{ \colhead{Galaxy Name} & \colhead{z} & \colhead{$M_{*}$} & \colhead{$v$} & \colhead{SFR} & \colhead{$r_e$} & \colhead{$\sigmasfr$} }
-% 
-% \startdata
-% J150636.29+540220.7   & 0.608 & 11.01 & -1211 &  621 & 0.13 & 5851 \\
-% J090523.60+575912.4   & 0.712 & 10.62 & -2470 & 344 & 0.10 & 5478 \\ 
-% %J094417.84+093019.3   & 0.514 & 10.73 & -1778 & $<43.22$ & 161 & 0.15 & 1139 \\
-% J134136.79$-$032125.2   & 0.658 & 10.61 & -875  & 490 & 0.16 & 3058 \\ 
-% % J1506 has Lx=42.66
-% \enddata
-% 
-% %\tablecomments{}
-% %\tablenotetext{a}{Star-formation rate based on \citet{ken98}.  No extinction correction has been applied.}
-% 
-% \end{deluxetable}
-% %\end{center}
+While the SEDs (Figure~\ref{fig:seds}) and optical spectra
+(Figure~\ref{fig:spectra}) for our sample indicate that their
+bolometric output is dominated by star formation, it is worthwhile to
+consider the level of ongoing AGN activity and its effect on our
+measurements.  Among the high-$\sigmasfr$ galaxies, the strongest case
+for detectable AGN emission can be made for J1506+5402, which has the
+most luminous \oiii~$\lambda5007$ line in the HST sample.  This source
+also has a weak \nev~$\lambda3426$ emission line, which is associated
+with AGN activity \citep{gil10}.  It was observed with the Chandra
+X-ray Observatory (proposal ID 11700896) and had four detected counts,
+corresponding to a 0.5--8.0~keV X-ray luminosity of
+$10^{42.7}$~erg~s$^{-1}$ (see P. Sell et al., in preparation for more
+details on the 12/29 galaxies with Chandra observations).  Using the
+relationship between 2--10~keV X-ray and 12.3~$\mu$m mid-IR luminosity
+for AGNs from \citet{gan09}, one would expect a source with
+$L_{\textnormal{\scriptsize{X}}}\approx5\times10^{42}$~erg~s$^{-1}$ to
+have
+$L_{\textnormal{\scriptsize{MIR}}}\approx7\times10^{42}$~erg~s$^{-1}$,
+which is 400$\times$ smaller than observed luminosity for J1506+5402
+($L_{\textnormal{\scriptsize{MIR}}}\approx3\times10^{45}$~erg~s$^{-1}$).
+Based on its \oiii\ luminosity ($10^{42.1}$~erg~s$^{-1}$, which may
+also include a contribution from star formation) and the calibration
+for type 1 AGNs from \citet{hec05}, one would expect an intrinsic
+2--10~keV luminosity of
+$L_{\textnormal{\scriptsize{X}}}\approx5\times10^{43}$~erg~s$^{-1}$,
+suggesting absorption by a factor of $\sim10$ in the X-rays.  However,
+even if the X-ray attenuation were a factor of 100, which is the
+typical value for local Compton-thick AGNs \citep{dia09}, the expected
+mid-IR AGN contribution would only be relevant at the $\lesssim$30\%
+level.  We conclude that the bolometric output of the galaxies in our
+sample is dominated by star formation and that our results regarding
+large $\sigmasfr$ values are not affected by AGN contamination.
 
-\section{Discussion}
+% Thus, similar to local ULIRGs \citep[e.g.,][]{far07}, the
+% bolometric output of the galaxies in our sample is dominated by star
+% formation, and we conclude that our results regarding large
+% $\sigmasfr$ values are not affected by AGN contamination.
 
-The compact sizes ($r_e\approx100$~pc) and large star formation rates
-($\textnormal{SFR}\approx500$~\msun) for the galaxies shown in
-Figure~\ref{fig:seds} imply extremely large star-formation rate
-surface densities ($\sigmasfr\approx5000$~\units).  To place these
-galaxies in context, we plot their $\sigmasfr$ values as a function of
-stellar mass in Figure~\ref{fig:sigmasfr}.  We also include
-measurements of late-stage, gas-rich mergers at $z<0.3$ from
-\citet{vei06}, star-forming galaxies at $z<0.3$ from \citet{ove09},
-and star-forming galaxies at $z=1.5$--3.6 from \citet{law12}.
+\subsection{The Outflow Launching Mechanism}\label{sec:launch}
 
-Points to make:
-\begin{itemize}
-\item \citet{ken98}, the standard reference for the relationship
-  between SFR and gas surface density, includes Arp 200 with
-  $\sigmasfr\approx10^3$~\units\ and
-  $\Sigma_{H_2}\approx5\times10^{10}$~\msun~kpc$^{-2}$.  
-\item The star clusters considered by \citet{meu97} extend into this
-  $\sigmasfr>10^{3}$~\units\ range.
+Are the high-velocity outflows observed in these galaxies produced by
+a compact starburst?  \citet{mur11} argued that massive star clusters
+with large gas surface densities are the ideal launching point for
+galactic-scale outflows driven by radiation pressure, and that the
+outflow velocity should scale with escape velocity of the most massive
+star clusters in a galaxy.  For our sample, if one assumes that the
+spatial extent of the stellar mass is comparable to that of the
+rest-frame $V$-band light (see Section~\ref{sec:context}), then half
+of the stellar mass ($\textnormal{\mstar}\sim10^{11}$~\msun) will be
+within the effective radius ($r_{e}\sim100$~pc).  Such a compact
+stellar population would have an escape velocity comparable to the
+$\gtrsim1000$~\kms\ outflow velocities we observe:
+\begin{eqnarray}\nonumber
+v_{esc}&=&\sqrt{2GM_{*}/r} \\
+&=& 2100
+\left({M_{*}\over10^{11} M_{\odot}}\right)^{1/2} 
+\left({r\over200~\textnormal{pc}}\right)^{-1/2}
+\textnormal{km~s}^{-1} 
+\label{eq:vesc}
+\end{eqnarray}
+This argument, combined with the fact that we observe galaxies with
+significant dust-obscured star formation and $\sigmasfr$ values near
+the Eddington limit, suggests that momentum input from massive stars
+in the form of radiation pressure is a viable mechanism for launching
+these outflows.
 
-\end{itemize}
+In addition to radiation pressure, we also expect significant momentum
+flux from stellar winds and supernovae.  For example, a starburst with
+$\textnormal{SFR}\approx200$~\msun~yr$^{-1}$ would be associated with
+radiation pressure $L_{bol}/c\approx3\times10^{35}$~dyne and ram
+pressure $\dot{p}\approx5$--$10\times10^{35}$~dyne from stellar winds
+and supernovae \citep{lei92,lei99,vei05}.  Furthermore, \citet{hec11}
+noted that such a large momentum injection
+($\dot{p}\approx10^{35}$~dyne) from a small initial radius
+$r_{0}\approx100$~pc could accelerate a cloud with column density
+$N_{H}\approx10^{21}$~cm$^{-2}$ to a terminal velocity
+$v_{\infty}\approx1800$~\kms.  Thus, the energetics of compact
+starbursts are sufficient to produce the high-velocity outflows we
+observe, and it is plausible that both radiation pressure on dust
+grains and supernova ram pressure contribute to driving the winds.
 
-% We show relationship between effective radius and stellar mass for our
-% WISE-HST sample in bottom panel of Figure~\ref{fig:sizemass}.  Here,
-% we include the gas-rich mergers from \citet{vei06} as well as
-% $z\sim2.3$ compact massive galaxies from \citet{van08}.  We also show
-% the size--mass relationship for elliptical galaxies at $z\sim0.1$ from
-% \citet{she03}, and the average size evolution of spheroidal ($n>2.5$)
-% galaxies from $z=2$ to $z=0.1$ from \citet{tru07}.
+\subsection{Placing These Galaxies in Context}\label{sec:context}
 
-%\subsection{A Maximum Star-Formation Rate Surface Density?}
+It is clear from Figure~\ref{fig:sigmasfr} that the high-$\sigmasfr$
+galaxies in our sample constitute a rare population, suggesting that
+they represent an unusual or short-lived phase.  Mergers of gas-rich
+galaxies are a viable mechanism for producing compact starbursts
+\citep{mih96}, and such gas-rich major mergers are rare at $z\sim0.6$
+due to the decline in both the gas fraction \citep{tac10} and the
+fractional major merger rate \citep{lot11} of galaxies since $z\sim2$.
+Furthermore, the high-$\sigmasfr$ galaxies in our sample are caught in
+a particular time interval where there is both vigorous star formation
+and strong feedback.  The length of this phase may be set by the gas
+consumption timescale or the timescale for feedback to suppress
+subsequent star formation.  Based on the Kennicutt--Schmidt (K-S)
+relation \citep{ken98}, a compact starburst with $r_e\approx100$~pc,
+$\textnormal{SFR}\approx200$~\msun, and
+$\sigmasfr\approx3000$~\units\ would have a gas surface density of
+$\Sigma_{gas}\sim10^{11}$~\msun~kpc$^{-2}$ corresponding to
+$M_{gas}\sim3\times10^{9}$~\msun\ inside 100~pc, which would be
+consumed on a timescale $\sim20$~Myr.  This scenario could be tested
+with CO observations of molecular gas masses and kinematics for these
+extreme galaxies.
 
-\subsection{Momentum Flux from Supernovae and Stellar Winds}
+Considering our full HST--WISE sample in Figure~\ref{fig:sigmasfr}, we
+find values of $\sigmasfr$ spanning four orders of magnitude.  This
+could be explained as an evolutionary sequence where the
+high-$\sigmasfr$ galaxies represent the peak of the starburst when the
+high-velocity outflows are launched, while the lower $\sigmasfr$
+galaxies represent a subsequent, post-starburst phase.  It is
+interesting to note that all 12/25 galaxies above the
+$\sigmasfr\approx25$~\units\ limit from \citet{meu97} exhibit outflows
+(with median centroid velocity $v=-1500$~\kms), while all 7/25
+galaxies without detected outflows (the smallest black circles in
+Figure~\ref{fig:sigmasfr}) have $\sigmasfr<20$~\units.  If a compact
+starburst is a requirement for the production of high-velocity
+outflows, it may be that the sources without outflows have not gone
+through such a phase (see A. Robaina, et al., in preparation for a
+discussion of the relationship between galaxy morphology, outflow
+velocity, and stellar population age in this sample).
 
-\citet{meu97} argued for a limit near 45~\units (somewhat smaller for
-a Chabrier IMF) based on the surface brightness of starbursts measured
-using rest-frame UV, H$\alpha$, far-IR, and radio continuum emission,
-such that only 10\% of starbursts exceeded this limit.  They argued
-that the momentum flux from supernovae and stellar winds expected at
-this threshold matches the mean central pressure measured by
-\citet{hec90} for starburst-driven winds.
+Finally, we consider the implications of our results for models of
+massive galaxy formation.  Simulations of major galaxy mergers with
+large gas fractions ($f_{gas}\sim50$\%) can produce
+$\textnormal{\mstar}\sim10^{11}$~\msun\ remnants with $r_{e}\sim1$~kpc
+\citep{wuy10}, but our sample includes galaxies of similar mass that
+are smaller in the rest-frame $V$ band by almost an order of
+magnitude.  If the mass in these galaxies follows their $V$-band
+light, it would be extremely challenging for them to grow in size from
+$r_e\sim0.1$~kpc to $r_e\sim5$~kpc to reach the local size--mass
+relation \citep{she03} in the $t\sim6$~Gyr since $z=0.6$.  For
+comparison the compact, quiescent galaxies observed at $z\sim2$
+\citep{tru07,van08} have $t\sim10$~Gyr to grow by a factor of $\sim5$.
+In this context, it is worth noting that the half-light radius
+(ignoring dust attenuation) at rest-frame $V$ band can be a factor of
+5--10 smaller than the half-mass radius for a gas-rich merger at final
+coalescence near the peak of starburst activity \citep{wuy10}.  One
+could test for such size discrepancies and probe the radial dependence
+of the mass-to-light ratio for these galaxies by measuring sizes at
+rest-frame near-IR wavelengths.
 
-There are also relevant arguments about ram pressure driving of
-high-velocity winds from \citet{hec11}.
+\section{Summary}
 
-\subsection{The Eddington Limit from Radiation Pressure on Dust Grains}
-
-In models where gaseous outflows are driven by radiation pressure from
-massive stars, estimates of the maximum $\sigmasfr$ where the outward
-force from radiation exceeds the inward force of gravity are in the
-$\sigmasfr\sim10^3$~\units\ range \citep[e.g.,][]{tho05,hop10}.
-
-% Our galaxies exceed the \citet{meu97} limit but are roughly in line
-% with the limit from radiation pressure.
-
-The relative importance of momentum injection versus thermal heating
-may vary as a function of galaxy mass \citep[e.g.,][]{hop12}, with
-thermal heating being less efficient in galaxies with larger gas
-densities and shorter cooling times.  Regarding momentum injection,
-\citet{sha11} have argued that radiation pressure becomes more
-important than ram pressure at large SFRs.  Massive star clusters with
-large gas surface densities are the ideal launching point for
-galactic-scale outflows driven by radiation pressure
-\citep[e.g.,][]{mur11}, and the outflow velocities are expected to
-scale with escape velocity of the most massive star clusters in a
-galaxy.
-
-\subsection{Outflows at the Escape Velocity}
-
-The observed $\gtrsim1000$~\kms\ outflow velocities we observe correspond
-approximately to the escape velocities for compact regions (i.e.,
-massive star clusters) with the sizes and masses that we've measured.
-
-\begin{equation}
-v_{esc} = \sqrt{2GM_{cl}/r_{cl}} = 2074~\textnormal{km~s}^{-1} \\%\left({v_c\over200}\right)^{5/2} 
-\left({M_{cl}\over10^{11} M_{\odot}}\right)^{1/2} 
-\left({r_{cl}\over200~\textnormal{pc}}\right)^{-1/2}
-\label{eq:vesc}
-\end{equation}
-
-% This is in agreement with the predicitons from radiation pressure
-% launching winds from the most massive star clusters in a galaxy.
-
-Question of whether other observables are plausible.  
-\begin{itemize}
-\item Expected velocity dispersion.  Some results have suggested that
-  turbulence becomes large at high surface densities, and therefore
-  the velocity dispersion should be large.  
-\item The dynamical time for the starburst.  If gas is consumed with
-  an efficiency of a few \% per dynamical time, how long do we expect
-  the starburst to last?
-\end{itemize}
-
-Other points: 
-\begin{itemize}
-\item Is this mechanism viable for the whole sample?  We see large
-  outflow velocities in rest of the sample, where the galaxies are
-  more ``post'' starburst.  This fits in a scenario where the genuine
-  post-starbursts are further along in the evolution after the outflow
-  quenches star formation.
-\item Will these evolve into ellipticals, or do they have enough gas
-  to reform a disk?  If they do quench, how difficult would it be to
-  grow in size to match the local size--mass relationship?  Could
-  their descendants be the handful of local galaxies that don't lie on
-  the size--mass relationship?
-\item Is there disagreement between $L_{IR}+L_{UV}$ and H$\alpha$
-  SFRs?  \citet{hec11} pointed out that this could be a sign of
-  escaping ionizing photons.
-\end{itemize}
-
-\subsection{Limits on Ongoing AGN Activity}
-
-No evidence in spectra for unobscured AGN component.  J1506+5402 has
-X-ray and \nev.
-
-\subsection{Placing These Galaxies in Context}
-
-They are rare and thus represent an unusual or short-lived phase.
-
-Connection to models.  How such large SFRs given the powerful wind?
-
-Connection to ellipticals.  Conceivable that they could grown in size
-sufficiently by $z=0$?
+We have measured large SFR surface densities for galaxies that exhibit
+$\gtrsim1000$~\kms\ outflows.  The largest $\sigmasfr$ values are
+comparable to the Eddington limit from radiation pressure on dust
+grains, and such compact starbursts are expected to have substantial
+momentum input from massive stars and supernovae.  High-velocity
+outflows have been previously interpreted as a signpost of AGN
+feedback, but given that feedback from a compact starburst is capable
+of producing such a signature and is clearly present in this sample,
+we conclude that the outflows we observe are driven by star formation.
 
@@
 
-We acknowledge useful discussions with and assistance from several
-people.  AMD acknowledges support from the Southern California Center
-for Galaxy Evolution, a multi-campus research program funded by the
-University of California Office of Research.
-
-% James Bullock, Xavier Prochaska, Kate Rubin, Art Wolfe, Alex Mendez
+We acknowledge useful discussions with and assistance from James Aird,
+Brandon Kelly, Dusan Keres, David Law, Alexander Mendez, Kate Rubin,
+Art Wolfe, and Stijn Wuyts.  AMD acknowledges support from the
+Southern California Center for Galaxy Evolution, a multi-campus
+research program funded by the University of California Office of
+Research.
 
 \begin{thebibliography}{}
-\bibitem[Abazajian et al.(2009)]{aba09} Abazajian, K.~N.,
-  Adelman-McCarthy, J.~K., Ag{\"u}eros, M.~A., et al.\ 2009, \apjs,
-  182, 543
-% \bibitem[Baldwin et al.(1981)]{bal81} Baldwin, J.~A., Phillips, M.~M.,
-%   \& Terlevich, R.\ 1981, \pasp, 93, 5
-% \bibitem[Barton \& Cooke(2009)]{bar09} Barton, E.~J., \& Cooke,
-%   J.\ 2009, \aj, 138, 1817
-% \bibitem[Bordoloi et al.(2011)]{bor11} Bordoloi, R., et al.\ 2011,
-%   arXiv:1106.0616
-% \bibitem[Buitrago et al.(2008)]{bui08} Buitrago, F., Trujillo, I.,
-%   Conselice, C.~J., Bouwens, R.~J., Dickinson, M., \& Yan, H.\ 2008,
-%   \apjl, 687, L61
-% \bibitem[Coil et al.(2011)]{coi11} Coil, A.~L., Weiner, B.~J., Holz,
-%   D.~E., et al.\ 2011, \apj, 743, 46
+%\bibitem[Abazajian et al.(2009)]{aba09} Abazajian, K.~N.,
+%  Adelman-McCarthy, J.~K., Ag{\"u}eros, M.~A., et al.\ 2009, \apjs,
+%  182, 543
+%\bibitem[Abel \& Satyapal(2008)]{abe08} Abel, N.~P., \& Satyapal,
+%  S.\ 2008, \apj, 678, 686
 \bibitem[Chary \& Elbaz(2001)]{cha01} Chary, R., \& Elbaz, D.\ 2001,
   \apj, 556, 562
-% \bibitem[Chen et al.(2010)]{hchen10} Chen, H.-W., Wild, V., Tinker,
-%   J.~L., Gauthier, J.-R., Helsby, J.~E., Shectman, S.~A., \& Thompson,
-%   I.~B.\ 2010, \apjl, 724, L176
-% \bibitem[Chen et al.(2010b)]{ychen10} Chen, Y.-M., Tremonti, C.~A.,
-%   Heckman, T.~M., Kauffmann, G., Weiner, B.~J., Brinchmann, J., \&
-%   Wang, J.\ 2010, \aj, 140, 445
 \bibitem[Chevalier \& Clegg(1985)]{che85} Chevalier, R.~A., \& Clegg,
   A.~W.\ 1985, \nat, 317, 44
-% \bibitem[Coil et al.(2011)]{coi11} Coil, A.~L., Weiner, B.~J., Holz,
-%   D.~E., Cooper, M.~C., Yan, R., \& Aird, J.\ 2011, arXiv:1104.0681
-\bibitem[Crenshaw et al.(2003)]{cre03} Crenshaw, D.~M., Kraemer,
-  S.~B., \& George, I.~M.\ 2003, \araa, 41, 117
-% \bibitem[Croton et al.(2006)]{cro06} Croton, D.~J., et al.\ 2006,
-%   \mnras, 365, 11
-\bibitem[Dale \& Helou(2002)]{dal02} Dale, D.~A., \& Helou, G.\ 2002,
-  \apj, 576, 159
-% \bibitem[Dekel \& Birnboim(2006)]{dek06} Dekel, A., \& Birnboim,
-%   Y.\ 2006, \mnras, 368, 2
-\bibitem[de Vaucouleurs(1948)]{dev48} de Vaucouleurs, G.\ 1948,
-  Annales d'Astrophysique, 11, 247
-\bibitem[Debuhr et al.(2012)]{deb12} Debuhr, J., Quataert, E., \& Ma,
-  C.-P.\ 2012, \mnras, 420, 2221
+\bibitem[Coil et al.(2011)]{coi11} Coil, A.~L., Weiner, B.~J., Holz,
+  D.~E., et al.\ 2011, \apj, 743, 46
+%\bibitem[Dale \& Helou(2002)]{dal02} Dale, D.~A., \& Helou, G.\ 2002,
+%  \apj, 576, 159
+%\bibitem[de Vaucouleurs(1948)]{dev48} de Vaucouleurs, G.\ 1948,
+%  Annales d'Astrophysique, 11, 247
+%\bibitem[Debuhr et al.(2012)]{deb12} Debuhr, J., Quataert, E., \& Ma,
+%  C.-P.\ 2012, \mnras, 420, 2221
+\bibitem[Diamond-Stanic et al.(2009)]{dia09} Diamond-Stanic, A.~M.,
+  Rieke, G.~H., \& Rigby, J.~R.\ 2009, \apj, 698, 623
 \bibitem[Di Matteo et al.(2005)]{dim05} Di Matteo, T., Springel, V.,
@@
   H.~S., et al.\ 2011, \aap, 533, A119
-\bibitem[Fazio et al.(2004)]{faz04} Fazio, G.~G., Hora, J.~L., Allen,
-  L.~E., et al.\ 2004, \apjs, 154, 10
-\bibitem[Granato et al.(2004)]{gra04} Granato, G.~L., De Zotti, G.,
-  Silva, L., Bressan, A., \& Danese, L.\ 2004, \apj, 600, 580
-\bibitem[Heckman et al.(1990)]{hec90} Heckman, T.~M., Armus, L., \&
-  Miley, G.~K.\ 1990, \apjs, 74, 833
+\bibitem[Fabian(2012)]{fab12} Fabian, A.~C.\ 2012,
+  arXiv:1204.4114
+%\bibitem[Farrah et al.(2007)]{far07} Farrah, D., Bernard-Salas, J.,
+%  Spoon, H.~W.~W., et al.\ 2007, \apj, 667, 149
+%\bibitem[Fazio et al.(2004)]{faz04} Fazio, G.~G., Hora, J.~L., Allen,
+%x  L.~E., et al.\ 2004, \apjs, 154, 10
+\bibitem[Gandhi et al.(2009)]{gan09} Gandhi, P., Horst, H., Smette,
+  A., et al.\ 2009, \aap, 502, 457
+\bibitem[Gilli et al.(2010)]{gil10} Gilli, R., Vignali, C., Mignoli,
+  M., et al.\ 2010, \aap, 519, A92
+%\bibitem[Heckman et al.(1993)]{hec93} Heckman, T.~M., Lehnert, M.~D.,
+%  \& Armus, L.\ 1993, The Environment and Evolution of Galaxies, 188,
+%  455
 \bibitem[Heckman et al.(2000)]{hec00} Heckman, T.~M., Lehnert, M.~D.,
@@
   at Low Redshift, 254, 292
+\bibitem[Heckman et al.(2005)]{hec05} Heckman, T.~M., Ptak, A.,
+  Hornschemeier, A., \& Kauffmann, G.\ 2005, \apj, 634, 161
 \bibitem[Heckman et al.(2011)]{hec11} Heckman, T.~M., et al.\ 2011,
   \apj, 730, 5
-% \bibitem[Hopkins et al.(2009)]{hop09} Hopkins, P.~F., Bundy, K.,
-%   Murray, N., Quataert, E., Lauer, T.~R., \& Ma, C.-P.\ 2009, \mnras,
-%   398, 898
-%\bibitem[Hopkins et al.(2009)]{hop09} Hopkins, P.~F., Hernquist, L.,
-%  Cox, T.~J., Keres, D., \& Wuyts, S.\ 2009, \apj, 691, 1424
 \bibitem[Hopkins et al.(2009)]{hop09} Hopkins, P.~F., Cox, T.~J.,
   Dutta, S.~N., et al.\ 2009, \apjs, 181, 135
-% \bibitem[Hopkins et al.(2010a)]{hop10a} Hopkins, P.~F.,
-%   Bundy, K., Hernquist, L., Wuyts, S., \& Cox, T.~J.\ 2010, \mnras,
-%   401, 1099
 \bibitem[Hopkins et al.(2010)]{hop10} Hopkins, P.~F., Murray, N.,
   Quataert, E., \& Thompson, T.~A.\ 2010, \mnras, 401, L19
-% %\bibitem[Hopkins et al.(2011)]{hop11} Hopkins, P.~F., Quataert, E., \&
-% %  Murray, N.\ 2011, arXiv:1101.4940
-% \bibitem[Hopkins et al.(2011)]{hop11} Hopkins, P.~F., Quataert, E., \&
-%   Murray, N.\ 2011, arXiv:1110.4638
-\bibitem[Hopkins et al.(2012)]{hop12} Hopkins, P.~F., Quataert, E., \&
-  Murray, N.\ 2012, \mnras, arXiv:1110.4638
-% \bibitem[Kacprzak et al.(2010)]{kac10} Kacprzak, G.~G., Churchill,
-%   C.~W., Ceverino, D., Steidel, C.~C., Klypin, A., \& Murphy,
-%   M.~T.\ 2010, \apj, 711, 533
-% \bibitem[Kacprzak et al.(2011a)]{kac11a} Kacprzak, G.~G., Churchill,
-%   C.~W., Barton, E.~J., \& Cooke, J.\ 2011, \apj, 733, 105
-% \bibitem[Kacprzak et al.(2011b)]{kac11b} Kacprzak, G.~G., Churchill,
-%   C.~W., Evans, J.~L., Murphy, M.~T., \& Steidel, C.~C.\ 2011,
-%   arXiv:1106.3068
-% \bibitem[Kauffmann et al.(2003)]{kau03} Kauffmann, G., Heckman, T.~M.,
-%   Tremonti, C., et al.\ 2003, \mnras, 346, 1055
-% \bibitem[Kennicutt(1998)]{ken98} Kennicutt, R.~C., Jr.\ 1998, \araa,
-%   36, 189
 \bibitem[Kennicutt(1998)]{ken98} Kennicutt, R.~C., Jr.\ 1998, \apj,
   498, 541
-% \bibitem[Kere{\v s} et al.(2005)]{ker05} Kere{\v s}, D., Katz, N.,
-%   Weinberg, D.~H., \& Dav{\'e}, R.\ 2005, \mnras, 363, 2
-% \bibitem[Kere{\v s} et al.(2009)]{ker09} Kere{\v s}, D., Katz, N.,
-%   Dav{\'e}, R., Fardal, M., \& Weinberg, D.~H.\ 2009, \mnras, 396,
-%   2332
-% \bibitem[Kobulnicky \& Kewley(2004)]{kob04} Kobulnicky, H.~A., \&
-%   Kewley, L.~J.\ 2004, \apj, 617, 240
 \bibitem[Kormendy et al.(2009)]{kor09} Kormendy, J., Fisher, D.~B.,
   Cornell, M.~E., \& Bender, R.\ 2009, \apjs, 182, 216
-% \bibitem[Kriek et al.(2010)]{kri10} Kriek, M., et al.\ 2010, \apjl,
-%   722, L64
-\bibitem[Law et al.(2012)]{law12} Law, D.~R., Steidel, C.~C., Shapley,
-  A.~E., et al.\ 2012, \apj, 745, 85
 \bibitem[Lehnert \& Heckman(1996)]{leh96} Lehnert, M.~D., \& Heckman,
   T.~M.\ 1996, \apj, 472, 546
-% \bibitem[Lehnert \& Heckman(1996)]{leh96} Lehnert, M.~D., \& Heckman,
-%   T.~M.\ 1996, \apj, 462, 651
 \bibitem[Leitherer et al.(1992)]{lei92} Leitherer, C., Robert, C., \&
   Drissen, L.\ 1992, \apj, 401, 596
+\bibitem[Leitherer et al.(1999)]{lei99} Leitherer, C., Schaerer, D.,
+  Goldader, J.~D., et al.\ 1999, \apjs, 123, 3
+\bibitem[Lotz et al.(2011)]{lot11} Lotz, J.~M., Jonsson, P., Cox,
+  T.~J., et al.\ 2011, \apj, 742, 103
 \bibitem[Martin(2005)]{mar05} Martin, C.~L.\ 2005, \apj, 621, 227
-% \bibitem[Martin(2006)]{mar06} Martin, C.~L.\ 2006, \apj, 647, 222
-% \bibitem[Martin \& Bouch{\'e}(2009)]{mar09} Martin, C.~L., \&
-%   Bouch{\'e}, N.\ 2009, \apj, 703, 1394
-% \bibitem[McIntosh et al.(2005)]{mci05} McIntosh, D.~H., et al.\ 2005,
-%   \apj, 632, 191
+%\bibitem[Martin et al.(2005)]{mar05galex} Martin, D.~C., Fanson, J.,
+%  Schiminovich, D., et al.\ 2005, \apjl, 619, L1
 \bibitem[Meurer et al.(1997)]{meu97} Meurer, G.~R., Heckman, T.~M.,
   Lehnert, M.~D., Leitherer, C., \& Lowenthal, J.\ 1997, \aj, 114, 54
-% \bibitem[Morrissey et al.(2007)]{mor07} Morrissey, P., Conrow, T.,
-%   Barlow, T.~A., et al.\ 2007, \apjs, 173, 682
+\bibitem[Mihos \& Hernquist(1996)]{mih96} Mihos, J.~C., \& Hernquist,
+  L.\ 1996, \apj, 464, 641
 \bibitem[Moustakas et al.(2011)]{mou11} Moustakas, J., Zaritsky, D.,
@@
   Thompson, T.~A.\ 2011, \apj, 735, 66
-% \bibitem[Nath \& Silk(2009)]{nat09} Nath, B.~B., \& Silk, J.\ 2009,
-%   \mnras, 396, L90
-% \bibitem[Nestor et al.(2011)]{nes11} Nestor, D.~B., Johnson, B.~D.,
-%   Wild, V., M{\'e}nard, B., Turnshek, D.~A., Rao, S., \& Pettini,
-%   M.\ 2011, \mnras, 412, 1559
-% \bibitem[Oke(1990)]{oke90} Oke, J.~B.\ 1990, \aj, 99, 1621
-% \bibitem[Oke et al.(1995)]{oke95} Oke, J.~B., et al.\ 1995, \pasp,
-%   107, 375
-% \bibitem[Oppenheimer \& Dav{\'e}(2006)]{opp06} Oppenheimer, B.~D., \&
-%   Dav{\'e}, R.\ 2006, \mnras, 373, 1265
-% \bibitem[Osterbrock(1989)]{ost89} Osterbrock, D.~E.\ 1989,
-%   Astrophysics of Gaseous Nebulae and Active Galactic Nuclei (Mill
-%   Valley, CA: University Science Books) 
 \bibitem[Overzier et al.(2009)]{ove09} Overzier, R.~A., Heckman,
   T.~M., Tremonti, C., et al.\ 2009, \apj, 706, 203
-% \bibitem[Pagel et al.(1979)]{pag79} Pagel, B.~E.~J., Edmunds, M.~G.,
-%   Blackwell, D.~E., Chun, M.~S., \& Smith, G.\ 1979, \mnras, 189, 95
 \bibitem[Peng et al.(2002)]{pen02} Peng, C.~Y., Ho, L.~C., Impey,
   C.~D., \& Rix, H.-W.\ 2002, \aj, 124, 266
-\bibitem[Peng et al.(2010)]{pen10} Peng, C.~Y., Ho, L.~C., Impey,
-  C.~D., \& Rix, H.-W.\ 2010, \aj, 139, 2097
-% \bibitem[Pettini et al.(2001)]{pet01} Pettini, M., Shapley, A.~E.,
-%   Steidel, C.~C., Cuby, J.-G., Dickinson, M., Moorwood, A.~F.~M.,
-%   Adelberger, K.~L., \& Giavalisco, M.\ 2001, \apj, 554, 981
+%\bibitem[Peng et al.(2010)]{pen10} Peng, C.~Y., Ho, L.~C., Impey,
+%  C.~D., \& Rix, H.-W.\ 2010, \aj, 139, 2097
 \bibitem[Polletta et al.(2007)]{pol07} Polletta, M., Tajer, M.,
   Maraschi, L., et al.\ 2007, \apj, 663, 81
-% \bibitem[Prochaska \& Hennawi(2009)]{pro09} Prochaska, J.~X., \&
-%   Hennawi, J.~F.\ 2009, \apj, 690, 1558
-% \bibitem[Prochaska et al.(2011a)]{pro11a} Prochaska, J.~X., Kasen, D.,
-%   \& Rubin, K.\ 2011, arXiv:1102.3444
-% \bibitem[Prochaska et al.(2011b)]{pro11b} Prochaska,
-%   J.~X., Weiner, B., Chen, H.~-., Mulchaey, J.~S., \& Cooksey,
-%   K.~L.\ 2011, arXiv:1103.1891
 \bibitem[Rodr{\'{\i}}guez Zaur{\'{\i}}n et al.(2008)]{rod08}
@@
 \bibitem[Rupke et al.(2005)]{rup05} Rupke, D.~S., Veilleux, S., \&
-  Sanders, D.~B.\ 2005, \apjs, 160, 115 % analysis and discussion
-% \bibitem[Rupke \& Veilleux(2011)]{rup11} Rupke, D.~S.~N., \& Veilleux,
-%   S.\ 2011, \apjl, 729, L27
-% \bibitem[Sato et al.(2009)]{sat09} Sato, T., Martin, C.~L., Noeske,
-%   K.~G., Koo, D.~C., \& Lotz, J.~M.\ 2009, \apj, 696, 214
-\bibitem[Schlegel et al.(1998)]{sch98} Schlegel, D.~J., Finkbeiner,
-  D.~P., \& Davis, M.\ 1998, \apj, 500, 525
-% \bibitem[Schwartz \& Martin(2004)]{sch04} Schwartz, C.~M., \& Martin,
-%   C.~L.\ 2004, \apj, 610, 201
+  Sanders, D.~B.\ 2005, \apjs, 160, 115 
+%\bibitem[Schlegel et al.(1998)]{sch98} Schlegel, D.~J., Finkbeiner,
+%  D.~P., \& Davis, M.\ 1998, \apj, 500, 525
 \bibitem[Scoville et al.(1997)]{sco97} Scoville, N.~Z., Yun, M.~S., \&
   Bryant, P.~M.\ 1997, \apj, 484, 702
-\bibitem[Sharma \& Nath(2011)]{sha11} Sharma, M., \& Nath,
-  B.~B.\ 2011, arXiv:1112.3447
 \bibitem[Shapley et al.(2003)]{sha03} Shapley, A.~E., Steidel, C.~C.,
@@
   \aap, 331, L1
-% \bibitem[Springel \& Hernquist(2003)]{spr03} Springel, V., \&
-%   Hernquist, L.\ 2003, \mnras, 339, 312
-% \bibitem[Steidel et al.(2002)]{ste02} Steidel, C.~C., Kollmeier,
-%   J.~A., Shapley, A.~E., Churchill, C.~W., Dickinson, M., \& Pettini,
-%   M.\ 2002, \apj, 570, 526
-\bibitem[Steidel et al.(2010)]{ste10} Steidel, C.~C., Erb, D.~K.,
-  Shapley, A.~E., Pettini, M., Reddy, N., Bogosavljevi{\'c}, M.,
-  Rudie, G.~C., \& Rakic, O.\ 2010, \apj, 717, 289
-% \bibitem[Stewart et al.(2011a)]{ste11a} Stewart, K.~R., Kaufmann, T.,
-%   Bullock, J.~S., Barton, E.~J., Maller, A.~H., Diemand, J., \&
-%   Wadsley, J.\ 2011, \apjl, 735, L1
-% \bibitem[Stewart et al.(2011b)]{ste11b} Stewart, K.~R., Kaufmann, T.,
-%   Bullock, J.~S., Barton, E.~J., Maller, A.~H., Diemand, J., \&
-%   Wadsley, J.\ 2011, arXiv:1103.4388
-% \bibitem[Strickland et al.(2004)]{str04} Strickland, D.~K., Heckman,
-%   T.~M., Colbert, E.~J.~M., Hoopes, C.~G., \& Weaver, K.~A.\ 2004,
-%   \apjs, 151, 193
-% \bibitem[Taylor et al.(2010)]{tay10} Taylor, E.~N., Franx, M.,
-%   Glazebrook, K., Brinchmann, J., van der Wel, A., \& van Dokkum,
-%   P.~G.\ 2010, \apj, 720, 723
+%\bibitem[Steidel et al.(2010)]{ste10} Steidel, C.~C., Erb, D.~K.,
+%  Shapley, A.~E., Pettini, M., Reddy, N., Bogosavljevi{\'c}, M.,
+%  Rudie, G.~C., \& Rakic, O.\ 2010, \apj, 717, 289
+\bibitem[Tacconi et al.(2010)]{tac10} Tacconi, L.~J., Genzel, R.,
+  Neri, R., et al.\ 2010, \nat, 463, 781
 \bibitem[Thompson et al.(2005)]{tho05} Thompson, T.~A., Quataert, E.,
@@
   al.\ 2008, \apjl, 677, L5
-% \bibitem[van Dokkum et al.(2010)]{van10} van Dokkum, P.~G., et
-%   al.\ 2010, \apj, 709, 1018
-% \bibitem[Vogt et al.(1994)]{vog94} Vogt, S.~S., et al.\ 1994,
-%   \procspie, 2198, 362
+\bibitem[Veilleux et al.(2005)]{vei05} Veilleux, S., Cecil, G., \&
+  Bland-Hawthorn, J.\ 2005, \araa, 43, 769
 \bibitem[Veilleux et al.(2006)]{vei06} Veilleux, S., Kim, D.-C., Peng,
@@
   \apj, 692, 187
-\bibitem[Werner et al.(2004)]{wer04} Werner, M.~W., Roellig, T.~L.,
-  Low, F.~J., et al.\ 2004, \apjs, 154, 1
-\bibitem[Wright et al.(2010)]{wri10} Wright, E.~L., Eisenhardt,
-  P.~R.~M., Mainzer, A.~K., et al.\ 2010, \aj, 140, 1868
-% \bibitem[Wuyts et al.(2010)]{wuy10} Wuyts, S., Cox, T.~J., Hayward,
-%   C.~C., Franx, M., Hernquist, L., Hopkins, P.~F., Jonsson, P., \& van
-%   Dokkum, P.~G.\ 2010, \apj, 722, 1666
-% \bibitem[Wuyts et al.(2011)]{wuy11} Wuyts, S., et al.\ 2011,
-%   arXiv:1107.0317
+%\bibitem[Werner et al.(2004)]{wer04} Werner, M.~W., Roellig, T.~L.,
+%  Low, F.~J., et al.\ 2004, \apjs, 154, 1
+%\bibitem[Wright et al.(2010)]{wri10} Wright, E.~L., Eisenhardt,
+%  P.~R.~M., Mainzer, A.~K., et al.\ 2010, \aj, 140, 1868
+\bibitem[Wuyts et al.(2010)]{wuy10} Wuyts, S., Cox, T.~J., Hayward,
+  C.~C., et al.\ 2010, \apj, 722, 1666
 \bibitem[Wuyts et al.(2011)]{wuy11} Wuyts, S., F{\"o}rster Schreiber,
   N.~M., van der Wel, A., et al.\ 2011, \apj, 742, 96
-% \bibitem[Zhang \& Thompson(2010)]{zha10} Zhang, D., \& Thompson,
-%   T.~A.\ 2010, arXiv:1005.4691
-% \bibitem[Zirm et al.(2007)]{zir07} Zirm, A.~W., et al.\ 2007, \apj,
-%   656, 66
 \end{thebibliography}
 
-\clearpage
-
-%\clearpage
-
-% \clearpage
-% 
-% \begin{figure*}[!t]
-% \begin{center}
-% \includegraphics[angle=0,scale=.60]{j0905_hires_mg.ps}
-% \caption{Keck/HIRES spectra.}
-% \label{fig:hires}
-% \end{center}
-% \end{figure*}
-
-%\clearpage
-
 \end{document}

### 2015-07-17 doc/tex/sigmasfr/ms.tex
moved the tex and proposals directories to doc

--- 2012-05-08 tex/sigmasfr/ms.tex
@@
-\documentclass[apj]{emulateapj}
+%\documentclass[apj]{emulateapj}
+\documentclass[12pt,preprint]{aastex}
 
@@
   University of California, San Diego, La Jolla, CA 92093, USA}
-\altaffiltext{2}{Center for Galaxy Evolution Fellow}
+\altaffiltext{2}{Center for Galaxy Evolution Fellow; aleks@ucsd.edu}
 \altaffiltext{3}{Department of Astronomy, University of
@@
 compact nuclei, and argued that such velocities could be explained by
-a wind that is launched from $r_0\sim100$~pc and driven by feedback
-from massive stars and supernovae.
+a wind launched from $r_0\sim100$~pc and driven by feedback from
+massive stars and supernovae.
 
@@
 Explorer (GALEX) photometry.
-
-% we focus our analysis on the galaxies with the most extreme
-% $\sigmasfr$ values.
-
-\begin{figure}[!t]
-\includegraphics[angle=0,scale=0.41]{f1.ps}
-\caption{Left: Observed UV--IR SEDs ($\lrest=0.1$--15~$\mu$m) for
-  three galaxies with the largest SFR surface densities
-  ($\sigmasfr\approx3000$~\units).  The top two SEDs are offset by 5
-  and 10 magnitudes, respectively.  We show stellar population fits to
-  the $\lrest=0.1$--3~$\mu$m emission (black solid line) and three
-  templates for dust emission \citep[M82 starburst, blue dashed line;
-    Arp 220 starburst, green dot-dashed line; obscured quasar, red
-    dotted line;][]{pol07} scaled to match the $\lobs=4.6~\mu$m band.
-  The starburst templates provide reasonable fits to the $\lobs=12$
-  and 22~$\mu$m WISE photometry, while the quasar template does not.
-  Right: HST/WFC3 F814W images (probing $\lrest\approx5000$~\AA)
-  showing that these galaxies are dominated by a compact nucleus.}
-\label{fig:seds}
-\end{figure}
 
@@
 
-\begin{figure}[!t]
-\includegraphics[angle=0,scale=0.41]{f2.ps}
-\caption{One-dimensional surface brightness profile for J0905+5759,
-  which has the smallest effective radius in the sample.  The observed
-  profile is shown as the solid black line, and the profiles of six
-  stars in the same image are shown in blue, normalized to the same
-  central surface brightness.  The best-fit de Vaucouleurs profile
-  with $r_e=100$~pc is shown as a dashed red line, and for comparison
-  a broader profile with $r_e=0.04\arcsec=290$~pc is shown as the
-  dotted green line.  This galaxy is quite compact, but is more
-  extended than a point source.}
-\label{fig:profile}
-\end{figure}
-
 \subsection{Star Formation Rates and Stellar Masses}\label{sec:seds}
 
-% We gathered photometry from the All-Sky Release of the Wide-field
-% Infrared Survey Explorer \citep[WISE,][]{wri10}, the Seventh Data
-% Release of the Sloan Digital Sky Survey \citep[SDSS,][]{aba09}, and
-% General Release 6 from the Galaxy Evolution Explorer
-% \citep[GALEX,][]{mar05galex}.  
 We gathered photometry from the WISE All-Sky Release, the SDSS Seventh
@@
 galaxies in Figure~\ref{fig:seds}.
-
-% All the photometry was corrected for Galactic extinction
-% based on the \citet{sch98} dust maps.
 
@@
 ionizing ($\lambda<912$~\AA) to non-ionizing UV photons.
-
-\begin{figure}[!t]
-\includegraphics[angle=0,scale=0.41]{f3.ps}
-\caption{Spectra covering $\lrest=2500$--5200~\AA\ for the three
-  galaxies shown in Figure~\ref{fig:seds}.  For clarity the top two
-  spectra are offset by $+10$ and $+20$ units.  These spectra are
-  dominated by the light of a young stellar population but have
-  relatively weak nebular emission lines (\oii~$\lambda3727$,
-  H$\beta$~$\lambda4861$, \oiii~$\lambda5007$) and strong
-  \mgii~$\lambda\lambda2796,2803$ absorption arising from the
-  interstellar medium.  The absense of broad \mgii\ or H$\beta$
-  emission lines rules out a significant contribution to the optical
-  continuum light from an AGN.  The panels on the right highlight the
-  region around the \mgii\ doublet in both wavelength and velocity
-  space to illustrate the outflow kinematics.  The spectrum in the
-  bottom panel has sufficient spectral resolution
-  ($\textnormal{FWHM}\approx8$~\kms) to resolve the intrinsic shape of
-  the absorption-line profile, revealing that the gas near the
-  centroid velocity ($v=-2470$~\kms) covers the entire galaxy.}
-\label{fig:spectra}
-\end{figure}
-
-\begin{figure*}[!t]
-\begin{center}
-\includegraphics[angle=0,scale=.8]{f4.ps} 
-\caption{SFR surface densities and stellar masses for the HST--WISE
-  sample described in this paper (black circles, with symbol size
-  proportional to outflow velocity), along with samples of $z<0.3$
-  gas-rich mergers (orange squares) and $z\sim1$ star-forming galaxies
-  (shown with 68\%, 95\%, and 99.7\% contours).  We mark the empirical
-  threshold for launching winds \citep[dotted line,
-    $\sigmasfr\approx0.1$~\units;][]{hec02}, the 90th-percentile
-  starburst intensity limit from \citet{meu97} (dashed line,
-  $\sigmasfr\approx25$~\units), and the Eddington limit from radiation
-  pressure on dust grains \citep[solid line,
-    $\sigmasfr\approx3000$~\units;][]{mur05,tho05,hop10}.  The
-  representative error bar in the top-right portion of the plot
-  corresponds to uncertainties of 0.3~dex in $\sigmasfr$ and 0.2~dex
-  in stellar mass.  Our HST--WISE sample overlaps with the region
-  characterized by gas-rich mergers, and extends to very large SFR
-  surface densities near the Eddington limit, suggesting growth that
-  is limited by momentum injection from massive stars.}
-\label{fig:sigmasfr}
-\end{center}
-\end{figure*}
 
@@
 $L_{\textnormal{\scriptsize{MIR}}}\approx7\times10^{42}$~erg~s$^{-1}$,
-which is 400$\times$ smaller than observed luminosity for J1506+5402
+which is 400$\times$ smaller than the observed luminosity for
+J1506+5402
 ($L_{\textnormal{\scriptsize{MIR}}}\approx3\times10^{45}$~erg~s$^{-1}$).
@@
 large $\sigmasfr$ values are not affected by AGN contamination.
-
-% Thus, similar to local ULIRGs \citep[e.g.,][]{far07}, the
-% bolometric output of the galaxies in our sample is dominated by star
-% formation, and we conclude that our results regarding large
-% $\sigmasfr$ values are not affected by AGN contamination.
 
@@
 research program funded by the University of California Office of
-Research.
+Research.  Support for HST GO-12272 was provided by NASA through a
+grant from STScI.  Support for Spitzer GO-60145 was provided by
+contract 1419615 from JPL/Caltech.
 
 \begin{thebibliography}{}
-%\bibitem[Abazajian et al.(2009)]{aba09} Abazajian, K.~N.,
-%  Adelman-McCarthy, J.~K., Ag{\"u}eros, M.~A., et al.\ 2009, \apjs,
-%  182, 543
-%\bibitem[Abel \& Satyapal(2008)]{abe08} Abel, N.~P., \& Satyapal,
-%  S.\ 2008, \apj, 678, 686
 \bibitem[Chary \& Elbaz(2001)]{cha01} Chary, R., \& Elbaz, D.\ 2001,
@@
   D.~E., et al.\ 2011, \apj, 743, 46
-%\bibitem[Dale \& Helou(2002)]{dal02} Dale, D.~A., \& Helou, G.\ 2002,
-%  \apj, 576, 159
-%\bibitem[de Vaucouleurs(1948)]{dev48} de Vaucouleurs, G.\ 1948,
-%  Annales d'Astrophysique, 11, 247
-%\bibitem[Debuhr et al.(2012)]{deb12} Debuhr, J., Quataert, E., \& Ma,
-%  C.-P.\ 2012, \mnras, 420, 2221
 \bibitem[Diamond-Stanic et al.(2009)]{dia09} Diamond-Stanic, A.~M.,
@@
   arXiv:1204.4114
-%\bibitem[Farrah et al.(2007)]{far07} Farrah, D., Bernard-Salas, J.,
-%  Spoon, H.~W.~W., et al.\ 2007, \apj, 667, 149
-%\bibitem[Fazio et al.(2004)]{faz04} Fazio, G.~G., Hora, J.~L., Allen,
-%x  L.~E., et al.\ 2004, \apjs, 154, 10
 \bibitem[Gandhi et al.(2009)]{gan09} Gandhi, P., Horst, H., Smette,
@@
   M., et al.\ 2010, \aap, 519, A92
-%\bibitem[Heckman et al.(1993)]{hec93} Heckman, T.~M., Lehnert, M.~D.,
-%  \& Armus, L.\ 1993, The Environment and Evolution of Galaxies, 188,
-%  455
 \bibitem[Heckman et al.(2000)]{hec00} Heckman, T.~M., Lehnert, M.~D.,
@@
 \bibitem[Martin(2005)]{mar05} Martin, C.~L.\ 2005, \apj, 621, 227
-%\bibitem[Martin et al.(2005)]{mar05galex} Martin, D.~C., Fanson, J.,
-%  Schiminovich, D., et al.\ 2005, \apjl, 619, L1
 \bibitem[Meurer et al.(1997)]{meu97} Meurer, G.~R., Heckman, T.~M.,
@@
   C.~D., \& Rix, H.-W.\ 2002, \aj, 124, 266
-%\bibitem[Peng et al.(2010)]{pen10} Peng, C.~Y., Ho, L.~C., Impey,
-%  C.~D., \& Rix, H.-W.\ 2010, \aj, 139, 2097
 \bibitem[Polletta et al.(2007)]{pol07} Polletta, M., Tajer, M.,
@@
   Sanders, D.~B.\ 2005, \apjs, 160, 115 
-%\bibitem[Schlegel et al.(1998)]{sch98} Schlegel, D.~J., Finkbeiner,
-%  D.~P., \& Davis, M.\ 1998, \apj, 500, 525
 \bibitem[Scoville et al.(1997)]{sco97} Scoville, N.~Z., Yun, M.~S., \&
@@
   \aap, 331, L1
-%\bibitem[Steidel et al.(2010)]{ste10} Steidel, C.~C., Erb, D.~K.,
-%  Shapley, A.~E., Pettini, M., Reddy, N., Bogosavljevi{\'c}, M.,
-%  Rudie, G.~C., \& Rakic, O.\ 2010, \apj, 717, 289
 \bibitem[Tacconi et al.(2010)]{tac10} Tacconi, L.~J., Genzel, R.,
@@
   \apj, 692, 187
-%\bibitem[Werner et al.(2004)]{wer04} Werner, M.~W., Roellig, T.~L.,
-%  Low, F.~J., et al.\ 2004, \apjs, 154, 1
-%\bibitem[Wright et al.(2010)]{wri10} Wright, E.~L., Eisenhardt,
-%  P.~R.~M., Mainzer, A.~K., et al.\ 2010, \aj, 140, 1868
 \bibitem[Wuyts et al.(2010)]{wuy10} Wuyts, S., Cox, T.~J., Hayward,
@@
 
+\clearpage
+
+\begin{figure}[!t]
+\begin{center}
+\includegraphics[angle=0,scale=0.7]{f1.ps}
+\caption{Left: Observed UV--IR SEDs ($\lrest=0.1$--15~$\mu$m) for
+  three galaxies with the largest SFR surface densities
+  ($\sigmasfr\approx3000$~\units).  The top two SEDs are offset by 5
+  and 10 magnitudes, respectively.  We show stellar population fits to
+  the $\lrest=0.1$--3~$\mu$m emission (black solid line) and three
+  templates for dust emission \citep[M82 starburst, blue dashed line;
+    Arp 220 starburst, green dot-dashed line; obscured quasar, red
+    dotted line;][]{pol07} scaled to match the $\lobs=4.6~\mu$m band.
+  The starburst templates provide reasonable fits to the $\lobs=12$
+  and 22~$\mu$m WISE photometry, while the quasar template does not.
+  Right: HST/WFC3 F814W images (probing $\lrest\approx5000$~\AA)
+  showing that these galaxies are dominated by a compact nucleus.}
+\label{fig:seds}
+\end{center}
+\end{figure}
+
+\clearpage
+
+\begin{figure}[!t]
+\begin{center}
+\includegraphics[angle=0,scale=0.7]{f2.ps}
+\caption{One-dimensional surface brightness profile for J0905+5759,
+  which has the smallest effective radius in the sample.  The observed
+  profile is shown as the solid black line, and the profiles of six
+  stars in the same image are shown in blue, normalized to the same
+  central surface brightness.  The best-fit de Vaucouleurs profile
+  with $r_e=100$~pc is shown as a dashed red line, and for comparison
+  a broader profile with $r_e=0.04\arcsec=290$~pc is shown as the
+  dotted green line.  This galaxy is quite compact, but is more
+  extended than a point source.}
+\label{fig:profile}
+\end{center}
+\end{figure}
+
+\clearpage
+
+\begin{figure}[!t]
+\begin{center}
+\includegraphics[angle=0,scale=0.7]{f3.ps}
+\caption{Spectra covering $\lrest=2500$--5200~\AA\ for the three
+  galaxies shown in Figure~\ref{fig:seds}.  For clarity the top two
+  spectra are offset by $+10$ and $+20$ units.  These spectra are
+  dominated by the light of a young stellar population but have
+  relatively weak nebular emission lines (\oii~$\lambda3727$,
+  H$\beta$~$\lambda4861$, \oiii~$\lambda5007$) and strong
+  \mgii~$\lambda\lambda2796,2803$ absorption arising from the
+  interstellar medium.  The absense of broad \mgii\ or H$\beta$
+  emission lines rules out a significant contribution to the optical
+  continuum light from an AGN.  The panels on the right highlight the
+  region around the \mgii\ doublet in both wavelength and velocity
+  space to illustrate the outflow kinematics.  The spectrum in the
+  bottom panel has sufficient spectral resolution
+  ($\textnormal{FWHM}\approx8$~\kms) to resolve the intrinsic shape of
+  the absorption-line profile, revealing that the gas near the
+  centroid velocity ($v=-2470$~\kms) covers the entire galaxy.}
+\label{fig:spectra}
+\end{center}
+\end{figure}
+
+\clearpage
+
+\begin{figure*}[!t]
+\begin{center}
+\includegraphics[angle=0,scale=.78]{f4.ps} 
+\caption{SFR surface densities and stellar masses for the HST--WISE
+  sample described in this paper (black circles, symbol size
+  proportional to outflow velocity), along with samples of $z<0.3$
+  gas-rich mergers (orange squares) and $z\sim1$ star-forming galaxies
+  (shown with 68\%, 95\%, and 99.7\% contours; see
+  Section~\ref{sec:discussion}).  We mark the empirical threshold for
+  launching winds \citep[dotted line,
+    $\sigmasfr\approx0.1$~\units;][]{hec02}, the 90th-percentile
+  starburst intensity limit from \citet{meu97} (dashed line,
+  $\sigmasfr\approx25$~\units), and the Eddington limit from radiation
+  pressure on dust grains \citep[solid line,
+    $\sigmasfr\approx3000$~\units;][]{mur05,tho05,hop10}.  The
+  representative error bar in the top-right portion of the plot
+  corresponds to uncertainties of 0.3~dex in $\sigmasfr$ and 0.2~dex
+  in stellar mass.  Our HST--WISE sample overlaps with the region
+  characterized by gas-rich mergers, and extends to very large SFR
+  surface densities near the Eddington limit, suggesting growth that
+  is limited by momentum injection from massive stars.}
+\label{fig:sigmasfr}
+\end{center}
+\end{figure*}
+
 \end{document}
